---
fontsize: 11pt
geometry: top=2cm, bottom=2cm, left=1.5cm, right=1.5cm,headsep=1cm
header-includes:
- \usepackage[utf8]{inputenc}
- \usepackage{fancyhdr}
- \pagestyle{fancy}
- \fancyfoot{}
- \usepackage{ragged2e}
- \linespread{1.15}
- \usepackage{float}
output: pdf_document
fig_caption: yes
keep_tex: yes
---

```{r set_libraries, include=FALSE, warning=FALSE}

#Libraries used in the r code
if (!require(pacman)){
  install.packages("pacman", repos="http://ftp.ussg.iu.edu/CRAN/")
  library(pacman)
}
p_load(kableExtra, sqldf, RODBC, dplyr)

#special for this script
p_load(plyr, data.table)

```


```{r set_parameters, include=FALSE}

# yr <- c(@paramYear)
# species <- @paramSpecies
# eventId <- @paramEvent
# expert <- @paramExpert
# trainee <- @paramTrainee

yr <- c(2024)
species <- c("BLH")
eventId <- "40"
expert <- "hr"
trainee <- "gho"
```


```{r get_data, include=FALSE}

channel <- odbcConnect("FishLine")

AQ <- sqlQuery(channel, paste("SELECT
       [L_OtolithReadingRemarkID] as otolithReadingRemarkId
      ,[otolithReadingRemark] AS AQ
  FROM  [FishLine].[dbo].[L_OtolithReadingRemark]
  ", sep = ""))

event <- sqlQuery(channel, paste("SELECT         
       CONCAT(sdEventId,' - ',name) as ids
  FROM   [FishLine].[dbo].[SDEvent]
  WHERE  sdEventId = (",eventId,")
  ", sep = ""))

sample <- sqlQuery(channel, paste("SELECT         
       [sdSampleId]
      ,[sdEventId]
      ,[animalId]
      ,[catchDate]
      ,[fishLengthMM]
      ,[sexCode]
  FROM   [FishLine].[dbo].[SDSample]
  WHERE  (sdEventId = ",eventId,")
  ", sep = ""))

file <- sqlQuery(channel, paste("SELECT         
       [sdFileId]
      ,[sdSampleId]
      ,[fileName]
      ,[path]
      ,[scale]
      ,[imageWidth]
      ,[imageHeight]
  FROM   [FishLine].[dbo].[SDFile]
  WHERE  sdSampleId IN (",paste(sample$sdSampleId,collapse = ","),")
  ", sep = ""))

annot <- sqlQuery(channel, paste("SELECT         
       [sdAnnotationId]
      ,[sdFileId]
      ,[createdByUserName]
      ,[isApproved]
      ,[isFixed]
      ,[isReadOnly]
      ,[createdTime]
      ,[modifiedTime]
      ,[sdAnalysisParameterId]
      ,[otolithReadingRemarkId]
      ,[edgeStructure]
      ,[age]
      ,[comment]
  FROM   [FishLine].[dbo].[SDAnnotation]
  WHERE  sdFileId IN (",paste(file$sdFileId,collapse = ","),") AND
         createdByUserName IN ('",expert,"' , '",trainee,"') AND
         isFixed = ",0,"
  ", sep = ""))

close(channel)


###
df1 <- merge(sample, file, by = "sdSampleId", all.x = T)
df2 <- merge(df1, annot, by = "sdFileId", all.x = T)

df2[is.na(df2$otolithReadingRemarkId), "otolithReadingRemarkId"] <- 15
df3 <- merge(df2, AQ, by = "otolithReadingRemarkId") 

df3$comment <- gsub(df3$comment, pattern = "\\.|,|;", replacement = " ")

setDT(df3)
#get rid of one user with more than one created age for the same fish, choose the latest
df4 <- unique(df3[order(-createdTime)], by=c("animalId", "createdByUserName"))

not_included <- c(names(df3)[! names(df3) %in% c("createdTime", "modifiedTime", "sdAnnotationId", "isApproved", "otolithReadingRemarkId")])
out <- df4[, ..not_included]

out <- dcast(out, ...~ createdByUserName, value.var = c("age", "AQ", "edgeStructure", "comment"))

write.csv(out, paste0(eventId, "_TwoReader_data_", format(Sys.Date(), "%d%m%y"), ".csv"),
            quote = FALSE, row.names = FALSE, na = '')

df4 <- df4[!is.na(df4$age), ]
```


```{r make_tables, include=FALSE}

dat <- dcast(df4, animalId + catchDate + fishLengthMM + sexCode ~ createdByUserName, value.var = c("age", "AQ"))

names(dat) <- gsub(expert, "expert", names(dat))
names(dat) <- gsub(trainee, "trainee", names(dat))

dat <- data.frame(dat)
ages <- c(0:max(dat$age_trainee, dat$age_expert))
#table 1
fun <- function(j) {
  
  i = ages[j]
  
  no_qc <- nrow(dat[!is.na(dat$QC) & dat$QC == i, ])
  
  no_exp <- nrow(dat[dat$age_expert == i,])
  no_trn <- nrow(dat[dat$age_trainee == i,])
  
  no_agr <- nrow(dat[dat$age_trainee == i & dat$age_expert == i, ])
  
  pct_agr <- (no_agr/no_exp)*100  
  
  a <- dat[dat$age_expert == i, ]
  ape <- sum(abs(((a$age_trainee/a$age_expert)*100)-100))/no_exp
  
  l_exp <- mean(dat[dat$age_expert == i, "fishLengthMM"])
  l_trn <- mean(dat[dat$age_trainee == i, "fishLengthMM"])
  
  av_trn_age <- mean(dat[dat$age_expert == i, "age_trainee"])
  sd_trn_age <- sd(dat[dat$age_expert == i, "age_trainee"])
  
  cv_trn <- 0.5 * sd_trn_age/av_trn_age
  conf <- 1.96 *(sd_trn_age/sqrt(no_exp))
  
  conf_lo <- av_trn_age - conf
  conf_up <- av_trn_age + conf
  
  bias <- av_trn_age - i
  
  
  #gather info
  out <- data.frame(age = i, no_exp, no_trn, no_agr, pct_agr, ape, l_exp, 
                    l_trn, av_trn_age, sd_trn_age, cv_trn, bias)
}
temp<-lapply(1:length(ages), fun)
tbl1<-do.call("rbind", temp)

tbl1 <- tbl1 %>% mutate_all(function(x) ifelse(is.nan(x), NA, x))

#table 2
aged <- sum(tbl1$no_exp)
agre <- sum(tbl1$no_agr)
disgr <- aged - agre
avrg_age <- mean(dat$age_expert) 

bias <- sum((tbl1$no_exp*tbl1$bias)/aged, na.rm = T)
cv <- sum((tbl1$no_exp*tbl1$cv_trn)/aged, na.rm = T)

ape <- sum(abs(((dat$age_trainee/dat$age_expert)*100)-100))/aged

pct_agre <- (agre/aged)*100

tbl2 <- data.frame(aged = aged, agre = agre, disgr = disgr, pct_agre = pct_agre, 
                   avrg_age = avrg_age, bias = bias, cv = cv, ape = ape)



#table 4
dat$month <- month(dat$catchDate)
dat$Q = ceiling(as.numeric(dat$month) / 3)
dat$agr <- ifelse(dat$age_expert == dat$age_trainee, 1, 0)

tbl4 <- matrix(, 3, 4)
for(row in 1:nrow(tbl4)) {
  for(col in 1:ncol(tbl4)) {
    
    a <- dat[dat$Q == col, ]
    
    b <- c(length(a$age_expert), sum(a$agr), length(a$age_expert) - sum(a$agr))
    
    tbl4[row, col] <- b[row]
    
  }
}

tbl4 <- data.frame(Quarter = c("No_Aged", "No_Agreed", "No_disagreed"), tbl4)
names(tbl4) <- c("Quarter", "Q1", "Q2", "Q3", "Q4")


#table 5
tbl5 <- matrix(, length(ages), length(ages))

for(row in 1:nrow(tbl5)) {
  for(col in 1:ncol(tbl5)) {
    
    tbl5[row, col] <- nrow(dat[dat$age_expert == row-1 & dat$age_trainee == col-1, ])
    
  }
}
arem <- tbl5 #for later use
tbl5[tbl5 == 0] <- NA

tbl5 <- rbind(tbl5, colSums(tbl5, na.rm = T))

tbl5 <- data.frame(age = c(ages, "Tot"), tbl5)
names(tbl5) <- c("Age", paste0(ages))

tbl5$tot <- rowSums(tbl5[-1], na.rm = T)


#tbl10
tbl10 <- arem/rowSums(arem)

tbl10[is.nan(tbl10)] <- NA
tbl10[tbl10 == 0] <- NA

tbl10 <- data.frame(age = c(ages), tbl10)
names(tbl10) <- c("Age", paste0(ages))


# table 8
diff_age <- dat$age_trainee - dat$age_expert

xx <- data.frame(table(diff_age))
zz <- data.frame(t(xx$Freq))
names(zz) <- paste0(xx$diff_age)

max <- max(abs(diff_age))
if (max > 5){
diff <- c(-max:max)
} else {
  diff <- c(-5:5)
}
tbl <- data.frame(t(rep(NA, length(diff))))
names(tbl) <- paste0(diff)

tbl8 <- rbind.fill(tbl[-1, ], zz)

tbl8 <- cbind(data.frame(Age_fifference = "No."), tbl8)


```


\thispagestyle{empty}

\vspace*{1cm}

\textbf{\huge Two Reader AquaDots Report}

\vspace*{1.5cm}
\textbf{\large Event `r event[1, ]`}

\vspace*{0.2cm}
This event consists of `r species` otoliths from the areas `r unique(sample$DFUArea)` in the period 
`r range(sample$catchDate)[1]` to `r range(sample$catchDate)[2]`. 

\vspace*{0.2cm}
For this event `r tbl2$aged` otoliths where read.


\vspace*{1.5cm}

\textcolor{gray}{\large Input Information:}\
\begin{itemize}
  \item \textcolor{gray}{\large Year: `r yr`}
  \item \textcolor{gray}{\large Year: `r species`}
  \item \textcolor{gray}{\large Event: `r event[1, ]`}
  \item \textcolor{gray}{\large Expert: `r expert`}
  \item \textcolor{gray}{\large Trainee: `r trainee`}
\end{itemize}
\vspace*{2cm}

\newpage

\tableofcontents

\newpage

\section{Age Reading Results}

The table here summarize the the event, with ages and number read by the trainee and the expert. Together with simple summary statistics.     

```{r table_1, echo=FALSE, results='asis'}

tbl1_out <- signif(tbl1, 3)

tbl1_out %>%
  mutate_all(function(x) ifelse(is.na(x), "", x)) %>%
         kbl(escape = F, longtable = T, booktabs = T, linesep = "", row.names = F,
             caption = "Age reading results by age group",
             col.names = c("Age", "No. Exp", "No. Trn", "No. Agr", "pct Agr",
                           "APE", "Exp", "Trn", "Avrg Age", "ST. DEV", "CV", "Bias"), align = "l") %>%
         add_header_above(c(" " = 6, "length at age" = 2, " " = 4)) %>%
         row_spec(0, bold = FALSE) %>%
         kable_styling(latex_options = c("striped", "hold_position"), font_size = 10, position = "center") %>%
         column_spec(1:12, width = "1cm")




```

\newpage

\section{Trainee vs Expert Results}

Here is shown how well the trainee agrees with the expert

\subsection{Overall Bias}
```{r table_2, echo=FALSE, results='asis'}

tbl2_out <- signif(tbl2, 3)

tbl2_out %>%
     kbl(escape = F, longtable = T, booktabs = T, linesep = "", row.names = F,
         caption = "Trainee vs Expert Results",
         col.names = c("No. Aged", "No. Agreed", "No. Disagree", "pct Agree",
                           "avrg Age", "Bias", "CV", "APE"), align = "l") %>%
         row_spec(0, bold = FALSE) %>%
         kable_styling(latex_options = c("striped", "hold_position"), font_size = 10) %>%
         column_spec(1:8, width = "1.5cm")




```

\subsection{Disagreement by Quarter}
```{r table_4, echo=FALSE, results='asis'}

tbl4_out <- tbl4

tbl4_out$Quarter <- gsub("_", "\\\\_", tbl4_out$Quarter)

tbl4_out %>%
     kbl(escape = F, longtable = T, booktabs = T, linesep = "", row.names = F,
         caption = "Numbers by quarter",
             align = "l") %>%
         row_spec(0, bold = FALSE) %>%
         kable_styling(latex_options = c("striped", "hold_position"), font_size = 10) %>%
         column_spec(1, width = "2cm")%>%
         column_spec(2:5, width = "1.5cm")




```

\subsection{Disagreement by ages}

This table shows the age difference from trainee to the the expert. If the expert has read age "2" and the trainee age 0, the "age difference would be "-2" 
\renewcommand{\arraystretch}{1}
```{r table_8, echo=FALSE, results='asis'}

tbl8_out <- tbl8

tbl8_out[is.na(tbl8_out)] <- 0

tbl8_out %>%
     kbl(escape = F, longtable = T, booktabs = F, row.names = F, 
         caption = "Trainee reader differences from expert reader",
             col.names = c("Age Difference", names(tbl8)[-1]), align = "l") %>%
         row_spec(0, bold = FALSE) %>%
         kable_styling(latex_options = c("striped", "hold_position"), font_size = 10) %>%
         column_spec(1, width = "2cm")




```

\newpage

\section{Trainee vs expert comparison matrix}
Green shaded area is agreement, blue represents under-ageing and brown represents over-ageing by the trainee

\definecolor{beaublue}{rgb}{0.74, 0.83, 0.9}
\definecolor{beige}{rgb}{0.96, 0.96, 0.86}
\definecolor{emerald}{rgb}{0.31, 0.78, 0.47}
\renewcommand{\arraystretch}{2}
```{r table_5, echo=FALSE, results='asis'}
tbl5_out <- tbl5

tbl5_out[is.na(tbl5_out)] <- ""


for (k in 1:(ncol(tbl5_out)-3)) {
  tbl5_out[1:k,k+2] <- cell_spec(tbl5_out[1:k,k+2], bold=T, 
                                 background = "beige")
}

for (k in 2:(ncol(tbl5_out)-2)) {
  tbl5_out[((k+1):nrow(tbl5))-1,k] <- cell_spec(tbl5_out[((k+1):nrow(tbl5))-1,k],
                                                bold=T, background = "beaublue")
}


for (k in 1:(ncol(tbl5_out)-2)) {
  tbl5_out[k,k+1] <- cell_spec(tbl5_out[k, k+1], bold=T, background = "emerald")
}




tbl5_out %>%
         kbl(escape = F, longtable = F, booktabs = F, row.names = F, align = "c") %>%
         kable_styling(latex_options = c("hold_position"), font_size = 10) %>%
         add_header_above(c(" ", "Trainee age" = ncol(tbl5_out)-1)) %>%
         column_spec(1:ncol(tbl5_out), width = "0.75cm")


```

\newpage

\section{Age Reading Error Matrix}
Trainee vs expert reader (Age Reading Error Matrix)

\definecolor{lightgray}{rgb}{0.83, 0.83, 0.83}
\renewcommand{\arraystretch}{2}
```{r table_10, echo=FALSE, results='asis'}
tbl10_out <- signif(tbl10, 3)

tbl10_out[is.na(tbl10_out)] <- ""


for (k in 1:(ncol(tbl10_out)-2)) {
  tbl10_out[k,k+1] <- cell_spec(tbl10_out[k, k+1], bold=T, background = "lightgray")
}




tbl10_out %>%
         kbl(escape = F, longtable = F, booktabs = F, row.names = F, align = "c") %>%
         kable_styling(latex_options = c("hold_position"), font_size = 10) %>%
         add_header_above(c(" ", "Trainee age" = ncol(tbl10_out)-1)) %>%
         column_spec(1:ncol(tbl10_out), width = "0.75cm")


```
\renewcommand{\arraystretch}{1}
\newpage

\section{Table of Disagreed readings}

```{r disagree table, echo=FALSE, results='asis'}

disagr <- dat[dat$agr == 0, 
              c("animalId", "age_expert", "age_trainee", "AQ_expert", "AQ_trainee", "fishLengthMM", "sexCode")]

disagr$AQ_expert <- gsub("_", " ", disagr$AQ_expert)
disagr$AQ_trainee<- gsub("_", " ", disagr$AQ_trainee)

disagr %>%
  kbl(escape = F, longtable = T, booktabs = T, linesep = "", row.names = F,
             caption = "Table of individuals where trainee and expert is in deisagreement",
             col.names = c("Id", "Age Exp", "Age Trn", "AQ Exp", "AQ Trn", "Length", "Sex"), align = "l") %>%
         row_spec(0, bold = FALSE) %>%
         kable_styling(latex_options = c("striped", "hold_position"), font_size = 10) %>%
         column_spec(1:7, width = "2cm")
```



