---
fontsize: 11pt
geometry: top=2cm, bottom=2cm, left=1.5cm, right=1.5cm,headsep=1cm
header-includes:
- \usepackage[utf8]{inputenc}
- \usepackage{fancyhdr}
- \pagestyle{fancy}
- \fancyfoot{}
- \usepackage{ragged2e}
- \linespread{1.15}
- \usepackage{float}
output: pdf_document
fig_caption: yes
keep_tex: yes
---

```{r set_libraries, include=FALSE, warning=FALSE}
#Libraries used in the r code
if (!require(pacman)){
  install.packages("pacman", repos="http://ftp.ussg.iu.edu/CRAN/")
  library(pacman)
}
p_load(kableExtra, sqldf, RODBC, dplyr)

#special for this script
p_load(data.table, mapplots, shapefiles, maptools, ggplot2, plyr, sm, ggrepel, dbscan)

```

```{r set_parameters, include=FALSE}
year <- @paramYear
cruise <- c(@paramCruise)
trip <- @paramTrip
weather <- @paramWeather
gear <- @paramGear
oxygen <- @paramOxygen

invisible(coast <- read.shapefile('europe'))
invisible(dk_eez <- read.shapefile('eez_dk_LandAndSea_2019'))

# Paramters to use in R
# year <- 2022
# cruise <- "Torsk"
# trip <- c(1)
# weather <-""
# gear <- ""
# oxygen <- "" 

# #get shapefiles for the map
# invisible(coast <- read.shapefile('Q:/gis/Dynamisk/GEOdata/BasicLayers/CoastLines/Europe/europe'))
# invisible(dk_eez <- read.shapefile('Q:/gis/Dynamisk/GEOdata/BasicLayers/Boundaries/EEZ/LandAndSea/eez_dk_LandAndSea_2019'))

#format input
weather <- ifelse(weather == "", "No Remarks on the Weather conditions")
gear <-ifelse(gear == "", "No remarks on the Gear performance")
oxygen <- ifelse(oxygen == "", "No remarks on the Oxygen conditions")

## #species of intrest
species <- c("BRS", "RSP", "SIL", "TNG", "TOR", "TBM")
```

```{r get_data, include=FALSE}

#get data from fishline data base

channel <- odbcConnect("FishLineDW")

trips<-sqlQuery(channel,  paste("SELECT    
       [year] 
      ,[trip]
      ,[dateStart]
      ,[dateEnd]
      ,[cruise]
      ,[platform1]
  FROM      Trip
  WHERE     year IN ('",paste0(year,collapse="','"), "') AND
            cruise IN ('",paste0(cruise,collapse="','"), "') AND
            trip IN ('",paste0(trip,collapse="','"), "')
  " ,sep = ""))

samples<-sqlQuery(channel, paste("SELECT    
       [sampleId]
      ,[tripId]
      ,[year]
      ,[cruise]
      ,[trip]
      ,[tripType]
      ,[station]
      ,[stationName]
      ,[gearQuality]
      ,[quarterGearStart]
      ,[dateGearStart]
      ,[dateGearEnd]
      ,[fishingtime]
      ,[latPosStartDec]
      ,[lonPosStartDec]
      ,[latPosEndDec]
      ,[lonPosEndDec]
      ,[distancePositions]
      ,[gearType]
      ,[windSpeed]
      ,[remark]
  FROM      Sample
  WHERE     year IN ('",paste0(year,collapse="','"), "') AND
            cruise IN ('",paste0(cruise,collapse="','"), "') AND
            trip IN ('",paste0(trip,collapse="','"), "') 
  " ,sep = ""))

sp_lst <- sqlQuery(channel, paste("SELECT
       [year]
      ,[cruise]
      ,[trip]
      ,[station]
      ,[speciesCode]
      ,[landingCategory]
      ,[weightSubSample]
      ,[weightTotal]
      ,[numberSubSample]
      ,[numberTotal]
   FROM      SpeciesListRaised
   WHERE     year IN ('",paste0(year,collapse="','"), "') AND 
             cruise IN ('",paste0(cruise,collapse="','"), "') AND
             trip IN ('",paste0(trip,collapse="','"), "') 
   ", sep = ""))

anim_lst <- sqlQuery(channel, paste("SELECT  
       [year]
      ,[cruise]
      ,[trip]
      ,[station]
      ,[speciesCode]
      ,[length]
      ,[lengthMeasureUnit]
      ,[numberSumSamplePerLength]
      ,[numberTotalPerLength]
      ,[weightMean]
   FROM      AnimalRaised
   WHERE     (speciesCode IN ('", paste(species,collapse = "','"),"')) AND
             year IN ('",paste0(year,collapse="','"), "') AND 
             cruise IN ('",paste0(cruise,collapse="','"), "') AND
             trip IN ('",paste0(trip,collapse="','"), "')
                                			       ", sep = ""))

names <- sqlQuery(channel, paste("SELECT   
     [speciesCode] 
    ,[dkName]
    ,[latin]
  FROM   L_Species"
  ,sep = ""))

age <- sqlQuery(channel, paste("SELECT   
       [animalId]
      ,[year]
      ,[cruise]
      ,[trip]
      ,[station]
      ,[speciesCode]
      ,[sexCode]
      ,[number]
      ,[length]
      ,[age]
      ,[genetics]
  FROM     Age
  WHERE    year IN ('",paste0(year,collapse="','"), "') AND 
           cruise IN ('",paste0(cruise,collapse="','"), "') AND
           trip IN ('",paste0(trip,collapse="','"), "') 
           ORDER BY dateGearStart
  ", sep = ""))

animal <- sqlQuery(channel, paste("SELECT     
       [animalId]
      ,[year]
      ,[cruise]
      ,[trip]
      ,[station]
      ,[speciesCode]
      ,[number]
      ,[length]
      ,[weight]
    FROM     animal
    WHERE    year IN ('",paste0(year,collapse="','"), "') AND 
             cruise IN ('",paste0(cruise,collapse="','"), "') AND
             trip IN ('",paste0(trip,collapse="','"), "') AND
             (individNum != 0)
             ORDER BY dateGearStart
    ", sep = ""))

close(channel)


```

```{r format_for_front_page, include=FALSE}

#here the information is formatted to be inserted directly into the later latex part.
ntur <- paste0(nrow(trips[trips$trip %in% trip]), " of ", nrow(trips))
ship <- toString(trips$platform1)

start_date <- as.Date(trips$dateStart)
end_date <- as.Date(trips$dateEnd)

start_time <- format(trips$dateStart, "%H-%M")
end_time <- format(trips$dateEnd, "%H-%M")

quarter <- unique(samples$quarterGearStart)
titl <- ifelse(cruise %like% "KASU", "BITS/KASU", cruise)

```

\thispagestyle{empty}

\vspace*{-2.5cm}

\begin{figure}[H]
        \flushright
        \includegraphics[width=3cm]{logo.png}
\end{figure}

\vspace*{0.5cm}


\textcolor{gray}{\huge DTU Aqua - Cruise report}

\vspace*{4.5cm}

\textbf{\Huge `r titl` - `r quarter`Q - `r year`}\
\vspace*{0.2cm}
\textit{\textbf{\large Trawl Survey}}\
\vspace*{1cm}

\textbf{\Huge `r ship`}

\vspace*{0.2cm}

\textbf{\Huge Denmark}

\vspace*{0.5cm}

\textbf{\large From `r start_date` to `r end_date`}


\vfill

\begin{figure}[H]
        \flushleft
        \includegraphics[width=8cm]{aqua_uk.png}
\end{figure}

\vspace{-3.1cm}
\begin{flushright}
DTU Aqua\\
Kemitorvet, Building 202\\
2800 Kgs. Lyngby\\
Denmark
\end{flushright}


\newpage
\setcounter{page}{1}
<!-- define header and fodder start-->
\fancypagestyle{companypagestyle}{
    \fancyhf{}
    \fancyfoot[L]{
    \parbox[b]{\dimexpr\linewidth\relax}{\vspace{0.8cm}
    {\color{red}\rule{\dimexpr\linewidth\relax}{0.4pt}}\\
    {\footnotesize \color{gray} www.aqua.dtu.dk \hfill DTU AQUA, Kemitorvet, Building 202\\[-0.15cm]
           +45 3588 3300 \hfill 2800 Kgs. Lyngby, Denmark}}
    }
    \fancyfoot[R]{
    \parbox[b]{0cm}{}
    }
}
\pagenumbering{arabic}
\pagestyle{companypagestyle}

\lhead{\footnotesize \color{gray}  CRUISE REPORT, `r titl` `r quarter`Q `r year`}
\rhead{\footnotesize \color{gray} PAGE \thepage\ OF \pageref{LastPage}}


<!-- define header and fodder end -->

\tableofcontents
\newpage

\section{Cruise Summary}

\subsection{General Information}

\begin{table}[H]
\resizebox{0.5\columnwidth}{!}{%
\begin{tabular}{lll}
\toprule
Cruise           &  & `r titl`              \\
Research Vessel  &  & `r ship`              \\
Year and Quarter &  & `r quarter`Q `r year` \\ 
Country          &  & Denmark              \\ \bottomrule
\end{tabular}
}
\end{table}

\subsection{Location and Time}

\begin{table}[H]
\resizebox{0.5\columnwidth}{!}{%
\begin{tabular}{lll}
\toprule
                        & Date            & Time            \\ \hline
Departure               & `r start_date` & `r start_time` \\
Arrival                 & `r end_date`   & `r end_time`   \\ \bottomrule
\end{tabular}
}
\end{table}

\subsection{Participants}
```{r format_crew list, echo=FALSE, results='asis'}
#read in the uploaded csv file with participants and output it to the report
participants <- read.csv2("participants.csv") 

if (2 %in% participants$Leg){ 
ind1 <- range(which(participants$Leg == 1))
ind2 <- range(which(participants$Leg == 2))

participants[1:3] %>%
         kbl(escape = F, longtable = T, booktabs = T, linesep = "", row.names = F,    
             col.names = c("Name", "Institute", "Function tasks"), align = "l") %>%
         row_spec(0, bold = TRUE) %>%
         kable_styling(latex_options = c("striped", "hold_position")) %>%
         column_spec(1:3, width = "5cm") %>%
         pack_rows("Leg 1", ind1[1], ind1[2], latex_gap_space = "2em") %>%
         pack_rows("Leg 2", ind2[1], ind2[2], latex_gap_space = "2em")

} else{
  ind1 <- range(which(participants$Leg == 1))
  participants[1:4] %>%
         kbl(escape = F, longtable = T, booktabs = T, linesep = "", row.names = F,    
             col.names = c("Name", "Institute", "Function tasks", "Leg"), align = "l") %>%
         row_spec(0, bold = TRUE) %>%
         kable_styling(latex_options = c("striped", "hold_position")) %>%
         column_spec(1:4, width = "4cm") %>%
         pack_rows("Leg 1", ind1[1], ind1[2], latex_gap_space = "2em")
}
```

\section{Objectives}

\begin{itemize}
    \item To describe the existence of fish in the waters surrounding Denmark based on their occurrence in scientific trawl./ At beskrive udbredelsen af fisk i farvandende omrking Danmark ved brug af videnskabeligt trawl.
    
    \item To collect biological data regarding age, weight and maturity from subsamples of the catch from selected species./ At indsamle biologisk materiale vedr. alder, vægt og modenhed fra stikprøver fra fangsten af udvalgte arter.
    
    \item Recording of hydrographic data with CTD./Opsamling af hydrografidata med CTD.
\end{itemize}


\section{This Survey}
During the cruise, apart from recording a complete set of factual
information concerning haul information, gear performance, catch
results, hydrographic information etc., the cruise leader keeps a
logbook taking notes about circumstances (unusual gear performance,
special catches, non-conformities etc. during the survey. The haul
summary below is the overview from this logbook.
\subsection{Stations}

`r nrow(samples)` hauls were conducted during the survey. The positions off all hauls are presented in the map in Fig. 1.

\subsection{Weather Conditions}
`r weather`

\subsection{Gear performance}
`r gear`

\subsection{Oxygen Conditions}
`r oxygen`

\newpage
\subsection{Station Map}
```{r station_plot, echo=FALSE, results='asis', cache=FALSE, message=FALSE, warning=FALSE, fig.width=12, fig.height=12}

#define the map outline
#setting coordinates for aspect ration:
asp <- 1/1

xlim <- c(floor(min(samples$lonPosStartDec)),ceiling(max(samples$lonPosStartDec)))

y_l <- ((xlim[2] - xlim[1])/asp)/2
y_max <- ceiling(max(samples$latPosStartDec)/0.5)*0.5

if (y_max - y_l < min(samples$latPosStartDec)){
  
  ylim <- c(y_max - y_l, y_max)
  
} else {
  
  ylim <- c(floor(min(samples$latPosStartDec)/0.5)*0.5,ceiling(max(samples$latPosStartDec)/0.5)*0.5)
  xlim <- c(floor(min(samples$lonPosStartDec)),ceiling(max(samples$lonPosStartDec)))
  
}

samples <- samples[order(samples$dateGearStart), ]
samples$st_no <- 1:nrow(samples)
valid <- samples[samples$gearQuality == "V", ]
invalid <- samples[samples$gearQuality != "V", ]

#make the plot using the mapplots pakage
p1 <- basemap(xlim, ylim, main = paste0(cruise, "-", year, " tur ", ntur))+
              draw.shape(coast, col="cornsilk")+
              draw.shape(dk_eez, col="transparent", border = "red")+
              draw.rect()+
              points(invalid$lonPosStartDec, invalid$latPosStartDec, col="black", 
                     pch = 15 + samples$trip, cex = 1.5)
              points(valid$lonPosStartDec, valid$latPosStartDec, col="green", 
                     pch = 15 + samples$trip, cex = 1.2)
              pointLabel(x=samples$lonPosStartDec,  y= samples$latPosStartDec,
                         labels=as.character(samples$st_no),
                         cex=1,offset=-1, allowSmallOverlap = FALSE)
              legend("bottomright", legend= c("Valid ", "Invalid"),
                  col=c("green", "black"), pch = 16, cex=1.5, bg='white')
             
              
```
Figur 1. Plot af stationer.
\newpage
\subsection{Catch Overview}
```{r format_catch list, echo=FALSE, results='asis'}
#format information to directly be inputed to latex table

species2 <- c("Total Catch", species)
fun <- function(jj) {
  
  sp <- species2[jj]
  
  if (sp == "Total Catch"){
    sps <- unique(sp_lst$speciesCode)
  } else {
    sps <- sp
  }
    
  w_s <- as.character(round(sum(sp_lst[sp_lst$speciesCode %in% sps, "weightSubSample"]), digits = 1))
  w_t <- as.character(round(sum(sp_lst[sp_lst$speciesCode  %in% sps, "weightTotal"]), digits = 1))
  
  n_s <- as.character(round(sum(sp_lst[sp_lst$speciesCode  %in% sps, "numberSubSample"]), digits = 0))
  n_t <- as.character(round(sum(sp_lst[sp_lst$speciesCode  %in% sps, "numberTotal"]), digits = 0))
  
  sam <- nrow(animal[animal$speciesCode %in% sps, ])
  gen <- nrow(age[age$speciesCode %in% sps & age$genetics == 1, ])
  
  out <- cbind(sp, w_s, w_t, n_s, n_t, sam, gen)
}
temp<-lapply(1:length(species2), fun) #function to get data and run the loop/function
sp_overview <- data.frame(do.call("rbind", temp))

 print(sp_overview %>%
         kbl(escape = F, longtable = T, caption = "Sample Overview", 
             booktabs = T, linesep = "", row.names = F,    
             col.names = c(" ", "Sub sampled [kg]", "Total [kg]", "Sub sampled [Nr.]", "Total [Nr.]",
                           "Individuals collected", "Genetics Sampled"), align = "l") %>%
         row_spec(0, bold = TRUE) %>%
         kable_styling(latex_options = c("striped", "hold_position")) %>%
         pack_rows("selected species", 2, 7, latex_gap_space = "1.5em") %>%
         column_spec(1, width = "3.5cm") %>%
         column_spec(2:7, width = "2.2cm")
       )

```

\newpage
\subsubsection{Length destribution}
```{r COD length frequency,echo=FALSE, results='asis', cache=FALSE, message=FALSE, warning=FALSE, fig.width=12, fig.height=7}

for (jjj in species) {
  
  dat <- setDT(anim_lst[anim_lst$speciesCode == jjj, ])  

  if (nrow(dat) == 0)
    next
  
  #create headder
  cat(paste0("\n\n### ",  jjj, "\n"))

  # get the frequency of age by length
  freq <- dat[ ,. (frequency = sum(numberTotalPerLength)),
               by = (length)]

  x_range <- round_any(seq(range(freq$length)[1], range(freq$length)[2], length.out = 5), 10)
  # Stacked barplot with multiple groups
  p2 <- ggplot(freq, aes(x=length, y=frequency)) +
          geom_bar(stat="identity")+
          theme_bw() +
          labs(x = "Længde [mm]", y = "Frekvens [antal")+
          ggtitle(paste0("Længdefrekvens af ", jjj))+
          theme(plot.title = element_text(hjust = 0.5))+
          scale_x_continuous(breaks=x_range)+
          theme(axis.title = element_text(size=16),
                plot.title = element_text(size=16),
                axis.text.x = element_text(angle = 45, hjust=1, size=14),
                axis.text.y = element_text(size=14))

  plot(p2)
}
```


\newpage
\subsection{Species Cought}
\setcounter{table}{0}
The total catch per species for the while cruise is presented in the table below.
 \vspace{0.2cm}
 
```{r format_species list, echo=FALSE, results='asis'}

#aggregate the raised species list, to make an overview of species couhgt 
setDT(sp_lst)
sp <- sp_lst[ ,. (number = round(sum(numberTotal, na.rm = T), digits = 0), 
                  weight = round(sum(weightTotal, na.rm = T), digits = 1)),
              by = .(speciesCode, trip)]


sp[sp$number == 0, "number"] <- NA

sp2 <- merge(names, sp, by = "speciesCode")

#exclude the litter rows
sp2 <- sp2[!sp2$speciesCode %in% c("AF1", "AF2", "AF3", "AF4", "AF5"), ]

#make table in loop, one table pr trip
for (i in trip) {
  
  dat <- sp2[sp2$trip == i, ]
  
  #format which column we would like, and their order 
  dat <- dat[ , c("latin", "dkName", "number", "weight")]
  
  print(dat %>%
         kbl(escape = F, longtable = T, booktabs = T, linesep = "", 
             row.names = F, caption = paste0("Arter fanget på tur ", i),   
             col.names = c("Latinsk navn", "Dansk navn", "Antal", "Vægt (kg)")
             , align = "lllrr") %>%
         row_spec(0, bold = TRUE) %>%
         kable_styling(latex_options = c("striped", "hold_position")) %>%
         column_spec(1, width = "4.5cm") %>%
         column_spec(2, width = "4cm") %>%
         column_spec(3:4, width = "2cm"))

 
  
  
}
```
 