---
fontsize: 11pt
geometry: top=2cm, bottom=2cm, left=1.5cm, right=1.5cm,headsep=1cm
header-includes:
- \usepackage[utf8]{inputenc}
- \usepackage{fancyhdr}
- \pagestyle{fancy}
- \fancyfoot{}
- \usepackage{ragged2e}
- \linespread{1.15}
- \usepackage{float}
- \usepackage{lastpage}
output: pdf_document
---

```{r set_libraries, include=FALSE, warning=FALSE}

#Libraries used in the r code
if (!require(pacman)){
  install.packages("pacman", repos="http://ftp.ussg.iu.edu/CRAN/")
  library(pacman)
}
p_load(kableExtra, sqldf, RODBC, dplyr)

#special for this script
p_load(data.table, mapplots, maptools, shapefiles, ggplot2, lubridate, 
       gridExtra, plyr)

```

```{r set_parameters, include=FALSE, error = TRUE}

  year <- @paramYear # mandatory
  cruise <- @paramCruise # mandatory
  exDate <- @paramExDate
  weather <- @paramWeather
  gear <- @paramGear
  oxygen <- @paramOxygen
  cruise_no <- @paramCruise_no
 
  stations <- readRDS(paste0("<dfad-path>/logbog_", cruise, "_", year, ".rds")) 
  
  invisible(coast <- read.shapefile('europe'))
  invisible(dk_eez <- read.shapefile('eez_dk_LandAndSea_2019'))

  
  # year <- 2021
  # cruise <- "BITS-2"
  # exDate <- "2022-11-04"
  # weather <-""
  # gear <- ""
  # oxygen <- ""
  # cruise_no <- 2
  # 
  # stations <- readRDS(paste0("Q:/dfad/users/jostou/home/FishLineRapporter/Togter/Togtrapport/logbog_", cruise, "_", year, ".rds"))
  # 
  # #get shapefiles for the map
  # invisible(coast <- read.shapefile('Q:/gis/Dynamisk/GEOdata/BasicLayers/CoastLines/Europe/europe'))
  # invisible(dk_eez <- read.shapefile('Q:/gis/Dynamisk/GEOdata/BasicLayers/Boundaries/EEZ/LandAndSea/eez_dk_LandAndSea_2019'))



weather <- ifelse(weather == "", "No remarks on the Weather conditions", weather)
gear <-ifelse(gear == "", "No further remarks on the Gear performance", gear)
oxygen <- ifelse(oxygen == "", "No remarks on the Oxygen conditions", oxygen)
exDate <- ifelse(exDate == "", "No exchange", exDate)

```


```{r get_data, include=FALSE}

#get data from fishline data base

channel <- odbcConnect("FishLine")

cruises <- sqlQuery(channel, paste("SELECT  cruiseId, year, cruise, participants,
                                            summary
                                   FROM     Cruise
                                   WHERE    year = (",year,")
                                			      ", sep = ""))

cruiseId <- cruises[cruises$cruise == cruise,  "cruiseId"]

trips <- sqlQuery(channel, paste("SELECT    cruiseId, trip, tripId, tripType, dateStart, dateEnd
                                   FROM     Trip
                                   WHERE    cruiseId = (",cruiseId,")
                                   		      ", sep = ""))

close(channel)

channel <- odbcConnect("FishLineDW")

samples <- sqlQuery(channel, paste("SELECT   year, cruise, trip, tripType, station,
                                             quarterGearStart AS quarter, stationName, haulType, 
                                             dateGearStart AS haul_start, dateGearEnd AS haul_end,
                                             latPosStartDec, lonPosStartDec, 
                                             latPosEndDec, lonPosEndDec,
                                             fishingtime, netOpening, otterBoardDist,
                                             wingSpread, gearRemark, dfuArea, 
                                             statisticalRectangle, statisticalRectangleEnd,
                                             gearType, gearQuality, hydroStnRef,
                                             temperatureBot, salinityBot, oxygenBot
                                   FROM      Sample
                                   WHERE     year = (",year,") AND
                                  	  	     cruise = ('",cruise,"') 
                                			       ", sep = ""))

sp_lst <- sqlQuery(channel, paste("SELECT    year, cruise, trip, tripType, station, dfuArea, 
                                             dateGearStart AS date, quarterGearStart AS quarter,
                                             speciesCode, numberTotal, weightTotal
                                   FROM      SpeciesListRaised
                                   WHERE     year = (",year,") AND
                                  	  	     cruise = ('",cruise,"') 
                                			       ", sep = ""))

cod_lst <- sqlQuery(channel, paste("SELECT    year, cruise, trip, tripType, station, dfuArea, 
                                             speciesCode, length, numberTotalPerLength
                                   FROM      AnimalRaised
                                   WHERE     year = (",year,") AND
                                  	  	     cruise = ('",cruise,"') AND 
                                  	  	     speciesCode = ('","TOR","') 
                                			       ", sep = ""))

names <- sqlQuery(channel, paste("SELECT   speciesCode, ukName, dkName, latin
                                    FROM   L_Species"
                                           ,sep = ""))

ages <- sqlQuery(channel, paste("SELECT    animalId, year, cruise, trip, tripType, station, dfuArea, 
                                          speciesCode, age, genetics
                                FROM      Age
                                WHERE     year = (",year,") AND
                              	  	      cruise = ('",cruise,"')
                              		        ", sep = ""))

close(channel)


```

```{r format_for_front_page, include=FALSE}

#here the information is formatted to be inserted directly into the later latex part.
ship <- "DANA"

start_date <- as.Date(trips$dateStart)
end_date <- as.Date(trips$dateEnd)

start_time <- format(trips$dateStart, "%H-%M")
end_time <- format(trips$dateEnd, "%H-%M")

quarter <- unique(samples$quarter)
titl <- ifelse(cruise %like% "BITS", "BITS", "cruise")
```

\thispagestyle{empty}

\vspace*{-2.5cm}

\begin{figure}[H]
        \flushright
        \includegraphics[width=3cm]{logo.png}
\end{figure}

\vspace*{0.5cm}


\textcolor{gray}{\huge DTU Aqua - Cruise report}

\vspace*{4.5cm}

\textbf{\Huge `r titl` `r quarter`Q `r year`}\
\vspace*{0.2cm}
\textit{\textbf{\large Baltic International Trawl Survey}}\
\vspace*{1cm}

\textbf{\Huge `r ship`}

\vspace*{0.2cm}

\textbf{\Huge Denmark}

\vspace*{0.5cm}

\textit{\textbf{\large Cruise no. `r cruise_no`}}\
\textbf{\large From `r start_date` to `r end_date`}


\vfill

\begin{figure}[H]
        \flushleft
        \includegraphics[width=8cm]{aqua_uk.png}
\end{figure}

\vspace{-3.1cm}
\begin{flushright}
DTU Aqua\\
Kemitorvet, Building 202\\
2800 Kgs. Lyngby\\
Denmark
\end{flushright}


\newpage
\setcounter{page}{1}
<!-- define header and fodder start-->
\fancypagestyle{companypagestyle}{
    \fancyhf{}
    \fancyfoot[L]{
    \parbox[b]{\dimexpr\linewidth\relax}{\vspace{0.8cm}
    {\color{red}\rule{\dimexpr\linewidth\relax}{0.4pt}}\\
    {\footnotesize \color{gray} www.aqua.dtu.dk \hfill DTU AQUA, Kemitorvet, Building 202\\[-0.15cm]
           +45 3588 3300 \hfill 2800 Kgs. Lyngby, Denmark}}
    }
    \fancyfoot[R]{
    \parbox[b]{0cm}{}
    }
}
\pagenumbering{arabic}
\pagestyle{companypagestyle}

\lhead{\footnotesize \color{gray}  CRUISE REPORT, `r titl` `r quarter`Q `r year`}
\rhead{\footnotesize \color{gray} PAGE \thepage\ OF \pageref{LastPage}}


<!-- define header and fodder end -->

\tableofcontents
\newpage

\section{Cruise Summary}

\subsection{General Information}

\begin{table}[H]
\resizebox{0.5\columnwidth}{!}{%
\begin{tabular}{lll}
\toprule
Cruise           &  & `r titl`              \\
Cruise Number    &  & `r cruise_no`        \\
Research Vessel  &  & `r ship`              \\
Year and Quarter &  & `r quarter`Q `r year` \\ 
Country          &  & Denmark              \\ \bottomrule
\end{tabular}
}
\end{table}

\subsection{Location and Time}

\begin{table}[H]
\resizebox{0.5\columnwidth}{!}{%
\begin{tabular}{lll}
\toprule
                        & Date            & Time            \\ \hline
Departure               & `r start_date` & `r start_time` \\
Arrival                 & `r end_date`   & `r end_time`   \\
Staff and crew Exchange & `r exDate`      &               \\ \bottomrule
\end{tabular}
}
\end{table}

\subsection{Participants}
```{r format_crew list, echo=FALSE, results='asis'}
#read in the uploaded csv file with participants and output it to the report
participants <- read.csv2("participants.csv") 

if (2 %in% participants$Leg){ 
ind1 <- range(which(participants$Leg == 1))
ind2 <- range(which(participants$Leg == 2))

participants[2:4] %>%
         kbl(escape = F, longtable = T, booktabs = T, linesep = "", row.names = F,    
             col.names = c("Name", "Institute", "Function tasks"), align = "l") %>%
         row_spec(0, bold = TRUE) %>%
         kable_styling(latex_options = c("striped", "hold_position")) %>%
         column_spec(1:3, width = "5cm") %>%
         pack_rows("Leg 1", ind1[1], ind1[2], latex_gap_space = "2em") %>%
         pack_rows("Leg 2", ind2[1], ind2[2], latex_gap_space = "2em")

} else
  ind1 <- range(which(participants$Leg == 1))
  participants[2:4] %>%
         kbl(escape = F, longtable = T, booktabs = T, linesep = "", row.names = F,    
             col.names = c("Name", "Institute", "Function tasks"), align = "l") %>%
         row_spec(0, bold = TRUE) %>%
         kable_styling(latex_options = c("striped", "hold_position")) %>%
         column_spec(1:3, width = "5cm") %>%
         pack_rows("Leg 1", ind1[1], ind1[2], latex_gap_space = "2em")

```

\section{Introduction}
The Danish research vessel Dana R/V was built in 1980-81 and is a versatile multipurpose vessel with
five large laboratories and 38 cabins. The Baltic cod stock has been monitored annually since 1982
through bottom trawl surveys carried out by most countries surrounding the Baltic. The national research
vessels have each surveyed part of the area with some overlap in coverage and applied a depth stratified
sampling design. However, different gears and design were applied and in 1985 ICES established a
Study Group on Young Fish Surveys in the Baltic in order to standardize the surveys. After agreement a
common standard trawl gear and standard sampling procedures were implemented in 2000 resulting in
the consistrent coverage of the western and central Baltic Sea.

To calibrate the national surveys from before 2000 with the TV3 gear used from 2000, a set of conversion
factors are produced by making comparative hauls. The work with standardizing gear and creating
conversion factors for old data was done under the EU project ISDBITS and gear specifications and
conversion factors can be found in the report (ISDBITS 2001).
The type of trawl is called “TV3L” with 930 meshes in the opening. The design and construction of the
standard trawls are given in ICES (1997) and can also be found in the BITS manual (Anon. 2000). Until
November 2007 Denmark was still using the rock hopper gear on hard fishing ground but since 2008 only
the standard TV3L has been used.

The BITS is conducted as a depth-stratified survey. The strata are based on Sub divisions and depth
layers. Each year the necessary stations are randomly selected before the beginning of the international
trawl surveys from a list of clear haul data. These stations are a stratified random selected sub-sample of
the possible trawl tracks. The standard haul is a 30 minute haul with a towing speed of 3 knots. Trawling
is only taking place during daylight, defined as the time between 15 minutes past sunrise until 15 minutes
before sunset.

\section{Objectives}

\subsection{Daytime}
\begin{itemize}
    \item To estimate the abundance and the year class strength of the Baltic cod and flatfish stocks in
ICES Sub-divisions 21-32. The 4st quarter survey is together with the spring survey the Danish
contribution to the "Baltic International Trawl Survey"(BITS) and takes place mainly in Sub-division
25 and 26. The main goal of the surveys is to provide the Baltic assessment working group fishery
independent data to use for assessment in ICES the working group in April. Furthermore, all fish
species are species determination, measured and weighted.

    
    \item To measure temperature, salinity and oxygen at the fishing location. The measurements are
conducted with a CTD. Calibration of the CTD is conducted before the survey.
    
    \item To take individual samples of cod to analyses of age determination, sex, weight and liver condition.
Data is used to produce maturity ogive, mean weights per age and condition which is used for
Eastern Baltic stock assessment.
\end{itemize}

\subsection{Nighttime}
\begin{itemize}
    \item To investigate the abundance and distribution of zooplankton in the central Baltic Sea. The analysis
is conducted with a bongo net were the stations are allocated in accordance to the Kiel grid net
covering most of SD 25. Trawling speed is 3 kn and the three nets are 150, 335 and 500 µm in cod
end.

    \item To investigate the distribution of juvenile cod caught in a IKMT.
    
    \item To catch live zooplankton with a WP2 net.
\end{itemize}

\section{This Survey}
During the cruise, apart from recording a complete set of factual information concerning haul information,
gear performance, catch results, hydrographic information etc., the cruise leader keeps a logbook taking
notes about circumstances (unusual gear performance, special catches, non-conformities etc. during the
survey. The haul summary below is the overview from this logbook

\subsection{Weather Conditions}

`r weather`


\subsection{Gear performance}
The gear performance is monitored during any trawl station. All relevant parameters describing the gear geometry during the fishing 
is logged to verify that the observed trawl geometry values are within the defined ranges for acceptance.

`r gear`

\subsection{Oxygen Conditions}
`r oxygen`

\newpage
\subsection{Stations}

An overview of he Trawl and Bongo stations are shown in figure 1, 2 and 3, followed by a haul summary of all gears used onboard. 

\subsubsection{Haul Summary}
```{r format hauls, echo=FALSE, results='asis'}
stations$Redskab <- trimws(stations$Redskab) #trim whitespace

n_valid <- nrow(samples[samples$gearQuality == "V", ])
n_no_oxy <- nrow(samples[samples$haulType == "N",  ])
n_invalid <- nrow(samples[samples$gearQuality == "I", ])
n_planed <- nrow(samples) - n_invalid

n_ctd <- nrow(stations[stations$Redskab == "SEA" & stations$Status != "Fail",])
n_bongo <- nrow(stations[stations$Redskab == "BONGO" & stations$Status != "Fail",])
n_wp2 <- nrow(stations[stations$Redskab == "WP2" & stations$Status != "Fail",])
n_apt <- nrow(stations[stations$Redskab == "apt" & stations$Status != "Fail",])


bongo <- stations[!is.na(stations$Status) & stations$Redskab == "BONGO" & stations$Status != "Fail", ]

```

\begin{table}[H]
\resizebox{0.5\columnwidth}{!}{%
\begin{tabular}{@{}lll@{}}
\toprule
               &                     & Number \\ \midrule
Trawl activity &                     &   \\
               & Planed Trawl Hauls  & `r n_planed`  \\
               & Trawl Related CTD   & `r n_planed`  \\
               & Valid Trawl Hauls   & `r n_valid`  \\
               & Invalid Trawl Hauls & `r n_invalid`  \\
               & No Oxygen Stations  & `r n_no_oxy`  \\ \midrule
Other activity &                     &   \\
               & CTD Hauls           & `r n_ctd - n_planed`  \\
               & Bongo Hauls         & `r n_bongo`  \\
               & WP2 Hauls           & `r n_wp2`  \\
               & Aptstein Hauls      & `r n_apt`  \\ \bottomrule
\end{tabular}
}
\end{table}

\subsubsection{Station Map}
```{r arrow_plot, echo=FALSE, results='asis', cache=FALSE, message=FALSE, warning=FALSE, fig.width=10, fig.height=10}

a <- data.frame(Starttid = samples$haul_start, lon = samples$lonPosStartDec, lat = samples$latPosStartDec)
a$Redskab <- "Trawl"


#define the map outline
#setting coordinates for aspect ration:
asp <- 1/1

xlim <- c(floor(min(a$lon)),ceiling(max(a$lon)))

y_l <- ((xlim[2] - xlim[1])/asp)/2
y_max <- ceiling(max(a$lat)/0.5)*0.5

if (y_max - y_l < min(a$lat)){
  
  ylim <- c(y_max - y_l, y_max)
  
} else {
  
  ylim <- c(floor(min(a$lat)/0.5)*0.5,ceiling(max(a$lat)/0.5)*0.5)
  xlim <- c(floor(min(a$lon)),ceiling(max(a$lon)))
  
}



if(exDate != "No exchange"){
b <- data.frame(Starttid = as.POSIXct(exDate), lon = 14.69, lat = 55.10, Redskab = "Harb")
} else {
  b <- data.frame(Starttid = NA, lon = NA, lat = NA, Redskab = "Harb")
}

q <- rbind(a, b, bongo[, c("Starttid", "lon", "lat", "Redskab")])

q$Redskab <- as.numeric(as.factor(q$Redskab))
q <- q[order(q$Starttid), ]

q$lon2 <- c(q$lon[-1], 12.59)
q$lat2 <- c(q$lat[-1], 55.69)

p1 <- basemap(xlim, ylim, main = paste0(titl, " ",  quarter, "Q ", year))+
  draw.shape(coast, col="cornsilk")+
  draw.shape(dk_eez, col="transparent", border = "red")+
  draw.rect()+
  points(q$lon, q$lat, col= 1 + q$Redskab, pch = 16, cex = 1.5)
  legend("bottomright", legend=c("Bongo", "Trawl ", "Harbour"),
         col= 1 + unique(q$Redskab), pch = 16, cex=1.5, bg='white')
  arrows(q$lon, q$lat, q$lon2, q$lat2, length = 0.075)
```
Figure 1. Survey map with the route drawn in.

```{r station_plot, echo=FALSE, results='asis', cache=FALSE, message=FALSE, warning=FALSE, fig.width=12, fig.height=12}

# no oxygen/ invalid hauls
invalid <- samples[samples$gearQuality != "V" & (samples$gearType == "TV3" | samples$gearType == "OTB"), ]

no_oxy <- samples[samples$haulType == "N",  ]

#make the plot using the mapplots pakage
p1 <- basemap(xlim, ylim, main = paste0(titl, " ",  quarter, "Q ", year))+
              draw.shape(coast, col="cornsilk")+
              draw.shape(dk_eez, col="transparent", border = "red")+
              draw.rect()+
              points(samples$lonPosStartDec, samples$latPosStartDec, col="green", pch = 16, cex = 1.5)
              points(invalid$lonPosStartDec, invalid$latPosStartDec, col="black", pch = 16, cex = 1.5)
              points(no_oxy$lonPosStartDec, no_oxy$latPosStartDec, col="red", pch = 16, cex = 1.5)
              pointLabel(x=samples$lonPosStartDec,  y= samples$latPosStartDec,
                         labels=as.character(samples$stationName),
                         cex=1,offset=-1, allowSmallOverlap = FALSE)
              legend("bottomright", legend=c("Valid ", "No Oxygen", "Invalid"),
                  col=c("green", "red", "black"), pch = 16, cex=1.5, bg='white')

```
Figure 2. Survey map with trawl stations. Indicated is the status of the station and weather oxygen was present at the bottom

```{r bongo_plot, echo=FALSE, results='asis', cache=FALSE, message=FALSE, warning=FALSE, fig.width=12, fig.height=12}                            
#make BONGO map
invalid <- stations[stations$Redskab == "BONGO" & stations$Status == "Fail",]
wp2 <- stations[stations$Redskab == "WP2" & stations$Status !="Fail",]
apt <- stations[(stations$Redskab =="apt" | stations$Redskab == "appi") & stations$Status !="Fail",] 

p2 <- basemap(xlim, ylim, main = paste0(titl, " ",  quarter, "Q ", year))+
              draw.shape(coast, col="cornsilk")+
              draw.shape(dk_eez, col="transparent", border = "red")+
              draw.rect()+
              points(bongo$lon, bongo$lat, col="green", pch = 16, cex = 1.5)
              points(invalid$lon, invalid$lat, col="black", pch = 16, cex = 1.5)
              points(apt$lon, apt$lat, col="orange", pch = 0, cex = 1.5)
              points(wp2$lon, wp2$lat, col="blue", pch = 2, cex = 1.5)
              text(bongo$lon, bongo$lat, bongo$gearNo, pos=3,cex=0.6,offset=0.5)
              legend("bottomright", legend=c("Bongo", "Apt", "WP2", "Invalid"),
                  col=c("green", "orange", "blue", "black"), pch = c(16, 0, 2, 16), cex=1.5, bg='white')

```
Figure 3: Survey map with bongo, Aptstein and WP2 stations, as well as station status.


\newpage
\section{Catch}

```{r format_catch list, echo=FALSE, results='asis'}

#format information to directly be inputed to latex table
total_w <- as.character(round(sum(sp_lst$weightTotal), digits = 1))
total_n <- as.character(round(sum(sp_lst$numberTotal), digits = 0))

cod_w <- as.character(round(sum(sp_lst[sp_lst$speciesCode == "TOR", "weightTotal"]), digits = 1))
cod_n <- as.character(round(sum(sp_lst[sp_lst$speciesCode == "TOR", "numberTotal"]), digits = 0))

plaice_w <- as.character(round(sum(sp_lst[sp_lst$speciesCode == "RSP", "weightTotal"]), digits = 1))
plaice_n <- as.character(round(sum(sp_lst[sp_lst$speciesCode == "RSP", "numberTotal"]), digits = 0))

sole_w <- as.character(round(sum(sp_lst[sp_lst$speciesCode == "TNG", "weightTotal"]), digits = 1))
sole_n <- as.character(round(sum(sp_lst[sp_lst$speciesCode == "TNG", "numberTotal"]), digits = 0))

# format age info for table
age <- ages[!is.na(ages$age), ]
age_t <- nrow(age)
age_cod <- nrow(age[age$speciesCode == "TOR", ])
age_plaice <- nrow(age[age$speciesCode == "RSP", ])
age_sole <- nrow(age[age$speciesCode == "TNG", ])

gen <- ages[ages$genetics == 1, ]
gen_t <- nrow(gen)
gen_cod <- nrow(gen[gen$speciesCode == "TOR", ])
gen_plaice <- nrow(gen[gen$speciesCode == "RSP", ])
gen_sole <- nrow(gen[gen$speciesCode == "TNG", ])
```

\subsection{Overview}
The total catch of all species, cod, plaice and sole are presented below. followed by a length frequency plot for COD caught shown in figure 4.

 \vspace{0.2cm}

\begin{table}[H]
\begin{center}
\resizebox{0.9\columnwidth}{!}{%
\begin{tabular}{lrrrr}
\toprule
            & Weight (kg)  & Number       & Aged            & Genetics sampled    \\ \midrule
Total Catch & `r total_w`  & `r total_n`  & `r age_t`       & `r gen_t`           \\
Cod         & `r cod_w`    & `r cod_n`    & `r age_cod`     & `r gen_cod`         \\
Plaice      & `r plaice_w` & `r plaice_n` & `r age_plaice`  & `r gen_plaice`      \\
Sole        & `r sole_w`   & `r sole_n`   & `r age_sole`    & `r gen_sole`        \\ \bottomrule
\end{tabular}
}
\end{center}
\end{table}

\vspace*{0.5cm}

```{r COD length frequency,echo=FALSE, results='asis', cache=FALSE, message=FALSE, warning=FALSE, fig.width=12, fig.height=7}
area <- unique(sp_lst$dfuArea)

for (j in area[1:length(area)]) {

dat <- setDT(cod_lst[cod_lst$dfuArea == j, ])  

# get the frequency of age by length
freq <- dat[ ,. (frequency = sum(numberTotalPerLength)),
             by = (length)]

x_range <- round_any(seq(range(freq$length)[1], range(freq$length)[2], length.out = 5), 10)
# Stacked barplot with multiple groups
p3 <- ggplot(freq, aes(x=length, y=frequency)) +
        geom_bar(stat="identity")+
        theme_bw() +
        labs(x = "Length [mm]", y = "Frequency in Nr")+
        ggtitle(paste0("cod - Area ", j, " - Frequency of Length"))+
        theme(plot.title = element_text(hjust = 0.5))+
        scale_x_continuous(breaks=x_range)+
        theme(axis.title = element_text(size=16),
              plot.title = element_text(size=16),
              axis.text.x = element_text(angle = 45, hjust=1, size=14),
              axis.text.y = element_text(size=14))

plot(p3)
}
```
Figure 4. Length frequency of the COD caught in the respective areas.
\newpage
\subsection{Species Cought}
\setcounter{table}{0}
The total catch per species per ICES area are presented in table 1-`r length(unique(sp_lst$dfuArea))`.
 \vspace{0.2cm}

```{r format_species list, echo=FALSE, results='asis'}

#aggregate the raised species list, to make an overview of species couhgt 
setDT(sp_lst)

sp <- sp_lst[ ,. (number = round(sum(numberTotal, na.rm = T), digits = 0), 
                  weight = round(sum(weightTotal, na.rm = T), digits = 1)),
              by = .(speciesCode, dfuArea)]


sp[sp$number == 0, "number"] <- NA

sp2 <- merge(names, sp, by = "speciesCode")

#exclude the litter rows
sp2 <- sp2[!sp2$speciesCode %in% c("AF1", "AF2", "AF3", "AF4", "AF5"), ]

#make table in loop, one table pr area
area <- unique(sp2$dfuArea)

for (i in area[1:length(area)]) {
  
  dat <- sp2[sp2$dfuArea == i, ]
  
  #format which column we would like, and their order 
  dat <- dat[ , c("latin", "ukName", "dkName", "number", "weight")]
  
  print(dat %>%
         kbl(escape = F, longtable = T, booktabs = T, linesep = "", 
             row.names = F, caption = paste0("Species Caught in area ", i),   
             col.names = c("Latin name", "English name", "Danish name", "Number", "Weight (kg)")
             , align = "lllrr") %>%
         row_spec(0, bold = TRUE) %>%
         kable_styling(latex_options = c("striped", "hold_position")) %>%
         column_spec(1, width = "4.5cm") %>%
         column_spec(2:3, width = "4cm") %>%
         column_spec(4:5, width = "2cm"))

 
  
  
}
```




