---
fontsize: 11pt
geometry: top=2cm, bottom=2cm, left=1.5cm, right=1.5cm,headsep=1cm
header-includes:
- \usepackage[utf8]{inputenc}
- \usepackage{fancyhdr}
- \pagestyle{fancy}
- \fancyfoot{}
- \usepackage{ragged2e}
- \linespread{1.15}
- \usepackage{float}
- \usepackage{lastpage}
output: pdf_document
---

```{r set_libraries, include=FALSE, warning=FALSE}

#Libraries used in the r code
if (!require(pacman)){
  install.packages("pacman", repos="http://ftp.ussg.iu.edu/CRAN/")
  library(pacman)
}
p_load(kableExtra, sqldf, RODBC, dplyr)

#special for this script
p_load(data.table, mapplots, shapefiles, officer)

```


```{r set_parameters, include=FALSE}

year <- @paramYear # mandatory
cruise <- @paramCruise # mandatory
exDate <- @paramExDate
weather <- @paramWeather
gear <- @paramGear
oxygen <- @paramOxygen

# year <- 2020 
# cruise <- "KASU-2"
# exDate <- "2020-11-06"
# weather <-""
# gear <- ""
# oxygen <- ""
```

```{r get_data, include=FALSE}

channel <- odbcConnect("FishLine")

cruises <- sqlQuery(channel, paste("SELECT  cruiseId, year, cruise, participants,
                                            summary
                                   FROM     Cruise
                                   WHERE    year = (",year,")
                                			      ", sep = ""))

cruiseID <- cruises[cruises$cruise == cruise,  "cruiseId"]

trips <- sqlQuery(channel, paste("SELECT    cruiseId, trip, tripId, tripType, dateStart, dateEnd
                                   FROM     Trip
                                   WHERE    cruiseId = (",cruiseID,")
                                   		      ", sep = ""))

close(channel)


tripID <- trips$tripId
species <- c("TOR", "RSP", "TNG")

channel <- odbcConnect("FishLineDW")

samples <- sqlQuery(channel, paste("SELECT   year, cruise, trip, tripType, station,
                                             quarterGearStart AS quarter, stationName, 
                                             dateGearStart AS haul_start, dateGearEnd AS haul_end,
                                             latPosStartDec, lonPosStartDec, 
                                             latPosEndDec, lonPosEndDec,
                                             fishingtime, gearRemark, dfuArea, 
                                             statisticalRectangle, statisticalRectangleEnd,
                                             gearType, gearQuality, windDirection, windSpeed,
                                             temperatureBot, salinityBot, oxygenBot
                                   FROM      Sample
                                   WHERE     year = (",year,") AND
                                  	  	     cruise = ('",cruise,"') 
                                			       ", sep = ""))

sp_lst <- sqlQuery(channel, paste("SELECT    year, cruise, trip, tripType, station, dfuArea, 
                                             dateGearStart AS date, quarterGearStart AS quarter,
                                             speciesCode, numberTotal, weightTotal
                                   FROM      SpeciesListRaised
                                   WHERE     year = (",year,") AND
                                  	  	     cruise = ('",cruise,"') 
                                			       ", sep = ""))

animal <- sqlQuery(channel, paste("SELECT     animalId, year, 
                                              cruise, trip, station, dfuArea AS area, speciesCode,
                                              number, weight
                                     FROM     animal
                                     WHERE    (speciesCode IN ('", paste(species,collapse = "','"),"')) AND 
                                              year = (",year,") AND
                                              cruise = ('",cruise,"')
                                        ORDER BY dateGearStart
                                			        ", sep = ""))

names <- sqlQuery(channel, paste("SELECT   speciesCode, ukName, dkName, latin
                                    FROM   L_Species"
                                           ,sep = ""))

close(channel)


```

```{r format_for_front_page, include=FALSE}

ship <- ifelse(cruise %like% "KASU", "Havfisken", "DANA")

start_date <- as.Date(trips$dateStart)
end_date <- as.Date(trips$dateEnd)

start_time <- format(trips$dateStart, "%H-%M")
end_time <- format(trips$dateEnd, "%H-%M")

cruises <- cruises[order(cruises$cruiseId), ]
cruise_no <- which(cruises$cruise == cruise)

quarter <- unique(samples$quarter)
titl <- ifelse(cruise %like% "KASU", "BITS/KASU", "BITS")
```

\thispagestyle{empty}

\vspace*{-2.5cm}

\begin{figure}[H]
        \flushright
        \includegraphics[width=3cm]{logo.png}
\end{figure}

\vspace*{0.5cm}


\textcolor{gray}{\huge DTU Aqua - Cruise report}

\vspace*{4.5cm}

\textbf{\Huge `r titl` `r quarter`Q `r year`}\

\vspace*{1cm}

\textbf{\Huge `r ship`}

\vspace*{0.3cm}

\textbf{\Huge Denmark}

\vspace*{0.5cm}

\textbf{\large Cruise no. `r cruise_no`}\

\textbf{\large From `r start_date` to `r end_date`}


\vfill

\begin{figure}[H]
        \flushleft
        \includegraphics[width=8cm]{aqua_uk.png}
\end{figure}

\vspace{-3.1cm}
\begin{flushright}
DTU Aqua\\
Kemitorvet, Building 202\\
2800 Kgs. Lyngby\\
Denmark
\end{flushright}


\newpage
\setcounter{page}{1}
<!-- define header and fodder start-->
\fancypagestyle{companypagestyle}{
    \fancyhf{}
    \fancyfoot[L]{
    \parbox[b]{\dimexpr\linewidth\relax}{\vspace{0.8cm}
    {\color{red}\rule{\dimexpr\linewidth\relax}{0.4pt}}\\
    {\footnotesize \color{gray} www.aqua.dtu.dk \hfill DTU AQUA, Kemitorvet, Building 202\\[-0.15cm]
           +45 3588 3300 \hfill 2800 Kgs. Lyngby, Denmark}}
    }
    \fancyfoot[R]{
    \parbox[b]{0cm}{}
    }
}
\pagenumbering{arabic}
\pagestyle{companypagestyle}

\lhead{\footnotesize \color{gray}  CRUISE REPORT, `r titl` `r quarter`Q `r year`}
\rhead{\footnotesize \color{gray} PAGE \thepage\ OF \pageref{LastPage}}


<!-- define header and fodder end -->

\tableofcontents
\newpage

\section{Cruise Summary}

\subsection{General Information}

\begin{table}[H]
\resizebox{0.5\columnwidth}{!}{%
\begin{tabular}{lll}
\toprule
Cruise           &  & `r titl`              \\
Cruise Number    &  & `r cruise_no`        \\
Research Vessel  &  & `r ship`              \\
Year and Quarter &  & `r quarter`Q `r year` \\ 
Country          &  & Denmark              \\ \bottomrule
\end{tabular}
}
\end{table}

\subsection{Location and Time}

\begin{table}[H]
\resizebox{0.5\columnwidth}{!}{%
\begin{tabular}{lll}
\toprule
                        & Date            & Time            \\ \hline
Departure               & `r start_date` & `r start_time` \\
Arrival                 & `r end_date`   & `r end_time`   \\
Staff and crew Exchange & `r exDate`      &               \\ \bottomrule
\end{tabular}
}
\end{table}

\subsection{Participants}
```{r format_crew list, echo=FALSE, results='asis'}

participants <- read.csv2("participants.csv") 

ind1 <- range(which(participants$Leg == 1))
ind2 <- range(which(participants$Leg == 2))

participants[2:4] %>%
         kbl(escape = F, longtable = T, booktabs = T, linesep = "", row.names = F,    
             col.names = c("Name", "Institute", "Function tasks"), align = "l") %>%
         row_spec(0, bold = TRUE) %>%
         kable_styling(latex_options = c("striped", "hold_position")) %>%
         column_spec(1:3, width = "5cm") %>%
         pack_rows("Leg 1", ind1[1], ind1[2], latex_gap_space = "2em") %>%
         pack_rows("Leg 2", ind2[1], ind2[2], latex_gap_space = "2em")


```


\section{Objectives}
```{r format_objective, include=FALSE}

if (titl == "BITS/KASU"){
  objective1 <- "To describe the existence of fish in Kattegat, Øresund, Storebælt, Lillebælt and the Western Baltic based on their occurrence in test trawl. The fishery in ICES araes 22 and 23 are a part of the IBTS survey./ At beskrive udbredelsen af fisk i Kattegat, Øresund, Storebælt, Lillebælt og den Vest-lige Østersø ud fra forekomst i forsøgstrawl. Fiskeriet i område 22 og 23 er en del af BITS."
  
  objective2 <- "To collect biological data regarding age, weight and maturity from subsamples of the catch from selected species./ At indsamle biologisk materiale vedr. alder, vægt og modenhed fra stikprøver fra fangsten af udvalgte arter."
  
  objective3 <- "Recording of hydrographic data with CTD./Opsamling af hydrografidata med CTD."
} else{
  
  objective1 <- ""
  
  objective2 <- ""
  
  objective3 <- ""
}
```

\begin{itemize}
    \item `r objective1`
    
    \item `r objective2`
    
    \item `r objective3`
\end{itemize}


\section{This Survey}

\subsection{Stations}

`r nrow(samples)` hauls were conducted during the survey. The positions off all hauls are presented in the map in Fig. 1.

\subsection{Weather Conditions}
`r weather`

\subsection{Gear performance}
`r gear`

\subsection{Oxygen Conditions}
`r oxygen`

\subsection{Station Map}

```{r station_plot, echo=FALSE, results='asis', cache=FALSE, message=FALSE, warning=FALSE, fig.width=12, fig.height=12}

invisible(coast <- read.shapefile('europe'))
invisible(dk_eez <- read.shapefile('eez_dk_LandAndSea_2019'))

if (titl == "BITS/KASU"){
ylim <- c(54,57.8)
xlim <- c(9.5,13.5)

}

samples$legend <- ifelse(samples$gearType == "TV3" & samples$gearQuality == "V", "Valid TV3", "Invalid")
samples$legend <- ifelse(samples$gearType == "OTB" & samples$gearQuality == "V", "Valid OTB", samples$legend)

samples$legend <- as.factor(samples$legend)

p1 <- basemap(xlim, ylim, main = paste0(titl, " ",  quarter, "Q ", year))+
              draw.shape(coast, col="cornsilk")+
              draw.shape(dk_eez, col="transparent", border = "red")+
              draw.rect()+
              points(samples$lonPosStartDec, samples$latPosStartDec, col=samples$legend, pch = 16, cex = 1.5)+
              text(samples$lonPosStartDec, samples$latPosStartDec, samples$stationName, pos=2)
legend("bottomright", legend=unique(samples$legend),
                    col=unique(samples$legend), pch=16, cex = 1.5)
```

\newpage
\section{catch}

```{r format_catch list, echo=FALSE, results='asis'}

total_w <- as.character(round(sum(sp_lst$weightTotal), digits = 1))
total_n <- as.character(round(sum(sp_lst$numberTotal), digits = 0))

cod_w <- as.character(round(sum(sp_lst[sp_lst$speciesCode == "TOR", "weightTotal"]), digits = 1))
cod_n <- as.character(round(sum(sp_lst[sp_lst$speciesCode == "TOR", "numberTotal"]), digits = 0))

plaice_w <- as.character(round(sum(sp_lst[sp_lst$speciesCode == "RSP", "weightTotal"]), digits = 1))
plaice_n <- as.character(round(sum(sp_lst[sp_lst$speciesCode == "RSP", "numberTotal"]), digits = 0))

sole_w <- as.character(round(sum(sp_lst[sp_lst$speciesCode == "TNG", "weightTotal"]), digits = 1))
sole_n <- as.character(round(sum(sp_lst[sp_lst$speciesCode == "TNG", "numberTotal"]), digits = 0))
```

The total catch of all species, cod, plaice and sole are presented below.
The total catch per species per ICES area are presented in table 1-`r length(unique(sp_lst$dfuArea))`.

 \vspace{0.2cm}

\begin{table}[H]
\resizebox{0.5\columnwidth}{!}{%
\begin{tabular}{lrr}
\toprule
            & Weight (kg)   & Number        \\ \midrule
Total Catch & `r total_w`  & `r total_n`  \\
Cod         & `r cod_w`    & `r cod_n`    \\
Plaice      & `r plaice_w` & `r plaice_n` \\
Sole        & `r sole_w`   & `r sole_n`   \\ \bottomrule
\end{tabular}
}
\end{table}

\setcounter{table}{0}

```{r format_species list, echo=FALSE, results='asis'}

setDT(sp_lst)

sp <- sp_lst[ ,. (number = round(sum(numberTotal, na.rm = T), digits = 0), 
                  weight = round(sum(weightTotal, na.rm = T), digits = 1)),
              by = .(speciesCode, dfuArea)]


sp[sp$number == 0, "number"] <- NA

sp2 <- merge(names, sp, by = "speciesCode")

sp2 <- sp2[!sp2$speciesCode %in% c("AF1", "AF2", "AF3", "AF4", "AF5"), ]


area <- unique(sp2$dfuArea)

for (i in area[1:length(area)]) {
  
  dat <- sp2[sp2$dfuArea == i, ]
  
  dat <- dat[ , c("latin", "ukName", "dkName", "number", "weight")]
  
  print(dat %>%
         kbl(escape = F, longtable = T, booktabs = T, linesep = "", 
             row.names = F, caption = paste0("Species Caught in area ", i),   
             col.names = c("Latin name", "English name", "Danish name", "Number", "Weight (kg)")
             , align = "lllrr") %>%
         row_spec(0, bold = TRUE) %>%
         kable_styling(latex_options = c("striped", "hold_position")) %>%
         column_spec(1, width = "4.5cm") %>%
         column_spec(2:3, width = "4cm") %>%
         column_spec(4:5, width = "2cm"))

 
  
  
}
```








