---
fontsize: 11pt
geometry: top=2cm, bottom=2cm, left=1.5cm, right=1.5cm,headsep=1cm
header-includes:
- \usepackage[utf8]{inputenc}
- \usepackage{fancyhdr}
- \pagestyle{fancy}
- \fancyfoot{}
- \usepackage{ragged2e}
- \linespread{1.15}
- \usepackage{float}
- \usepackage{lastpage}
output: pdf_document
---

```{r set_libraries, include=FALSE, warning=FALSE}

#Libraries used in the r code
if (!require(pacman)){
  install.packages("pacman", repos="http://ftp.ussg.iu.edu/CRAN/")
  library(pacman)
}
p_load(kableExtra, sqldf, RODBC, dplyr)

#special for this script
p_load(data.table, mapplots, shapefiles, maptools, ggplot2, plyr)

```


```{r set_parameters, include=FALSE}

# year <- @paramYear # mandatory
# cruise <- @paramCruise # mandatory
# exDate <- @paramExDate
# weather <- @paramWeather
# gear <- @paramGear
# oxygen <- @paramOxygen

year <- 2021
cruise <- "KASU-2"
exDate <- "2020-11-06"
weather <-""
gear <- ""
oxygen <- ""

weather <- ifelse(weather == "", "No Remarks on the Weather conditions")
gear <-ifelse(gear == "", "No remarks on the Gear performance")
oxygen <- ifelse(oxygen == "", "No remarks on the Oxygen conditions")

#get shapefiles for the map
invisible(coast <- read.shapefile('Q:/gis/Dynamisk/GEOdata/BasicLayers/CoastLines/Europe/europe'))
invisible(dk_eez <- read.shapefile('Q:/gis/Dynamisk/GEOdata/BasicLayers/Boundaries/EEZ/LandAndSea/eez_dk_LandAndSea_2019'))

# invisible(coast <- read.shapefile('europe'))
# invisible(dk_eez <- read.shapefile('eez_dk_LandAndSea_2019'))
```

```{r get_data, include=FALSE}

#get data from fishline data base

channel <- odbcConnect("FishLine")

cruises <- sqlQuery(channel, paste("SELECT  cruiseId, year, cruise, participants,
                                            summary
                                   FROM     Cruise
                                   WHERE    year = (",year,")
                                			      ", sep = ""))

cruiseID <- cruises[cruises$cruise == cruise,  "cruiseId"]

trips <- sqlQuery(channel, paste("SELECT    cruiseId, trip, tripId, tripType, dateStart, dateEnd
                                   FROM     Trip
                                   WHERE    cruiseId = (",cruiseID,")
                                   		      ", sep = ""))

close(channel)

channel <- odbcConnect("FishLineDW")

samples <- sqlQuery(channel, paste("SELECT   year, cruise, trip, tripType, station,
                                             quarterGearStart AS quarter, stationName, 
                                             dateGearStart AS haul_start, dateGearEnd AS haul_end,
                                             latPosStartDec, lonPosStartDec, 
                                             latPosEndDec, lonPosEndDec,
                                             fishingtime, gearRemark, dfuArea, 
                                             statisticalRectangle, statisticalRectangleEnd,
                                             gearType, gearQuality, windDirection, windSpeed,
                                             temperatureBot, salinityBot, oxygenBot
                                   FROM      Sample
                                   WHERE     year = (",year,") AND
                                  	  	     cruise = ('",cruise,"') 
                                			       ", sep = ""))

sp_lst <- sqlQuery(channel, paste("SELECT    year, cruise, trip, tripType, station, dfuArea, 
                                             dateGearStart AS date, quarterGearStart AS quarter,
                                             speciesCode, numberTotal, weightTotal
                                   FROM      SpeciesListRaised
                                   WHERE     year = (",year,") AND
                                  	  	     cruise = ('",cruise,"') 
                                			       ", sep = ""))

cod_lst <- sqlQuery(channel, paste("SELECT   year, cruise, trip, tripType, station, dfuArea, 
                                             speciesCode, length, numberTotalPerLength
                                   FROM      AnimalRaised
                                   WHERE     year = (",year,") AND
                                  	  	     cruise = ('",cruise,"') AND 
                                  	  	     speciesCode = ('","TOR","') 
                                			       ", sep = ""))

names <- sqlQuery(channel, paste("SELECT   speciesCode, ukName, dkName, latin
                                    FROM   L_Species"
                                           ,sep = ""))

ages <- sqlQuery(channel, paste("SELECT    animalId, year, cruise, trip, tripType, station, dfuArea, 
                                          speciesCode, age, genetics
                                FROM      Age
                                WHERE     year = (",year,") AND
                              	  	      cruise = ('",cruise,"')
                              		        ", sep = ""))

close(channel)

```

```{r format_for_front_page, include=FALSE}

#here the information is formatted to be inserted directly into the later latex part.
ship <- ifelse(cruise %like% "KASU", "Havfisken", "DANA")

start_date <- as.Date(trips$dateStart)
end_date <- as.Date(trips$dateEnd)

start_time <- format(trips$dateStart, "%H-%M")
end_time <- format(trips$dateEnd, "%H-%M")

cruises <- cruises[order(cruises$cruiseId), ]
cruise_no <- which(cruises$cruise == cruise)

quarter <- unique(samples$quarter)
titl <- ifelse(cruise %like% "KASU", "BITS/KASU", "BITS")
```

\thispagestyle{empty}

\vspace*{-2.5cm}

\begin{figure}[H]
        \flushright
        \includegraphics[width=3cm]{logo.png}
\end{figure}

\vspace*{0.5cm}


\textcolor{gray}{\huge DTU Aqua - Cruise report}

\vspace*{4.5cm}

\textbf{\Huge `r titl` `r quarter`Q `r year`}\
\vspace*{0.2cm}
\textit{\textbf{\large Baltic International Trawl Survey}}\
\vspace*{1cm}

\textbf{\Huge `r ship`}

\vspace*{0.2cm}

\textbf{\Huge Denmark}

\vspace*{0.5cm}

\textbf{\large Cruise no. `r cruise_no`}\
\textbf{\large From `r start_date` to `r end_date`}


\vfill

\begin{figure}[H]
        \flushleft
        \includegraphics[width=8cm]{aqua_uk.png}
\end{figure}

\vspace{-3.1cm}
\begin{flushright}
DTU Aqua\\
Kemitorvet, Building 202\\
2800 Kgs. Lyngby\\
Denmark
\end{flushright}


\newpage
\setcounter{page}{1}
<!-- define header and fodder start-->
\fancypagestyle{companypagestyle}{
    \fancyhf{}
    \fancyfoot[L]{
    \parbox[b]{\dimexpr\linewidth\relax}{\vspace{0.8cm}
    {\color{red}\rule{\dimexpr\linewidth\relax}{0.4pt}}\\
    {\footnotesize \color{gray} www.aqua.dtu.dk \hfill DTU AQUA, Kemitorvet, Building 202\\[-0.15cm]
           +45 3588 3300 \hfill 2800 Kgs. Lyngby, Denmark}}
    }
    \fancyfoot[R]{
    \parbox[b]{0cm}{}
    }
}
\pagenumbering{arabic}
\pagestyle{companypagestyle}

\lhead{\footnotesize \color{gray}  CRUISE REPORT, `r titl` `r quarter`Q `r year`}
\rhead{\footnotesize \color{gray} PAGE \thepage\ OF \pageref{LastPage}}


<!-- define header and fodder end -->

\tableofcontents
\newpage

\section{Cruise Summary}

\subsection{General Information}

\begin{table}[H]
\resizebox{0.5\columnwidth}{!}{%
\begin{tabular}{lll}
\toprule
Cruise           &  & `r titl`              \\
Cruise Number    &  & `r cruise_no`        \\
Research Vessel  &  & `r ship`              \\
Year and Quarter &  & `r quarter`Q `r year` \\ 
Country          &  & Denmark              \\ \bottomrule
\end{tabular}
}
\end{table}

\subsection{Location and Time}

\begin{table}[H]
\resizebox{0.5\columnwidth}{!}{%
\begin{tabular}{lll}
\toprule
                        & Date            & Time            \\ \hline
Departure               & `r start_date` & `r start_time` \\
Arrival                 & `r end_date`   & `r end_time`   \\
Staff and crew Exchange & `r exDate`      &               \\ \bottomrule
\end{tabular}
}
\end{table}

\subsection{Participants}
```{r format_crew list, echo=FALSE, results='asis'}
#read in the uploaded csv file with participants and output it to the report
participants <- read.csv2("participants.csv") 

ind1 <- range(which(participants$Leg == 1))
ind2 <- range(which(participants$Leg == 2))

participants[2:4] %>%
         kbl(escape = F, longtable = T, booktabs = T, linesep = "", row.names = F,    
             col.names = c("Name", "Institute", "Function tasks"), align = "l") %>%
         row_spec(0, bold = TRUE) %>%
         kable_styling(latex_options = c("striped", "hold_position")) %>%
         column_spec(1:3, width = "5cm") %>%
         pack_rows("Leg 1", ind1[1], ind1[2], latex_gap_space = "2em") %>%
         pack_rows("Leg 2", ind2[1], ind2[2], latex_gap_space = "2em")


```


\section{Objectives}

\begin{itemize}
    \item To describe the existence of fish in Kattegat, Øresund, Storebælt, Lillebælt and the Western Baltic based on their occurrence in test trawl. The fishery in ICES araes 22 and 23 are a part of the IBTS survey./ At beskrive udbredelsen af fisk i Kattegat, Øresund, Storebælt, Lillebælt og den Vest-lige Østersø ud fra forekomst i forsøgstrawl. Fiskeriet i område 22 og 23 er en del af BITS.
    
    \item To collect biological data regarding age, weight and maturity from subsamples of the catch from selected species./ At indsamle biologisk materiale vedr. alder, vægt og modenhed fra stikprøver fra fangsten af udvalgte arter.
    
    \item Recording of hydrographic data with CTD./Opsamling af hydrografidata med CTD.
\end{itemize}


\section{This Survey}
During the cruise, apart from recording a complete set of factual
information concerning haul information, gear performance, catch
results, hydrographic information etc., the cruise leader keeps a
logbook taking notes about circumstances (unusual gear performance,
special catches, non-conformities etc. during the survey. The haul
summary below is the overview from this logbook.
\subsection{Stations}

`r nrow(samples)` hauls were conducted during the survey. The positions off all hauls are presented in the map in Fig. 1.

\subsection{Weather Conditions}
`r weather`

\subsection{Gear performance}
`r gear`

\subsection{Oxygen Conditions}
`r oxygen`

\subsection{Station Map}

```{r station_plot, echo=FALSE, results='asis', cache=FALSE, message=FALSE, warning=FALSE, fig.width=12, fig.height=12}

#define the map outline
if (titl == "BITS/KASU"){
ylim <- c(54,57.8)
xlim <- c(9.5,13.5)

}

invalid <- samples[samples$gearQuality != "V", ]

#make the plot using the mapplots pakage
p1 <- basemap(xlim, ylim, main = paste0(titl, " ",  quarter, "Q ", year))+
              draw.shape(coast, col="cornsilk")+
              draw.shape(dk_eez, col="transparent", border = "red")+
              draw.rect()+
              points(samples$lonPosStartDec, samples$latPosStartDec, col="green", pch = 16, cex = 1.5)
              points(invalid$lonPosStartDec, invalid$latPosStartDec, col="black", pch = 16, cex = 1.5)
              pointLabel(x=samples$lonPosStartDec,  y= samples$latPosStartDec,
                         labels=as.character(samples$stationName),
                         cex=1,offset=-1, allowSmallOverlap = FALSE)
              legend("bottomright", legend=c(paste0("Valid ", unique(samples$gearType)), "Invalid"),
                  col=c("green", "black"), pch = 16, cex=1.5, bg='white')
```
Figure 1. Survey map with trawl stations.
\newpage
\section{Catch}

```{r format_catch list, echo=FALSE, results='asis'}

#format information to directly be inputed to latex table
total_w <- as.character(round(sum(sp_lst$weightTotal), digits = 1))
total_n <- as.character(round(sum(sp_lst$numberTotal), digits = 0))

cod_w <- as.character(round(sum(sp_lst[sp_lst$speciesCode == "TOR", "weightTotal"]), digits = 1))
cod_n <- as.character(round(sum(sp_lst[sp_lst$speciesCode == "TOR", "numberTotal"]), digits = 0))

plaice_w <- as.character(round(sum(sp_lst[sp_lst$speciesCode == "RSP", "weightTotal"]), digits = 1))
plaice_n <- as.character(round(sum(sp_lst[sp_lst$speciesCode == "RSP", "numberTotal"]), digits = 0))

sole_w <- as.character(round(sum(sp_lst[sp_lst$speciesCode == "TNG", "weightTotal"]), digits = 1))
sole_n <- as.character(round(sum(sp_lst[sp_lst$speciesCode == "TNG", "numberTotal"]), digits = 0))

area <- unique(sp_lst$dfuArea)
a <- chartr("123456789", "ABCDEFGHI", c(1:length(area)))


# format age info for table
age <- ages[!is.na(ages$age), ]
age_t <- nrow(age)
age_cod <- nrow(age[age$speciesCode == "TOR", ])
age_plaice <- nrow(age[age$speciesCode == "RSP", ])
age_sole <- nrow(age[age$speciesCode == "TNG", ])

gen <- ages[ages$genetics == 1, ]
gen_t <- nrow(gen)
gen_cod <- nrow(gen[gen$speciesCode == "TOR", ])
gen_plaice <- nrow(gen[gen$speciesCode == "RSP", ])
gen_sole <- nrow(gen[gen$speciesCode == "TNG", ])

```

\subsection{Overview}
The total catch of all species, cod, plaice and sole are presented below. followed by a length frequency plot for COD caught in each area shown in figure 2 `r a`.

 \vspace{0.2cm}

\begin{table}[H]
\begin{center}
\resizebox{0.9\columnwidth}{!}{%
\begin{tabular}{lrrrr}
\toprule
            & Weight (kg)  & Number       & Aged            & Genetics sampled    \\ \midrule
Total Catch & `r total_w`  & `r total_n`  & `r age_t`       & `r gen_t`           \\
Cod         & `r cod_w`    & `r cod_n`    & `r age_cod`     & `r gen_cod`         \\
Plaice      & `r plaice_w` & `r plaice_n` & `r age_plaice`  & `r gen_plaice`      \\
Sole        & `r sole_w`   & `r sole_n`   & `r age_sole`    & `r gen_sole`        \\ \bottomrule
\end{tabular}
}
\end{center}
\end{table}

\vspace*{0.5cm}

```{r COD length frequency,echo=FALSE, results='asis', cache=FALSE, message=FALSE, warning=FALSE, fig.width=12, fig.height=7}
jj = 0
for (j in area[1:length(area)]) {
jj = jj + 1

dat <- setDT(cod_lst[cod_lst$dfuArea == j, ])  

# get the frequency of age by length
freq <- dat[ ,. (frequency = sum(numberTotalPerLength)),
             by = (length)]

x_range <- round_any(seq(range(freq$length)[1], range(freq$length)[2], length.out = 5), 10)
# Stacked barplot with multiple groups
p2 <- ggplot(freq, aes(x=length, y=frequency)) +
        geom_bar(stat="identity")+
        theme_bw() +
        labs(x = "Length [mm]", y = "Frequency in Nr")+
        ggtitle(paste0(a[jj],", cod - Area ", j, " - Histogram of Length by Age"))+
        theme(plot.title = element_text(hjust = 0.5))+
        scale_x_continuous(breaks=x_range)+
        theme(axis.title = element_text(size=16),
              plot.title = element_text(size=16),
               axis.text.x = element_text(angle = 45, hjust=1, size=14),
               axis.text.y = element_text(size=14))

plot(p2)
}
```
Figure 2 `r a`. Length frequency of the COD caught in the respective areas.
\newpage
\subsection{Species Cought}
\setcounter{table}{0}
The total catch per species per ICES area are presented in table 1-`r length(unique(sp_lst$dfuArea))`.
 \vspace{0.2cm}
 
```{r format_species list, echo=FALSE, results='asis'}

#aggregate the raised species list, to make an overview of species couhgt 
setDT(sp_lst)

sp <- sp_lst[ ,. (number = round(sum(numberTotal, na.rm = T), digits = 0), 
                  weight = round(sum(weightTotal, na.rm = T), digits = 1)),
              by = .(speciesCode, dfuArea)]


sp[sp$number == 0, "number"] <- NA

sp2 <- merge(names, sp, by = "speciesCode")

#exclude the litter rows
sp2 <- sp2[!sp2$speciesCode %in% c("AF1", "AF2", "AF3", "AF4", "AF5"), ]

#make table in loop, one table pr area
area <- unique(sp2$dfuArea)

for (i in area[1:length(area)]) {
  
  dat <- sp2[sp2$dfuArea == i, ]
  
  #format which column we would like, and their order 
  dat <- dat[ , c("latin", "ukName", "dkName", "number", "weight")]
  
  print(dat %>%
         kbl(escape = F, longtable = T, booktabs = T, linesep = "", 
             row.names = F, caption = paste0("Species Caught in area ", i),   
             col.names = c("Latin name", "English name", "Danish name", "Number", "Weight (kg)")
             , align = "lllrr") %>%
         row_spec(0, bold = TRUE) %>%
         kable_styling(latex_options = c("striped", "hold_position")) %>%
         column_spec(1, width = "4.5cm") %>%
         column_spec(2:3, width = "4cm") %>%
         column_spec(4:5, width = "2cm"))

 
  
  
}
```








