---
fontsize: 11pt
geometry: top=2cm, bottom=2cm, left=1.5cm, right=1.5cm,headsep=1cm
header-includes:
- \usepackage[utf8]{inputenc}
- \usepackage{fancyhdr}
- \pagestyle{fancy}
- \fancyfoot{}
- \usepackage{ragged2e}
- \linespread{1.15}
- \usepackage{float}
output: pdf_document
fig_caption: yes
keep_tex: yes
---

```{r set_libraries, include=FALSE, warning=FALSE}
#Libraries used in the r code
if (!require(pacman)){
  install.packages("pacman", repos="http://ftp.ussg.iu.edu/CRAN/")
  library(pacman)
}
p_load(kableExtra, sqldf, RODBC, dplyr)

#special for this script
p_load(data.table, mapplots, shapefiles, maptools, ggplot2, plyr, sm, ggrepel, dbscan)

```

```{r set_parameters, include=FALSE}
year <- @paramYear
cruise <- c(@paramCruise)
trip <- @paramTrip

invisible(coast <- read.shapefile('europe'))
invisible(dk_eez <- read.shapefile('eez_dk_LandAndSea_2019'))

# Paramters to use in R
# year <- 2022
# cruise <- "BITS-2"
# trip <- c(1)
# 
# #get shapefiles for the map
# invisible(coast <- read.shapefile('Q:/gis/Dynamisk/GEOdata/BasicLayers/CoastLines/Europe/europe'))
# invisible(dk_eez <- read.shapefile('Q:/gis/Dynamisk/GEOdata/BasicLayers/Boundaries/EEZ/LandAndSea/eez_dk_LandAndSea_2019'))
# 


## #species of intrest
species <- c("BRS", "RSP", "SIL", "TNG", "TOR", "TBM")
```

```{r get_data, include=FALSE}

#get data from fishline data base

channel <- odbcConnect("FishLineDW")

trips<-sqlQuery(channel,  paste("SELECT    
       [year] 
      ,[trip]
      ,[cruise]
      ,[platform1]
  FROM      Trip
  WHERE     year IN ('",paste0(year,collapse="','"), "') AND
            cruise IN ('",paste0(cruise,collapse="','"), "') AND
            trip IN ('",paste0(trip,collapse="','"), "')
  " ,sep = ""))

samples<-sqlQuery(channel, paste("SELECT    
       [sampleId]
      ,[tripId]
      ,[year]
      ,[cruise]
      ,[trip]
      ,[tripType]
      ,[station]
      ,[stationName]
      ,[gearQuality]
      ,[dateGearStart]
      ,[dateGearEnd]
      ,[fishingtime]
      ,[latPosStartDec]
      ,[lonPosStartDec]
      ,[latPosEndDec]
      ,[lonPosEndDec]
      ,[distancePositions]
      ,[gearType]
      ,[windSpeed]
      ,[remark]
  FROM      Sample
  WHERE     year IN ('",paste0(year,collapse="','"), "') AND
            cruise IN ('",paste0(cruise,collapse="','"), "') AND
            trip IN ('",paste0(trip,collapse="','"), "') 
  " ,sep = ""))

sp_lst <- sqlQuery(channel, paste("SELECT
       [year]
      ,[cruise]
      ,[trip]
      ,[station]
      ,[speciesCode]
      ,[landingCategory]
      ,[weightSubSample]
      ,[weightTotal]
      ,[numberSubSample]
      ,[numberTotal]
   FROM      SpeciesListRaised
   WHERE     year IN ('",paste0(year,collapse="','"), "') AND 
             cruise IN ('",paste0(cruise,collapse="','"), "') AND
             trip IN ('",paste0(trip,collapse="','"), "') 
   ", sep = ""))

anim_lst <- sqlQuery(channel, paste("SELECT  
       [year]
      ,[cruise]
      ,[trip]
      ,[station]
      ,[speciesCode]
      ,[length]
      ,[lengthMeasureUnit]
      ,[numberSumSamplePerLength]
      ,[numberTotalPerLength]
      ,[weightMean]
   FROM      AnimalRaised
   WHERE     (speciesCode IN ('", paste(species,collapse = "','"),"')) AND
             year IN ('",paste0(year,collapse="','"), "') AND 
             cruise IN ('",paste0(cruise,collapse="','"), "') AND
             trip IN ('",paste0(trip,collapse="','"), "')
                                			       ", sep = ""))

names <- sqlQuery(channel, paste("SELECT   
     [speciesCode] 
    ,[dkName]
    ,[latin]
  FROM   L_Species"
  ,sep = ""))

age <- sqlQuery(channel, paste("SELECT   
       [animalId]
      ,[year]
      ,[cruise]
      ,[trip]
      ,[station]
      ,[speciesCode]
      ,[sexCode]
      ,[number]
      ,[length]
      ,[age]
      ,[genetics]
  FROM     Age
  WHERE    year IN ('",paste0(year,collapse="','"), "') AND 
           cruise IN ('",paste0(cruise,collapse="','"), "') AND
           trip IN ('",paste0(trip,collapse="','"), "') 
           ORDER BY dateGearStart
  ", sep = ""))

animal <- sqlQuery(channel, paste("SELECT     
       [animalId]
      ,[year]
      ,[cruise]
      ,[trip]
      ,[station]
      ,[speciesCode]
      ,[number]
      ,[length]
      ,[weight]
    FROM     animal
    WHERE    year IN ('",paste0(year,collapse="','"), "') AND 
             cruise IN ('",paste0(cruise,collapse="','"), "') AND
             trip IN ('",paste0(trip,collapse="','"), "') AND
             (individNum != 0)
             ORDER BY dateGearStart
    ", sep = ""))

close(channel)


```

```{r format_for_front_page, include=FALSE}

#here the information is formatted to be inserted directly into the later latex part.
ntur <- paste0(nrow(trips[trips$trip %in% trip]), " af ", nrow(trips))
skib <- toString(trips$platform1)


```

\thispagestyle{empty}

\vspace*{1cm} 

\textbf{\huge Data Kvalitets tjek af togtet `r cruise`, i `r year`}

\vspace{1cm}   

\textbf{\LARGE  Antal Ture Valgt: `r ntur`}\
\textbf{\LARGE  Skib(e): `r skib`}\

\vspace{2cm}

\textcolor{gray}{\LARGE  The following was used as input}\

\textcolor{gray}{\LARGE  years: `r unique(year)`}\

\textcolor{gray}{\LARGE  cruise: `r unique(cruise)`}\

\textcolor{gray}{\LARGE  Trip: `r unique(trip)`}\


\newpage

\tableofcontents

\newpage

\section{Stationer}

Denne section giver et overblik over antallet af stationer, hvor de er og tjekker for inkonsistens i træk tid, distance og hastighed. 

\subsection{Kort over tsationer}

```{r station_plot, echo=FALSE, results='asis', cache=FALSE, message=FALSE, warning=FALSE, fig.width=12, fig.height=12}

#define the map outline
#setting coordinates for aspect ration:
asp <- 1/1

xlim <- c(floor(min(samples$lonPosStartDec)),ceiling(max(samples$lonPosStartDec)))

y_l <- ((xlim[2] - xlim[1])/asp)/2
y_max <- ceiling(max(samples$latPosStartDec)/0.5)*0.5

if (y_max - y_l < min(samples$latPosStartDec)){
  
  ylim <- c(y_max - y_l, y_max)
  
} else {
  
  ylim <- c(floor(min(samples$latPosStartDec)/0.5)*0.5,ceiling(max(samples$latPosStartDec)/0.5)*0.5)
  xlim <- c(floor(min(samples$lonPosStartDec)),ceiling(max(samples$lonPosStartDec)))
  
}


valid <- samples[samples$gearQuality == "V", ]
invalid <- samples[samples$gearQuality != "V", ]

#make the plot using the mapplots pakage
p1 <- basemap(xlim, ylim, main = paste0(cruise, "-", year, " tur ", ntur))+
              draw.shape(coast, col="cornsilk")+
              draw.shape(dk_eez, col="transparent", border = "red")+
              draw.rect()+
              points(invalid$lonPosStartDec, invalid$latPosStartDec, col="black", 
                     pch = 15 + samples$trip, cex = 1.5)
              points(valid$lonPosStartDec, valid$latPosStartDec, col="green", 
                     pch = 15 + samples$trip, cex = 1.2)
              pointLabel(x=samples$lonPosStartDec,  y= samples$latPosStartDec,
                         labels=as.character(samples$station),
                         cex=1,offset=-1, allowSmallOverlap = FALSE)
              legend("bottomright", legend= c("Valid ", "Invalid"),
                  col=c("green", "black"), pch = 16, cex=1.5, bg='white')
             
              
```
Figur 1. Plot af stationer.
\newpage
\subsection{Tjek af stations data}
```{r station_outlier, echo=FALSE, results='asis', cache=FALSE, message=FALSE, warning=FALSE, fig.width=12, fig.height=6}

samples$knob = samples$distancePositions/(samples$fishingtime/60)
dat <- samples[ samples$gearQuality == "V", ]

lst <- c("fishingtime", "distancePositions", "knob")

fun <- function(j) {
  
  i <- lst[j]
  
  ## Calculate the mean and sd
  dat$var <- dat[, i]
  smean <- mean(dat$var, na.rm = TRUE)
  sds <-  sd(dat$var, na.rm = TRUE)
  
  ## Identify the cells with value greater than cutoff * sd (column wise)
  dat$outlier <- ifelse(dat$var >  smean + (2 * sds) | dat$var <  smean - (3 * sds), "Yes", "No")
  
  ## lav pæne titler
  ii <- gsub("fishingtime", "Fiske tid [min]", i)
  ii <- gsub("distancePositions", "Træk distance [Nm]", ii)
  ii <- gsub("knob", "Træk Hastighed [kn]", ii)
  
  #create headder
  cat(paste0("\n\n### ", ii, "\n"))
  
  p1 <- ggplot(dat, aes(x = as.factor(sampleId), y = var, color = outlier)) +
  geom_point()+
  theme_bw()+
  ylab(ii)+
  xlab("Station")+  
  scale_color_manual(name='Outlier',
                     breaks=c('Yes', 'No'),
                     values=c('Yes'='red', 'No'='blue'))+
  theme(axis.text = element_text(size=14),
        legend.text = element_text(size=14),
        axis.text.x=element_blank())
  
  #plot the plot
  plot(p1)
  
  #get the outliers for later table
  out <- dat[dat$outlier == "Yes", ]
  
  if (nrow(out) > 0)
  out$type <- ii
  
  #state the output for the function
  out
  
} 
temp<-lapply(1:length(lst), fun) #function to get data and run the loop/function
outliers<-data.frame(do.call("rbind", temp))
             
 
```


\newpage
\subsection{Tabel af Outliers}
```{r ,echo=FALSE, results='asis', cache=FALSE, message=FALSE, warning=FALSE}

## make a table of outliers found above, if any.
if (nrow(outliers) > 0){
  
  setDT(outliers)
  out_outliers <- outliers[,. (type = toString(unique(type))),
                           by = .(year, cruise, trip, station)]

  
  print(out_outliers %>%
         kbl(escape = F, longtable = T, caption = "Trip outliers", 
             booktabs = T, linesep = "", row.names = F,    
             col.names = c("År", "Togt", "Tur", "Station", "Outlier Type"), align = "l") %>%
         row_spec(0, bold = TRUE) %>%
         kable_styling(latex_options = c("striped", "hold_position")) %>%
         column_spec(1:4, width = "1.5cm") %>%
         column_spec(5, width = "10cm")
       )
  
} else {
  
  text<-c("Ingen outliers fundet på trækniveau")
  #Make table
  print(text %>% 
      cell_spec(color = "green", font_size = 15, bold = T) %>%
      kbl(booktabs = T, escape = F, col.names = NULL)  %>%  
      kable_styling(latex_options = c("hold_position")) 
  )
}  

```

\newpage
\section{Fangst Oversigt}
Denne section giver et overblik over hvor meget der er fanget totalt samt tal og længde frikvenser for udvalgte arter.

\subsection{Fangst Tabel}
```{r format_catch list, echo=FALSE, results='asis'}
#format information to directly be inputed to latex table

species2 <- c("Total Fangst", species)
fun <- function(jj) {
  
  sp <- species2[jj]
  
  if (sp == "Total Fangst"){
    sps <- unique(sp_lst$speciesCode)
  } else {
    sps <- sp
  }
    
  w_s <- as.character(round(sum(sp_lst[sp_lst$speciesCode %in% sps, "weightSubSample"]), digits = 1))
  w_t <- as.character(round(sum(sp_lst[sp_lst$speciesCode  %in% sps, "weightTotal"]), digits = 1))
  
  n_s <- as.character(round(sum(sp_lst[sp_lst$speciesCode  %in% sps, "numberSubSample"]), digits = 0))
  n_t <- as.character(round(sum(sp_lst[sp_lst$speciesCode  %in% sps, "numberTotal"]), digits = 0))
  
  aged <- nrow(age[age$speciesCode %in% sps & !is.na(age$age), ])
  gen <- nrow(age[age$speciesCode %in% sps & age$genetics == 1, ])
  
  out <- cbind(sp, w_s, w_t, n_s, n_t, aged, gen)
}
temp<-lapply(1:length(species2), fun) #function to get data and run the loop/function
sp_overview <- data.frame(do.call("rbind", temp))

 print(sp_overview %>%
         kbl(escape = F, longtable = T, caption = "Sample Overview", 
             booktabs = T, linesep = "", row.names = F,    
             col.names = c(" ", "Sub sampled [kg]", "Total [kg]", "Sub sampled [antal]", "Total [antal]",
                           "Aldret", "Genetik indsamlet"), align = "l") %>%
         row_spec(0, bold = TRUE) %>%
         kable_styling(latex_options = c("striped", "hold_position")) %>%
         pack_rows("Udvalgte Arter", 2, 7, latex_gap_space = "1.5em") %>%
         column_spec(1, width = "3.5cm") %>%
         column_spec(2:7, width = "2.2cm")
       )

```
\newpage
\subsection{Længde Frekvens}
```{r COD length frequency,echo=FALSE, results='asis', cache=FALSE, message=FALSE, warning=FALSE, fig.width=12, fig.height=7}

species2 <- sort(unique(anim_lst$speciesCode))
for (jjj in species2) {
  
  dat <- setDT(anim_lst[anim_lst$speciesCode == jjj, ])  

  if (nrow(dat) == 0)
    next
  
  #create headder
  cat(paste0("\n\n### ",  jjj, "\n"))
  # get the frequency of age by length
  freq <- dat[ ,. (frequency = sum(numberTotalPerLength)),
               by = (length)]

  x_range <- round_any(seq(range(freq$length)[1], range(freq$length)[2], length.out = 5), 10)
  # Stacked barplot with multiple groups
  p2 <- ggplot(freq, aes(x=length, y=frequency)) +
          geom_bar(stat="identity")+
          theme_bw() +
          labs(x = "Længde [mm]", y = "Frekvens [antal")+
          ggtitle(paste0("Længdefrekvens af ", jjj))+
          theme(plot.title = element_text(hjust = 0.5))+
          scale_x_continuous(breaks=x_range)+
          theme(axis.title = element_text(size=16),
                plot.title = element_text(size=16),
                axis.text.x = element_text(angle = 45, hjust=1, size=14),
                axis.text.y = element_text(size=14))

  plot(p2)
}
```
\newpage
\subsection{Artsliste}
Her er oversigten over alle arter fanget på togtet, samt den totale vægt og det estimerede totale antal.
```{r format_species list, echo=FALSE, results='asis'}

#aggregate the raised species list, to make an overview of species couhgt 
setDT(sp_lst)
sp <- sp_lst[ ,. (number = round(sum(numberTotal, na.rm = T), digits = 0), 
                  weight = round(sum(weightTotal, na.rm = T), digits = 1)),
              by = .(speciesCode, trip)]


sp[sp$number == 0, "number"] <- NA

sp2 <- merge(names, sp, by = "speciesCode")

#exclude the litter rows
sp2 <- sp2[!sp2$speciesCode %in% c("AF1", "AF2", "AF3", "AF4", "AF5"), ]

#make table in loop, one table pr trip
for (i in trip) {
  
  dat <- sp2[sp2$trip == i, ]
  
  #format which column we would like, and their order 
  dat <- dat[ , c("latin", "dkName", "number", "weight")]
  
  print(dat %>%
         kbl(escape = F, longtable = T, booktabs = T, linesep = "", 
             row.names = F, caption = paste0("Arter fanget på tur ", i),   
             col.names = c("Latinsk navn", "Dansk navn", "Antal", "Vægt (kg)")
             , align = "lllrr") %>%
         row_spec(0, bold = TRUE) %>%
         kable_styling(latex_options = c("striped", "hold_position")) %>%
         column_spec(1, width = "4.5cm") %>%
         column_spec(2, width = "4cm") %>%
         column_spec(3:4, width = "2cm"))

 
  
  
}
```
\newpage
\section{Enkeltfisk}

Denne section viser længde vægt forholdet samt mulige inkonsistencer.
```{r ,echo=FALSE, results='asis', cache=FALSE, message=FALSE, warning=FALSE, fig.width=12, fig.height=7}  
## subsection data again to plot frequency by species by area, (same subset over again due to report structure)
##this time with fuction, as to collect outlier data

species3 <- sort(unique(animal$speciesCode))
fun <- function(k) {
  
  sp <- species3[k]
  #create headder
  cat(paste0("\n\n## ", sp, "\n")) 
  ##subset by species
  
  sp_len <- animal[animal$speciesCode == sp & 
                     !is.na(animal$length) & !is.na(animal$weight), ]
  sp_age <- age[age$speciesCode == sp & !is.na(age$age), ]
  
  ## legth weight
  
  #outliers
  mod1 <- lm(log(weight) ~ log(length), data = sp_len)
  sp_len$res <- abs(rstandard(mod1))
  
  ## Identify the cells with residuals greater than .... industry standard 3, but here 9
  out_len <- sp_len[sp_len$res >  9, ]
  
  plot(sp_len$length, sp_len$weight, pch = 16, cex = 1, col = "blue",
        main = paste(paste0("Længde Vægt ", sp)),
          xlab = "Længde [mm]",
          ylab = "Vægt (kg)",
          cex.main = 1.5,
          cex.lab = 1.5)+
         points(out_len$length, out_len$weight, pch = 16, cex = 1, col = "red")
  
  
  
  if (nrow(sp_age) > 0) {
    
    ID <- unique(sp_age$age)
    fun <- function(kk) {
      a <- sp_age[sp_age$age == ID[kk], ]
          
      if (nrow(a) >= 2){
          
        a$ids <- c(1:nrow(a))
          
        #Local Outlier Factor Score    
        a$lofs <- lof(a[, c("length", "age")], minPts = 2)
          
        lofs <- a[a$lofs > 1 & a$lofs != Inf, ]
          
        ## Calculate the mean and sd
        smean <- mean(a$length, na.rm = TRUE)
        sds <-  sd(a$length, na.rm = TRUE)
        ## Identify the cells with value greater than cutoff * sd (column wise)
        points <- a[a$length <  smean + (2 * sds) & a$length >  smean - (2 * sds), ]
          
        ## exclude points from lof, which are too close to the mean to be outliers
        lofs <- lofs[! lofs$ids %in% points$ids, ]
          
        ## outliers that is far from the mean, but have more than one occurence, so does not get picked up by lof
        points2 <- a[a$length  >  smean + (3.5 * sds) | a$length <  smean - (3.5 * sds), ]
          
        #bind the outliers, but exclude rows that has already been found, as to avoid duplicates
        outliers <- rbind(lofs, points2[! points2$ids %in% lofs$ids, ])
        
        #exclude outliers that are inbtween points not deemed outliers
        not_outliers <- a[! a$animalId %in% outliers$animalId, ]
        outliers <- outliers[outliers$length > max(not_outliers$length) |
                              outliers$length < min(not_outliers$length), ]
        
        } else outliers <- c()
    }
    temp<-lapply(1:length(ID), fun) #funktion to get data and run the loop/function
    out_age<-data.frame(do.call("rbind", temp)) #make data frame from the temp file
      
    ## Plot the data, by species by area, with outliers in red, and trend line in red
    plot(sp_age$age, sp_age$length, col = "white",
         main = paste(paste0("Længde Alder ", sp)),
         xlab = "Age",
         ylab = "Length [mm]",
         cex.main = 1.5,
         cex.lab = 1.5,
         xaxt="n")+
      axis(1,at=unique(sp_age$age),labels=unique(sp_age$age))+
      grid()+
      points(sp_age$age, sp_age$length, pch = 16, cex = 1, col = "blue")+
      points(out_age$age, out_age$length, pch = 16, cex = 1, col = "red")
  
  } else{
    text<-c(paste0("Ingen ", sp, " Alderet"))
    #Make table
    print(text %>% 
        cell_spec(color = "green", font_size = 15, bold = T) %>%
        kbl(booktabs = T, escape = F, col.names = NULL)  %>%  
        kable_styling(latex_options = c("hold_position"))
    )
    out_age <- data.frame(animalId = NA, type = NA)
  }
  
  if (nrow(out_len) > 0)
  out_len$type <- "len"
  
  if (nrow(out_age) > 0)
  out_age$type <- "age"
  
  out <- rbind.fill(out_len, out_age)
  
  if(nrow(out) > 0){
  outliers2 <- out[, c("animalId", "type")]
  }else{
     outliers2 <- c()
  }
}
temp<-lapply(1:length(species3), fun) #function to get data and run the loop/function
outliers2<-data.frame(do.call("rbind", temp))

```


\newpage
\subsection{Tabel af Outliers}
```{r ,echo=FALSE, results='asis', cache=FALSE, message=FALSE, warning=FALSE, fig.width=12, fig.height=7}

weight_outliers <- animal[animal$animalId %in% outliers2[outliers2$type == "len", "animalId"],
                            c("animalId", "speciesCode", "year", "cruise", "station", "trip",
                                         "length", "weight")] #state the variable that should be

age_outliers <- age[age$animalId %in% outliers2[outliers2$type == "age", "animalId"], 
                         c("animalId", "speciesCode", "year", "cruise", "station", "trip",
                                         "length", "age")] #state the variable that should be
## make a table of outliers found above, if any.

if (nrow(data.frame(weight_outliers)) > 0){
  
  print(weight_outliers %>%
         kbl(escape = F, longtable = T, caption = "Weight outliers", 
             booktabs = T, linesep = "", row.names = F,    
             col.names = c("AnimalId", "Art", "År", "Togt", "Station", "Tur", 
                           "Længde", "Vægt"), align = "l") %>%
         row_spec(0, bold = TRUE) %>%
         kable_styling(latex_options = c("striped", "hold_position")) %>%
         column_spec(1, width = "1.5cm") %>%
         column_spec(2:6, width = "1.2cm") %>%
         column_spec(7:8, width = "2cm")
  )
    
} else {
    
  text<-c("No Detected Weight Outliers")
  #Make table
  print(text %>% 
      cell_spec(color = "green", font_size = 15, bold = T) %>%
      kbl(booktabs = T, escape = F, col.names = NULL)  %>%  
      kable_styling(latex_options = c("hold_position")) 
  )
}

if (nrow(data.frame(age_outliers)) > 0){
  
 print(age_outliers %>%
         kbl(escape = F, longtable = T, caption = "Age outliers", 
             booktabs = T, linesep = "", row.names = F,    
             col.names = c("AnimalId", "Art", "År", "Togt", "Station", "Tur", 
                           "Længde", "Alder"), align = "l") %>%
         row_spec(0, bold = TRUE) %>%
         kable_styling(latex_options = c("striped", "hold_position")) %>%
         column_spec(1, width = "1.5cm") %>%
         column_spec(2:6, width = "1.2cm") %>%
         column_spec(7:8, width = "2cm")
 )
} else {
    
    text<-c("No Detected Age Outliers")
    #Make table
    print(text %>% 
        cell_spec(color = "green", font_size = 15, bold = T) %>%
        kbl(booktabs = T, escape = F, col.names = NULL)  %>%  
        kable_styling(latex_options = c("hold_position")) 
    )
}  
  
```




