---
fontsize: 11pt
geometry: top=1.5cm, bottom=1.5cm, left=1.2cm, right=1cm
header-includes:
- \usepackage{booktabs}
- \usepackage{longtable}
- \usepackage{floatrow}
- \usepackage[T1]{fontenc}
- \usepackage[danish]{babel}
- \usepackage[utf8]{inputenc}
- \usepackage{graphicx}
- \floatsetup[table]{capposition=top}
- \usepackage[table]{}
- \usepackage{ragged2e}
- \usepackage{catchfile}
- \usepackage{array}
- \usepackage[export]{adjustbox}
- \usepackage{multirow}
- \linespread{1.15}
- \usepackage{tabularx}
- \usepackage{tcolorbox}
- \usepackage{lipsum}
- \usepackage{pbox}
output: pdf_document
classoption: landscape
---
  
\renewcommand{\familydefault}{\sfdefault}
\sffamily


```{r define_input, echo=FALSE}

#Parameters
year <- @paramYear
cruise <- @paramCruise
trip <- @paramTrip
station <- @paramStation


```




```{r set_libraries, include=FALSE}

#Libraries
if (!require(sqldf)) {
  install.packages("sqldf", repos="http://ftp.ussg.iu.edu/CRAN/")
  library(sqldf)
}
if (!require(RODBC)) {
  install.packages("RODBC", repos="http://ftp.ussg.iu.edu/CRAN/")
  library(RODBC)
}
if (!require(xtable)) {
  install.packages("xtable", repos="http://ftp.ussg.iu.edu/CRAN/")
  library(xtable)
}

```




```{r table_setup, echo=FALSE, results='asis',message=FALSE,warning=FALSE}

######### Setup to use in xtable prints ###################### 

addtorow          <- list()
addtorow$pos      <- list()
addtorow$pos[[1]] <- c(0)
addtorow$command  <- c(paste("\\hline \n",
                             "\\endhead \n",
                             "\\hline \n",
                             #"{\\footnotesize Continued on next page} \n",
                             "\\endfoot \n",
                             "\\endlastfoot \n",sep=""))
```


```{r, echo=FALSE, message=FALSE, warning=FALSE}

#Get data

channel <- odbcConnect("FishLineDW")
data <- sqlQuery(channel, paste("SELECT     year, cruise, trip, tripType, station, dateGearStart, dfuArea, statisticalRectangle, 
                                            speciesCode as Art, landingCategory as Landingkategori, sizeSortingEU as Sortering, sizeSortingDFU as Opdeling,
                                            treatment as Behandling, sexCode as Køn,ovigorous as Rogn, number as Antal, 
                                            weightStep0 as Trin0, weightStep1 as Trin1, weightStep2 as Trin2, weightNonRep as EjRep, 
                                            wemSpeciesList, remark as Bemærkning,dateGearStart,totalWeight
                                 FROM       SpeciesList
                                 WHERE      (year = (",year, ") AND 
                                             cruise = ('",cruise,"') AND
                                             trip = ('",trip,"') AND
                                             station = (",station, ") ) " ,sep=""), stringsAsFactors=FALSE)


totWeight <- sqlQuery(channel, paste("SELECT     SUM(weightTotal) as sum_weightTotal
                                      FROM        SpeciesListRaised
                                      WHERE      (year = (",year, ") AND 
                                                 cruise = ('",cruise,"') AND
                                                 trip = ('",trip,"') AND
                                                 station = (",station, ") ) " ,sep=""), stringsAsFactors=FALSE)
close(channel)

data[data$wemSpeciesList=="FALSE" & !is.na(data$wemSpeciesList),"wemSpeciesList"] <- "F"


```


<!-- Infor om tur/station -->
\begin{tabularx}{0.9\textwidth}{rrrrr}
\textbf{År:} `r year`  & \textbf{Togt:} `r cruise`  & \textbf{Tur:} `r trip` & \textbf{Station:} `r data$station[1]` &  \textbf{Dato:} `r format(as.Date(data$dateGearStart[1]), "%d-%m-%Y")`
\end{tabularx}

\vspace{0.4cm}

<!-- Infor om tur/station -->
\begin{tabularx}{0.9\textwidth}{rrrrr}
\textbf{Totalfangst (UR) kg:} `r data$totalWeight[1]` & & & &
\end{tabularx}

\vspace{-0.2cm}

<!-- Tabel artsliste -->
\definecolor{lightgray}{gray}{0.92}
\def\arraystretch{1.3}

```{r, echo=FALSE,cache=FALSE, warning=FALSE,message=FALSE, results='asis'}



dataTable <- xtable(data[,c(9:22)])
for (i in c(9:12)) { dataTable[,i] <- formatC(dataTable[,i], decimal.mark = ",", digits = 3,format = "f") 
                     dataTable[,i] <- gsub(" ", "", dataTable[,i], fixed = TRUE)
                     dataTable[,i] <- gsub("NA","",dataTable[,i], fixed = TRUE)}

colnames(dataTable) <- c("Art","Kategori","Sortering","Opdeling","Behandling","Køn","Rogn","Antal","Trin0","Trin1","Trin2",
                             "EjRep","Vægtest.","Bemærkning")

dataTable[nrow(dataTable)+1,] <- c("Totalvægt",rep(NA,7),formatC(sum(data$Trin0,na.rm=TRUE),decimal.mark = ",", digits = 3,format = "f"),rep(NA,5))
dataTable[nrow(dataTable)+1,] <- c("Totalvægt UR",rep(NA,7),formatC(totWeight$sum_weightTotal,decimal.mark = ",", digits = 3,format = "f"),rep(NA,5))


print(dataTable,
      tabular.environment = "longtable", 
      floating = FALSE, hline.after=c(-1,nrow(data)),
      include.colnames=TRUE,
      add.to.row = addtorow, 
      #sanitize.colnames.function=bold, 
      #booktabs=T,
      #size="small",
      comment=FALSE)


```

