---
title: "check_redsk_dim"
author: "Kirsten Birch Håkansson, DTU Aqua"
date: \today
output: pdf_document
---

This script checks the present coding of redsk_dim

```{r setup, include = F}

library(RODBC)
library(dplyr)
library(data.table)
library(knitr)

knitr::opts_chunk$set( echo = F,
  warning = F,
  message = F,
  error = F,
  comment = F, results = 'asis')

output_dir <- "Q:/mynd/kibi/fishLine/FishLineRapporter/Biomasseberegninger/creating_a_new_biomasse_report/output/"

```

```{r data, include = F}

# Import data from all cruises with BV - same call as in biomasse.rmd line 87 and on


channel <- odbcConnect("FishLineDW")
data_org <- sqlQuery(channel, paste("SELECT    Sample.sampleId, Sample.year, Sample.cruise, Sample.trip, Sample.station, Sample.stationName,
                                           Sample.haulType, Sample.latPosStartText, Sample.lonPosStartText, Sample.latPosEndText, 
                                           Sample.lonPosEndText, Sample.latPosStartDec, Sample.lonPosStartDec, Sample.latPosEndDec, 
                                           Sample.lonPosEndDec, Sample.fishingtime, Sample.distancePositions, Sample.coursetrack,
                                           Sample.distanceBottom,Sample.haulSpeedBot * 0.514 as haulSpeedBotMS,Sample.gearQuality, SpeciesList.speciesCode, SpeciesList.dfuBase_Category, 
                                           SpeciesList.weightStep0, SpeciesList.weightStep1, SpeciesList.weightStep2, 
                                           SpeciesList.weightStep3, SpeciesList.raisingFactor, Animal.representative, Animal.individNum,
                                           Animal.length, Animal.number, Animal.weight, Animal.sizeSortingDFU, SpeciesList.speciesListId, Animal.animalId, Sample.gearType
                                FROM       Animal RIGHT OUTER JOIN
                                           SpeciesList ON Animal.speciesListId = SpeciesList.speciesListId LEFT JOIN
                                           Sample ON SpeciesList.sampleId = Sample.sampleId
                                 WHERE     Sample.cruise like 'BV%'", sep=""), stringsAsFactors=FALSE) 
                                 
close(channel)

```


# gear dimemsion (redsk_dim)- original version

line 114-159 from old biomasse.rmd

Comment in script - *some dimensions not implemented?*

skal være 1,435 for bmsok
BOS = 0,965 m
stationtype=MSK18 = 

```{r redsk_dim, include = F}

data <- data_org

data$stationType <- ifelse(data$gearType == "MSKOES" & !is.na(data$gearType),"BOS",
                      ifelse(data$gearType %like% "^OSK" & !is.na(data$gearType),"OES",
                      ifelse(data$gearType=="MSK-OKYST15" & !is.na(data$gearType),"BMSOK",
                      ifelse(data$gearType == "MSK" & !is.na(data$gearType),"BMS",
                      ifelse(data$gearType == "MSK18" & !is.na(data$gearType),"BMS18", 
                      ifelse(data$gearType %like% "^RAM" & !is.na(data$gearType),"RAM",
                      ifelse(data$gearType %like% "^SUG" & !is.na(data$gearType),"SUG",
                      ifelse(data$gearType %like% "^VV" & !is.na(data$gearType),"VV","SST"))))))))



data[grepl("\\d",(data$gearType)) & data$stationType!="RAM","gearVal"] <-  
      as.numeric(gsub("[^\\d]+", "", data[grepl("\\d",(data$gearType)) & data$stationType!="RAM",]$gearType, perl=TRUE) )

data[grepl("\\d",(data$gearType)) & data$stationType=="RAM","gearVal"] <-  
  as.numeric(paste0("0.",gsub("[^\\d]+", "", data[grepl("\\d",(data$gearType)) & data$stationType=="RAM",]$gearType, perl=TRUE) ))

data[data$stationType=="SST","redsk_dim"] <- 2.4
data[is.na(data$gearval) & 
       data$stationType %in% c("BMS","OES","BMSOK"),"redsk_dim"] <- 1 # skal være 1,435 for bmsok
          # BOS = 0,965 m
          # stationtype=MSK18 =
data[is.na(data$gearval) &
       data$stationType %in% c("BOS"),"redsk_dim"] <- 0.965
data[is.na(data$gearval) &
      data$stationType %in% c("MSK18"),"redsk_dim"] <- 1.8
data[!is.na(data$gearVal) & data$stationType=="SUG","redsk_dim"] <-
  data[!is.na(data$gearVal) & data$stationType=="SUG","gearVal"]/100
data[!is.na(data$gearVal) & data$stationType %in% c("BMS","BMSOK"),"redsk_dim"] <-
  data[!is.na(data$gearVal) & data$stationType %in% c("BMS","BMSOK"),"gearVal"]/10
data[!is.na(data$gearVal) & data$stationType=="RAM","redsk_dim"] <-
  data[!is.na(data$gearVal) & data$stationType=="RAM","gearVal"]
data[is.na(data$redsk_dim),"redsk_dim"] <- 1

```

```{r}

kable(distinct(data, gearType, gearVal, stationType, redsk_dim))


write.csv(distinct(data, gearType, gearVal, stationType, redsk_dim), paste0(output_dir, "check_redsk_dim_", Sys.Date(), ".csv"), row.names = F)

```

# gear dimemsion (redsk_dim) - gearVal corrected

Assuming an error in original script

A lot of the original script don't do as expected, since gearVal is often misspelled as gearval - the v in lower case

Trying to run all statements with gearVal

```{r redsk_dim_new, include = F}

data <- data_org

data$stationType <- ifelse(data$gearType == "MSKOES" & !is.na(data$gearType),"BOS",
                      ifelse(data$gearType %like% "^OSK" & !is.na(data$gearType),"OES",
                      ifelse(data$gearType=="MSK-OKYST15" & !is.na(data$gearType),"BMSOK",
                      ifelse(data$gearType == "MSK" & !is.na(data$gearType),"BMS",
                      ifelse(data$gearType == "MSK18" & !is.na(data$gearType),"BMS18", 
                      ifelse(data$gearType %like% "^RAM" & !is.na(data$gearType),"RAM",
                      ifelse(data$gearType %like% "^SUG" & !is.na(data$gearType),"SUG",
                      ifelse(data$gearType %like% "^VV" & !is.na(data$gearType),"VV","SST"))))))))



data[grepl("\\d",(data$gearType)) & data$stationType!="RAM","gearVal"] <-  
      as.numeric(gsub("[^\\d]+", "", data[grepl("\\d",(data$gearType)) & data$stationType!="RAM",]$gearType, perl=TRUE) )

data[grepl("\\d",(data$gearType)) & data$stationType=="RAM","gearVal"] <-  
  as.numeric(paste0("0.",gsub("[^\\d]+", "", data[grepl("\\d",(data$gearType)) & data$stationType=="RAM",]$gearType, perl=TRUE) ))

data[data$stationType=="SST","redsk_dim"] <- 2.4
data[is.na(data$gearVal) & 
       data$stationType %in% c("BMS","OES","BMSOK"),"redsk_dim"] <- 1 # skal være 1,435 for bmsok
          # BOS = 0,965 m
          # stationtype=MSK18 =
data[is.na(data$gearVal) &
       data$stationType %in% c("BOS"),"redsk_dim"] <- 0.965
data[is.na(data$gearVal) &
      data$stationType %in% c("MSK18"),"redsk_dim"] <- 1.8
data[!is.na(data$gearVal) & data$stationType=="SUG","redsk_dim"] <-
  data[!is.na(data$gearVal) & data$stationType=="SUG","gearVal"]/100
data[!is.na(data$gearVal) & data$stationType %in% c("BMS","BMSOK"),"redsk_dim"] <-
  data[!is.na(data$gearVal) & data$stationType %in% c("BMS","BMSOK"),"gearVal"]/10
data[!is.na(data$gearVal) & data$stationType=="RAM","redsk_dim"] <-
  data[!is.na(data$gearVal) & data$stationType=="RAM","gearVal"]
data[is.na(data$redsk_dim),"redsk_dim"] <- 1

```


```{r}

kable(distinct(data, gearType, gearVal, stationType, redsk_dim))

write.csv(distinct(data, gearType, gearVal, stationType, redsk_dim), paste0(output_dir, "check_redsk_dim_corrected_gearVal_", Sys.Date(), ".csv"), row.names = F)

```
