---
title: "creating_a_ref_table"
author: "Kirsten Birch Håkansson, DTU Aqua"
date: \today
output: pdf_document
---

This scripts create the start of a reference table for gear, gear dimensions and selectivity based on the old biomasse.rmd (version 23/9 - 2019).

The idea being these are specified outside the script in an excel sheet - to make it easier

gearType:

gearVal: This may not be needed in the future, since it is only used for specifying the gear dimensions - *TODO - check*

stationType: This may not be needed in the future - *TODO - check*

redsk_dim:

speciesCode: the relevant species - at this moment BMS, OES, SST, SKL, HMS, TRU and OST

correction_fun: the function for correcting Fangst_kg_m2 (x) for gear effectiveness e.g. f(x) = x*2.47


```{r setup, include = F}

library(RODBC)
library(dplyr)
library(data.table)
library(knitr)

knitr::opts_chunk$set( echo = F,
  warning = F,
  message = F,
  error = F,
  comment = F, results = 'asis')

output_dir <- "Q:/mynd/kibi/fishLine/FishLineRapporter/Biomasseberegninger/creating_a_new_biomasse_report/output/"

```

```{r data, include = F}

# Import data from all cruises with BV - same call as in biomasse.rmd line 87 and on


channel <- odbcConnect("FishLineDW")
data_org <- sqlQuery(channel, paste("SELECT    Sample.sampleId, Sample.year, Sample.cruise, Sample.trip, Sample.station, Sample.stationName,
                                           Sample.haulType, Sample.latPosStartText, Sample.lonPosStartText, Sample.latPosEndText, 
                                           Sample.lonPosEndText, Sample.latPosStartDec, Sample.lonPosStartDec, Sample.latPosEndDec, 
                                           Sample.lonPosEndDec, Sample.fishingtime, Sample.distancePositions, Sample.coursetrack,
                                           Sample.distanceBottom,Sample.haulSpeedBot * 0.514 as haulSpeedBotMS,Sample.gearQuality, SpeciesList.speciesCode, SpeciesList.dfuBase_Category, 
                                           SpeciesList.weightStep0, SpeciesList.weightStep1, SpeciesList.weightStep2, 
                                           SpeciesList.weightStep3, SpeciesList.raisingFactor, Animal.representative, Animal.individNum,
                                           Animal.length, Animal.number, Animal.weight, Animal.sizeSortingDFU, SpeciesList.speciesListId, Animal.animalId, Sample.gearType
                                FROM       Animal RIGHT OUTER JOIN
                                           SpeciesList ON Animal.speciesListId = SpeciesList.speciesListId LEFT JOIN
                                           Sample ON SpeciesList.sampleId = Sample.sampleId
                                 WHERE     Sample.cruise like 'BV%'", sep=""), stringsAsFactors=FALSE) 
                                 
close(channel)

```


# gear dimemsion (redsk_dim) - gearVal not corrected - original version

line 114-159 from old biomasse.rmd

Comment in script - *some dimensions not implemented?*

skal være 1,435 for bmsok
BOS = 0,965 m
stationtype=MSK18 = 


```{r redsk_dim_new, include = F}

data <- data_org

data$stationType <- ifelse(data$gearType == "MSKOES" & !is.na(data$gearType),"BOS",
                      ifelse(data$gearType %like% "^OSK" & !is.na(data$gearType),"OES",
                      ifelse(data$gearType=="MSK-OKYST15" & !is.na(data$gearType),"BMSOK",
                      ifelse(data$gearType == "MSK" & !is.na(data$gearType),"BMS",
                      ifelse(data$gearType == "MSK18" & !is.na(data$gearType),"BMS18", 
                      ifelse(data$gearType %like% "^RAM" & !is.na(data$gearType),"RAM",
                      ifelse(data$gearType %like% "^SUG" & !is.na(data$gearType),"SUG",
                      ifelse(data$gearType %like% "^VV" & !is.na(data$gearType),"VV","SST"))))))))



data[grepl("\\d",(data$gearType)) & data$stationType!="RAM","gearVal"] <-  
      as.numeric(gsub("[^\\d]+", "", data[grepl("\\d",(data$gearType)) & data$stationType!="RAM",]$gearType, perl=TRUE) )

data[grepl("\\d",(data$gearType)) & data$stationType=="RAM","gearVal"] <-  
  as.numeric(paste0("0.",gsub("[^\\d]+", "", data[grepl("\\d",(data$gearType)) & data$stationType=="RAM",]$gearType, perl=TRUE) ))

data[data$stationType=="SST","redsk_dim"] <- 2.4
data[is.na(data$gearval) & 
       data$stationType %in% c("BMS","OES","BMSOK"),"redsk_dim"] <- 1 # skal være 1,435 for bmsok
          # BOS = 0,965 m
          # stationtype=MSK18 =
data[is.na(data$gearval) &
       data$stationType %in% c("BOS"),"redsk_dim"] <- 0.965
data[is.na(data$gearval) &
      data$stationType %in% c("MSK18"),"redsk_dim"] <- 1.8
data[!is.na(data$gearVal) & data$stationType=="SUG","redsk_dim"] <-
  data[!is.na(data$gearVal) & data$stationType=="SUG","gearVal"]/100
data[!is.na(data$gearVal) & data$stationType %in% c("BMS","BMSOK"),"redsk_dim"] <-
  data[!is.na(data$gearVal) & data$stationType %in% c("BMS","BMSOK"),"gearVal"]/10
data[!is.na(data$gearVal) & data$stationType=="RAM","redsk_dim"] <-
  data[!is.na(data$gearVal) & data$stationType=="RAM","gearVal"]
data[is.na(data$redsk_dim),"redsk_dim"] <- 1


```

# speciesCode

```{r, include = F}

speciesCode <- c("BMS", "OES", "SST", "SKL", "HMS", "TRU", "OST")
speciesCode <- data.frame(speciesCode)

ref <- merge(distinct(data, gearType, gearVal, stationType, redsk_dim), speciesCode, all = T)


```

# correction_fun

To be filled in manually based on biomasse.rmd (version 23/9 - 2019) - line 383-521

```{r, include = F}

ref_1 <- mutate(ref, correction_fun = "")

```

```{r, include = F}

write.csv(ref_1, paste0(output_dir, "ref_table.csv"), row.names = F)

```

