
---
fontsize: 11pt
geometry: top=1in, bottom=0.8in, left=0.8in, right=0.8in
header-includes:
- \usepackage{booktabs}
- \usepackage{longtable}
- \usepackage{floatrow}
- \usepackage[T1]{fontenc}
- \usepackage[danish]{babel}
- \usepackage[utf8]{inputenc}
- \usepackage{graphicx}
- \floatsetup[table]{capposition=bottom}
- \usepackage{fancyhdr}
- \pagestyle{fancy}
- \fancyhf{}
- \fancyfoot[R]{\thepage}
- \usepackage[table]{xcolor}
- \usepackage{rotating}
- \usepackage{ragged2e}
- \usepackage{catchfile}
- \usepackage{array}
- \usepackage[export]{adjustbox}
- \usepackage{multirow}
- \linespread{1.15}
- \usepackage{tabularx}
- \usepackage{tcolorbox}
- \usepackage{lipsum}
- \usepackage{makecell}
- \usepackage{etoolbox}
- \usepackage{colortbl, xcolor}
- \usepackage{lscape}
- \usepackage{caption}
- \usepackage{lastpage}
output:
  pdf_document:
    fig_caption: yes
    keep_tex: no
---



\renewcommand\theadalign{bc}
\renewcommand\theadfont{\bfseries}
\renewcommand\theadgape{\Gape[4pt]}
\renewcommand\cellgape{\Gape[4pt]}


\fancypagestyle{companypagestyle}{
    \fancyhf{}
    \fancyfoot[L]{
    \parbox[b]{\dimexpr\linewidth\relax}{\vspace{1cm}
    {\color{red}\rule{\dimexpr\linewidth\relax}{0.4pt}}\\
    {\footnotesize \color{gray} www.aqua.dtu.dk \hfill DTU AQUA, Kemitorvet, Building 202\\[-0.15cm]
           +45 3588 3300 \hfill 2800 Kgs. Lyngby, Denmark}}
    }
    \fancyfoot[R]{
    \parbox[b]{0cm}{}
    }
}



\pagenumbering{arabic}
\pagestyle{companypagestyle}

\renewcommand{\familydefault}{\sfdefault}
\def\Tiny{\fontsize{5pt}{5pt}\selectfont}

\sffamily

\renewcommand\floatpagefraction{0}
\renewcommand\textfraction{0}


\def\figurename{Figure}
\def\tablename{Table}


\pagenumbering{arabic}




```{r set_libraries, include=FALSE}


#Libraries
if (!require(pacman)) {
  install.packages("pacman", repos="http://ftp.ussg.iu.edu/CRAN/")
  library(pacman)
}

p_load(RODBC,dplyr,sf,Hmisc,knitr,RColorBrewer,colormap,ggrepel,lubridate)

detach(package:Hmisc)


mylatex <- function (...) {
    o <- capture.output(latex(...))
    # this will strip /all/ line-only comments; or if you're only
    #  interested in stripping the first such comment you could
    #  adjust accordingly
    o <- grep('^%', o, inv=T, value=T)
    cat(o, sep='\n')
}


textplot2 <- function(x, 
                      y, 
                      words, 
                      cex = 1, 
                      pch = 16, 
                      pointcolor = "red", 
                      new = TRUE,
                      show.lines=TRUE, 
                      ...){
  if(new)
    plot(x,y,type="n",...)
  lay <- wordlayout(x,y,words,cex,...)
  if(show.lines){
    for(i in 1:length(x)){
      xl <- lay[i,1]
      yl <- lay[i,2]
      w <- lay[i,3]
      h <- lay[i,4]
      if(x[i]<xl || x[i]>xl+w ||
         y[i]<yl || y[i]>yl+h){
        points(x[i],y[i],pch= pch,col= pointcolor,cex= .5)
        nx <- xl+.5*w
        ny <- yl+.5*h
        lines(c(x[i],nx),c(y[i],ny),col="grey")
      }
    }
  }
  text(lay[,1]+.5*lay[,3],lay[,2]+.5*lay[,4],words,cex = cex,...)
}

```



```{r define_input, include=FALSE, echo=FALSE}
plannedHauls <- 50
opts_knit$set(eval.after = 'fig.cap')


# year <- @paramYear # mandatory
# cruise <- "Tunger"#@paramCruise # mandatory
# trip <- c(@paramTrip)
# par <- "participants.csv"
# coastString <- 'europe_simple_wgs84'
# dk_eezString <- 'eez_dk_line'
# 
# str_weather <- @paramWeather
# str_guest <- @paramGuest
# str_oxygen <- @paramOxygen
# str_gear  <- @paramGear
# str_other  <- @paramOther


year <- 2018#@paramYear # mandatory
cruise <- "Tobisskrabetogt"
trip <- c(1,2,4,6,8) # mandatory
par <- "participants.csv"
str_cruiseLeader <- "Henrik Degel"#@paramCruiseLeader
coastString <- 'M:/123 - FiskeLine/Rapporter/Rapporter/Discardtjek/kort/europe_simple_wgs84'
# dk_eezString <- "Q:/gis/Dynamisk/GEOdata/BasicLayers/Boundaries/EEZ/DK_EEZ_Jan_2017"
dk_eezString <- "Q:/gis/Dynamisk/GEOdata/BasicLayers/Boundaries/EEZ/World_EEZ_v10_20180221/EEZ_v10"
sandeelAreasString <- "Q:/gis/Dynamisk/GEOdata/BasicLayers/Boundaries/Tobis/Tobisomr"
sandeelBanksString <- "Q:/gis/Dynamisk/GEOdata/BasicLayers/Boundaries/Tobis/2018_opdatering/Tobisbanker2018"

str_weather <- ""
str_guest <- ""
str_oxygen <- ""
str_gear  <- ""
str_other  <- ""

trips <- paste0(trip,collapse = "','")
zipfile <- sprintf("Danish_sole_survey_maps_%s-%s.zip",year,format(Sys.Date(),"%Y%m%d"))
# maps <- zip(zipfile = zipfile)
```




```{r table_setup, echo=FALSE, results='asis',message=FALSE,warning=FALSE}

######### Setup to use in xtable prints ######################

bold <- function(x) {paste('{\\textbf{',x,'}}', sep ='')}
gray <- function(x) {paste('{\\textcolor{gray}{',x,'}}', sep ='')}

addtorow          <- list()
addtorow$pos      <- list()
addtorow$pos[[1]] <- c(0)
addtorow$command  <- c(paste("\\hline \n",
                             "\\endhead \n",
                             "\\hline \n",
                             #"{\\footnotesize Continued on next page} \n",
                             "\\endfoot \n",
                             "\\endlastfoot \n",sep=""))

```




```{r dbcall, echo=FALSE, message=FALSE, warning=FALSE,include=FALSE}

query1<-sprintf("SELECT Trip.year,Trip.contactPersonName,Trip.contactPersonId , Trip.trip, Trip.cruise, tripLeaderName, dateStart, dateEnd, platform1
              FROM Trip
              WHERE     Trip.year = %s and Trip.cruise like '%s%s' and Trip.trip in ('%s')" 
             ,year,cruise,"%",trips)
query1


query2 <-sprintf("SELECT     Animal.year, Animal.cruise, Animal.speciesCode, Animal.representative, Animal.individNum,
                           Animal.number, Animal.length, Animal.weight,Animal.statisticalRectangle as ICESsquare
                FROM       Animal
                WHERE     Animal.year=%s and Animal.cruise like'%s%s' and 
               Animal.trip in ('%s')"
                          ,year,cruise,"%",trips)
query2

query4<-sprintf("SELECT Sample.cruise,Sample.trip,Sample.station, Sample.stationName, Sample.fishingtime, Sample.latPosStartDec AS lat, Sample.lonPosStartDec AS lon,
Sample.latPosStartText, Sample.lonPosStartText,
                      Sample.gearType,Sample.gearQuality,Sample.haulType, Sample.selectionDevice,Sample.meshSize, Sample.dfuArea,
                      Sample.statisticalRectangle,Sample.quarterGearStart,
                      Sample.netOpening,Sample.wireLength as warpLength, Sample.otterBoardDist as DoorSpread,Sample.dateGearEnd,
                      Sample.depthAvg,Sample.windDirection,Sample.windSpeed, Sample.dateGearStart, Trip.platform1
              FROM Sample
              left join Trip
              on Sample.Trip = Trip.Trip and
                Sample.Cruise = Trip.Cruise and
                Sample.year = Trip.year
              WHERE     (Sample.year=%s and Sample.cruise like '%s%s' and 
Sample.trip in ('%s'))"
              ,year,cruise,"%",trips)
query4


query5 <-sprintf("SELECT     s.year, s.cruise, s.speciesCode, SUM(s.numberTotal) AS number, SUM(s.weightTotal) AS weight
                FROM         SpeciesListRaised as s
                WHERE     s.year=%s and s.cruise like '%s%s' and
                s.trip in ('%s')
                GROUP BY s.year, s.cruise, s.speciesCode
              "
              ,year,cruise,"%s",trips)
query5

ql <- sprintf("select responsibleName from cruise where year = %s and cruise like '%s%s'",
              year,cruise,"%")

channel <- odbcConnect("FishLineDW")
data1 <- sqlQuery(channel, paste(query1),stringsAsFactors=FALSE)
data_animal <- sqlQuery(channel, paste(query2),stringsAsFactors=FALSE)
data_sample <- sqlQuery(channel, paste(query4),stringsAsFactors=FALSE)
all_spec <- sqlQuery(channel, paste(query5),stringsAsFactors=FALSE)
CL <- sqlQuery(channel, paste(ql),stringsAsFactors=FALSE)
close(channel)
```


```{r info_cruise2, echo=FALSE, message=FALSE, warning=FALSE,include=FALSE}
# add tobis area to stations
sea <- st_read(paste0(sandeelAreasString,".shp"),stringsAsFactors = F) %>% 
  st_transform(4326)
# banker <- st_read()

data_sample$shipName[data_sample$platform1=="L526"] <- "L526 - Lonny Hedvig"
data_sample$shipName[data_sample$platform1=="REYKJA"] <- "E157 - Reykjanes"
data_sample$shipName[data_sample$platform1=="SALLIN"] <- "E180 - Salling"
  
  
  
data_sample$x <- data_sample$lon
data_sample$y <- data_sample$lat

data_sample2 <- data_sample %>% 
  st_as_sf(coords = c("x","y")) %>% 
  st_set_crs(4326)


data_sample3 <- st_join(data_sample2,sea)

st_geometry(data_sample3) <- NULL

table(data_sample3$platform1,data_sample3$tbs_omr_r,exclude=F)

```


```{r info_cruise3, echo=FALSE, message=FALSE, warning=FALSE,include=FALSE}


cruiseLeader <- CL$responsibleName[1] 
data1 <- with(data1, data1[order(data1$dateStart),])

cruise2 <- ifelse(cruise %in% c('Torsk','2262-Torsk'),
                  "Torsk",ifelse(tolower(cruise)=='tunger',"Tunger",
                                 substr(cruise,1,4)))
Quarter <- unique(quarter(data1$dateStart),quarter(data1$dateEnd) )
StartDate <- ifelse(nrow(data1)==1,
                    format(data1$dateStart,"%d-%m-%Y"),
                    format(data1$dateStart[1],"%d-%m-%Y"))
EndDate <- ifelse(nrow(data1)==1,
                  format(data1$dateEnd,"%d-%m-%Y"),
                  format(data1$dateEnd[nrow(data1)],"%d-%m-%Y"))


StartTime <- paste0(format(data1$dateStart,"%H"),":00")
EndTime <- paste0(format(data1$dateEnd,"%H"),":00")

cruiseName <- sprintf("Sand eel Survey")
# cruiseName <- ifelse(substr(cruise,1,4) %in% c("IBTS","BITS","KASU"),
#                      substr(cruise,1,4),cruise)
#if (cruiseName=="KASU") {cruiseName <- "BITS"}
# ship <- ifelse(substr(cruise,1,4) %in% c("IBTS","BITS"),
#                "R/V DANA",ifelse(substr(cruise,1,4)=="KASU","Havfisken",
#                                  paste(unique(data1$platform1), collapse=', ' )))
ship <- paste(sort(unique(data_sample$platform1)),collapse = ", ")

cruise_title2 <- ""
# ifelse(substr(cruise,1,4)=="IBTS",
#                         "International Bottom Trawl Survey",
#                         ifelse(substr(cruise,1,4)=="BITS",
#                                                                                               "Baltic International Trawl Survey",""))
cruise_title <- "Danish Sandeel Survey"
cruise_title <- ifelse(length(unique(Quarter))==1,
                       paste0(cruiseName," ",Quarter,"Q"," ",year),
                       paste(cruiseName, paste0(Quarter,"Q"," ",year, collapse = "\\& ")))



# TripNum <- ifelse(nrow(data1)>1,"MT","ST")
# 
# num_AS <- as.character(round(sum(all_spec$number, na.rm=TRUE),0))
# wei_AS <- as.character(round(sum(all_spec$weight, na.rm=TRUE),1))
# 
# num_TOR <- as.character(round(sum(all_spec[all_spec$speciesCode=="TOR","number"], na.rm=TRUE),0))
# num_RSP <- as.character(round(sum(all_spec[all_spec$speciesCode=="RSP","number"], na.rm=TRUE),0))
# num_TNG <- as.character(round(sum(all_spec[all_spec$speciesCode=="TNG","number"], na.rm=TRUE),0))
# 
# wei_TOR <- as.character(round(sum(all_spec[all_spec$speciesCode=="TOR","weight"], na.rm=TRUE),1))
# wei_RSP <- as.character(round(sum(all_spec[all_spec$speciesCode=="RSP","weight"], na.rm=TRUE),1))
# wei_TNG <- as.character(round(sum(all_spec[all_spec$speciesCode=="TNG","weight"], na.rm=TRUE),1))


```

<!-- definere forside -->




\thispagestyle{empty}

<!--

\vspace*{-1cm}


\vspace{-0.9cm}


<!-- #\begin{figure}[H] -->
<!-- #        \flushright -->
<!-- #        \includegraphics[width=10cm]{X:/Line/Togtrapport/logotilkort.png} -->
<!-- #\end{figure} -->

\vspace*{0.5cm}





\thispagestyle{empty}



\vspace*{-2.5cm}



\begin{figure}[H]
        \flushright
        \includegraphics[height=2cm]{Corp_Red_RGB.png}
\end{figure}

\vspace*{0.5cm}



\noindent\textcolor{gray}{\rule{0.6\textwidth}{1pt}}\par
\vspace*{-0.6cm}
\noindent\textcolor{gray}{\rule{0.8\textwidth}{1pt}}\par


\textcolor{gray}{\Large DTU Aqua - Cruise report}

\vspace*{4.5cm}




\textbf{\Huge `r cruise_title`}\

\vspace*{-0.3cm}

\textbf{\it{\Large `r cruise_title2`}}\

\vspace*{1cm}

\textbf{\Huge `r ship`}

\vspace*{0.3cm}

\textbf{\Huge Denmark}

\vspace*{0.5cm}

\textbf{\large From `r StartDate` to `r EndDate`}




\vfill

\begin{figure}[H]
        \flushleft
        \includegraphics[width=10cm]{aqua_uk.png}
\end{figure}

\vspace{-3.1cm}
\begin{flushright}
DTU Aqua\\
Kemitorvet, Building 202\\
2800 Kgs. Lyngby\\
Denmark
\end{flushright}







\newpage


<!-- define header -->

\lhead{\footnotesize \color{gray}  CRUISE REPORT, `r cruise_title`}
\rhead{\footnotesize \color{gray} PAGE \thepage\ OF \pageref{LastPage}}


\vspace*{0.01cm}



\vspace*{0.01cm}

\renewcommand{\contentsname}{Contents}
\tableofcontents

\newpage



\section{Cruise summary}
\vspace{0.3cm}

\newcolumntype{s}{>{\hsize=.4\hsize}X}
\newcolumntype{u}{>{\hsize=1\hsize}X}
\newcolumntype{t}{>{\hsize=0.6\hsize}X}


\subsubsection*{General information}
\vspace{-0.5cm}



\renewcommand{\arraystretch}{1}
\renewcommand{\tabcolsep}{5pt}
\begin{tabularx}{0.93\textwidth}{utst}
        &\textbf{}   & \textbf{} &  \textbf{} \\
\it{Cruise} & `r cruiseName`  &  &  \\
\it{Cruise leader} & `r cruiseLeader`  &  &  \\
\it{Reseach vessel(s)}   & `r ship` &   &  \\
\it{Year and quarter}   & `r paste0(Quarter[1],"Q")` `r year`&   &  \\
\it{Country}    & Denmark & &
\end{tabularx}



\vspace{0.3cm}

\subsubsection*{Participants and time}





```{r tripInfo,results='asis',echo=FALSE,message=FALSE,warning=FALSE}

# if (TripNum=="MT") {
    tripInfo <- data1[,c("trip","dateStart","dateEnd","platform1")]

    tripInfo$dateStart <- paste0(format(data1$dateStart,"%d-%m-%Y %H"),":00")
    tripInfo$dateEnd <- paste0(format(data1$dateEnd,"%d-%m-%Y %H"),":00")

    ti <- tripInfo
    # trip_table <- xtable(tripInfo,label = "",caption="")
    colnames(ti) <- c("Trip no.","Start date and time", "End date and time","Ship")
    # align(trip_table) <- "lp{3cm}p{5cm}p{5cm}p{2.5cm}"

     library(Hmisc)

     mylatex(ti,
             file='',
             booktabs =T,
             col.just = c("l","l","l","l"),
             # rgroup =n.rgroup$rgroup ,
             rowname="",
             # n.rgroup=n.rgroup$n.rgroup,
             rowlabel="",
             colnamesTexCmd="bfseries",
             rgroupTexCmd="itshape",
             where='H',
             # collabel.just=c("l","l"),
             center='none')


    detach(package:Hmisc)

 # }

```


\vspace{0.5cm}


\vspace{0.2cm}

\renewcommand{\arraystretch}{1}
\renewcommand{\tabcolsep}{20pt}

```{r participants1, results='asis',echo=FALSE,message=FALSE,warning=FALSE}
read.csv.unknown.sep <- function(file,numCol){
    for (i in c(",",";","","_")){
        f <- read.csv(file, header=TRUE, sep = i,stringsAsFactors = F)
        if (ncol(f)==numCol){
            return(f)}
        }    
    }

participants <- read.csv.unknown.sep(par,6) 
# participants <- participants[!is.na(participants$Leg),]
# participants <- participants[participants$Leg==1,]
participants$order <- as.integer(rownames(participants))

colnames(participants) <- c("Name","Vessel","Institute", "Function and tasks","trip","Leg","no")

pt <- full_join(participants,tripInfo)

colnames(pt) <- c("Name","Vessel","Institute","Function \\\\ and tasks", "Trip",
                  "Part","no","Start","End","platform1")

library(Hmisc)
mylatex <- function (...) {
    o <- capture.output(latex(...))
    # this will strip /all/ line-only comments; or if you're only
    #  interested in stripping the first such comment you could
    #  adjust accordingly
    o <- grep('^%', o, inv=T, value=T)
    cat(o, sep='\n')
}
detach(package:Hmisc)
# colnames(participants)[4] <- sprintf)


for (i in sort(unique(pt$Trip))){
  # cat(sprintf("\\paragraph{Trip %s} ",i))
  
  pt2 <- pt[pt$Trip==i,]
  
  cat(sprintf("\\paragraph{Trip: %s, Vessel: %s, Start: %s, End:  %s} ",
              i,unique(pt2$Vessel),unique(pt2$Start),unique(pt2$End)))
  
  colnames(pt2) <- sprintf("\\thead{ %s } ",colnames(pt2))
 
  lines <- data.frame(table(pt2$Leg))
 
  library(Hmisc) 
  mylatex(pt2[,c(1,3,4,6)],
       file='',
       booktabs =T,
       col.just = c(rep("l",4)),
       rgroup = lines$Var1 ,
       rowname=NULL,
       n.rgroup=lines$Freq,
       # rowlabel="",
       # colnamesTexCmd="bfs",
       # rgroupTexCmd="itshape",
       where='H',
       collabel.just=c(rep("l",4)),
       center='none')
  detach(package:Hmisc)

  # cat("\\\\ ")

}



```




```{r SIS_data, results='asis',echo=FALSE,message=FALSE,warning=FALSE}

#SIS_info <- read.table("X:\\Line\\Togtrapport\\SIS-info_BITS1_2008.csv",header=TRUE,sep=",")

No_oxy <- 1 #nrow(SIS_info[SIS_info$Redskab=="AKU",])
No_CTD <- 1 #nrow(SIS_info[SIS_info$Redskab=="SEA",])




# yn_cruiseLeader <- ifelse(str_cruiseLeader!="","yes","no")
# yn_oxygen <- ifelse(str_oxygen!="","yes","no")
# yn_weather <- ifelse(str_weather!="","yes","no")
# yn_results <- ifelse(str_results!="","yes","no")
# yn_comments <- ifelse(str_comments!="","yes","no")
# yn_gear <- ifelse(str_gear!="","yes","no")


pos <- data_sample %>% 
  filter(gearType!="GRB") %>%
  select(station,stationName,gearType,gearQuality,lat,lon,dfuArea,latPosStartText,
         lonPosStartText,platform1,shipName)
pos[is.na(pos$stationName),"stationName"] <- pos[is.na(pos$stationName),"station"]
pos$stationName <- as.character(pos$stationName)
pos$platform1 <- as.factor(pos$platform1)
pos$shipName <- as.factor(pos$shipName)

```


\newpage

\section{Objectives}
The purpose of the sand eel dredge survey is to collect sand eels buried in the seabed and compare catches (number and age composition) with the previous year's collections to assess the 2018 year class strength of sand eel in area 1r, 2r and 3r of the different areas adopted by ICES in 2016 (figure 1). Data from the dredge survey is the basis for calculating an index, which is used in the stock assessment for sand eel in the North Sea.
 

 
\section{Sampling method and strategy}



```{r weather, echo=F, results='asis'}
if (str_weather!=""){
  cat("\\subsection{Weather conditions} ")
  
  cat(str_weather)
}
```

```{r oxygen, echo=F, results='asis'}
if (str_oxygen!=""){
  cat("\\subsection{Oxygen conditions} ")
  
  cat(str_oxygen)
}
```

```{r gear, echo=F, results='asis'}
if (str_gear!=""){
  cat("\\subsection{Gear performance} ")
  
  cat(str_gear)
}
```

```{r guests, echo=F, results='asis'}
if (str_guest!=""){
  cat("\\subsection{List of guests} ")
  
  cat(str_guest)
}
```


```{r other, echo=F, results='asis'}
if (str_guest!=""){
  cat("\\subsection{Other remarks} ")
  
  cat(str_other)
}
```

\subsection{Results}
```{r results, echo=F, results='asis'}
positions <- length(unique(data_sample$stationName[data_sample$fishingtime>0]))
stationNames <- length(unique(data_sample$stationName))

cat(sprintf("In total where %s stations fished using the dredges distributed on %s positions. Furthermore, %s sediment samples where obtained.",
            nrow(pos),length(unique(pos$stationName)),nrow(data_sample %>% filter(gearType=="GRB"))))
```



\subsection*{Stations}
`r nrow(pos)` hauls were conducted during the survey. The positions off all hauls are presented in the map in Fig. 1 and hauls per ICES area are plotted in the maps in Fig. 2-`r length(unique(pos$dfuArea))+1`.


```{r , include=F}
ylim <- c(round(min(pos$lat,na.rm=T)-2),round(max(pos$lat,na.rm=T)+2))
xlim <- c(round(min(pos$lon,na.rm=T)-1),round(max(pos$lon,na.rm=T)+1))

# bat <- marmap::getNOAA.bathy(lon1 = min(xlim)-1, lon2 = max(xlim)+1,
#                       lat1 = min(ylim)-1, lat2 = max(ylim)+1, resolution = 1,keep = T)

bat <- marmap::getNOAA.bathy(lon1 = 0, lon2 = 11,
                             lat1 = 50, lat2 = 60, 
                             resolution = 1,keep = T)


bat2 <- fortify(bat)
# coast <- read.shapefile(coastString)
# dk_eez <- read.shapefile(dk_eezString)
# bat[bat>=0] <- NA

coast <- st_read(paste0(coastString,".shp"))%>%
  st_transform(crs=4326)
dkeez <- st_read(paste0(dk_eezString,".shp"))%>%
  st_transform(crs=4326)

sandeelBanks <- st_read(paste0(sandeelBanksString,".shp")) %>%
  st_transform(crs=4326)

# sandeelAreas <- st_read(paste0(sandeelAreasString,".shp")) %>%
#   st_transform(crs=4326)

```

```{r, include=F}
p_load(mapplots,shapefiles,wordcloud,oce,oceData,colormap)

# coast <- read.shapefile(coastString)
# sandeelBanks <- read.shapefile(sandeelBanksString)

```

```{r, include=F}

shipColors <- c('#e41a1c', '#984ea3','#ff7f00',
                            '#ffff33','#a65628','#f781bf','#377eb8','#4daf4a')

stations <- pos %>% 
  group_by(stationName) %>% 
  filter(row_number()==1) %>% 
  mutate()

bat[bat<=-150] <- -150
bat[bat<=-100 & bat>-150] <- -100
bat[bat<=-75 & bat>-100] <- -75
bat[bat<=-50 & bat>-75] <- -50
bat[bat<=-30 & bat>-50] <- -30
bat[bat<=-15 & bat>-30] <- -15
bat[bat<=-1 & bat>-15] <- -1


ylim2 <- c(floor(min(pos$lat,na.rm=T)/.1)*.1,ceiling(max(pos$lat,na.rm=T)/.1)*.1)
xlim2 <- c(floor(min(pos$lon,na.rm=T)/.5)*.5,ceiling(max(pos$lon,na.rm=T)/.5)*.5)

  gr   <- colormap::colormap(colormaps$greys, nshades = 10)[4:6]
  bl   <- colormap::colormap(colormaps$velocity_blue, nshades = 13)[3:9]
  cols <- c(bl, gr)

png("tripmap.png")
# png("tripmap.png",width = 7,height = 7,units = "in",res = 300)
basemap(xlim = xlim2, ylim = ylim2,bg = "transparent")

plot(bat,image = T, land = T, lwd = 0,col="transparent",
     bpal = list(c(0, max(bat), "grey"),
                 c(min(bat),0,bl)), add=T)

draw.rect()
coastCol <- "#555555ff"
sandeelBankCol <- "#999999"

plot(coast,col = coastCol, add=T, border = "transparent")
plot(sandeelBanks, col=sandeelBankCol, add=T, border = "black")

# use sandeel areas or eez?
plot(sea,add=T,col="transparent",border="black",lty=1,lwd=1) 
plot(dkeez, add=T, col="transparent",border = "red")


# add points for each vessel used in the cruise - and make the legend adapt to this
platform1 <- c()
color <- c()
lty <- c()
pch <- c()
pt.bg <- c()

for (i in 1:length(levels(pos$shipName))){

  pos2 <- pos %>% filter(shipName == levels(pos$shipName)[i])

  points(x=pos2$lon,y=pos2$lat,pch=20,col=shipColors[i])
  
  platform1 <- c(platform1, levels(pos$shipName)[i])
  color <- c(color, shipColors[i])
  lty <- c(lty,0)
  pch <- c(pch,16)
  pt.bg <- c(pt.bg,"white")
}

textplot2(x=stations$lon,y=stations$lat,words = paste0(" ",stations$station," "),
                    new = F,pointcolor = NA)

legend( x="bottomright",
        legend=c("ICES rectangle","Sandeel bank",rev(platform1)),
        lty=c(2,0,rev(lty)),pch=c(NA,15,rev(pch)), col = c(coastCol,sandeelBankCol,rev(color)),
        cex = 0.9, pt.bg=c("white","#999999",rev(pt.bg)) ,bg=c("white"))

dev.off()

```

\begin{figure}[H]
        \includegraphics[width=18cm]{tripmap.png}
\end{figure}


```{r stationTable, echo=FALSE, message=FALSE, warning=FALSE, results='asis',fig.pos='h',fig.cap=paste0("Survey map with all sampling stations.\\label{fig:mapall}"),dpi=300, fig.width=10,fig.height=11}

tableData <- data_sample3 %>% 
  select(shipName,dateGearStart)

  library(Hmisc) 
  mylatex(pt2[,c(1,3,4,6)],
       file='',
       booktabs =T,
       col.just = c(rep("l",4)),
       rgroup = lines$Var1,
       rowname=NULL,
       n.rgroup=lines$Freq,
       # rowlabel="",
       # colnamesTexCmd="bfs",
       # rgroupTexCmd="itshape",
       where='H',
       collabel.just=c(rep("l",4)),
       center='none')
  detach(package:Hmisc)


```
