---
title: "Cruise Report" 
cruiseTitle: "Sandeel dredge cruse 2017"
cruiseTitle2: "Extended area"
vessel: "M/V Salling"
cruiseArea: "Southern North Sea– sand eel Area 1r." #
output: 
  word_document:
    reference_docx: style-template.docx
---

```{r input vars, include=FALSE}

title <- "Cruise Report"
cruise <- "Salling"
cruiseTitle <- "Sandeel dredge cruse 2017"
cruiseTitle2 <- "Extended area"
year <- 2017
cruiseArea <-"Southern North Sea– sand eel Area 1r."
platform1 <- "M/V Salling"

```


```{r set_libraries, include=FALSE}


#Libraries
if (!require(sqldf)) {
  install.packages("sqldf", repos="http://ftp.ussg.iu.edu/CRAN/")
  library(sqldf)
}
if (!require(RODBC)) {
  install.packages("RODBC", repos="http://ftp.ussg.iu.edu/CRAN/")
  library(RODBC)
}
if (!require(dplyr)) {
  install.packages("dplyr", repos="http://ftp.ussg.iu.edu/CRAN/")
  library(dplyr)
}
if (!require(xtable)) {
  install.packages("xtable", repos="http://ftp.ussg.iu.edu/CRAN/")
  library(xtable)
}
if (!require(ggplot2)) {
  install.packages("gplots", repos="http://ftp.ussg.iu.edu/CRAN/")
  library(gplots)
}
if (!require(lubridate)) {
  install.packages("lubridate", repos="http://ftp.ussg.iu.edu/CRAN/")
  library(lubridate)
}
if (!require(reshape2)) {
  install.packages("reshape2", repos="http://ftp.ussg.iu.edu/CRAN/")
  library(reshape2)
}
if (!require(ggrepel)) {
  install.packages("ggrepel", repos="http://ftp.ussg.iu.edu/CRAN/")
  library(ggrepel)
}
 if (!require(grid)) {
  install.packages("grid", repos="http://ftp.ussg.iu.edu/CRAN/")
  library(grid)
}
 if (!require(gridExtra)) {
  install.packages("gridExtra", repos="http://ftp.ussg.iu.edu/CRAN/")
  library(gridExtra)
}
 if (!require(gplots)) {
  install.packages("gplots", repos="http://ftp.ussg.iu.edu/CRAN/")
  library(gplots)
}
 if (!require(Hmisc)) {
  install.packages("Hmisc", repos="http://ftp.ussg.iu.edu/CRAN/")
  library(Hmisc)
}
 if (!require(stringr)) {
  install.packages("stringr", repos="http://ftp.ussg.iu.edu/CRAN/")
  library(stringr)
}
 if (!require(dismo)) {
  install.packages("dismo", repos="http://ftp.ussg.iu.edu/CRAN/")
  library(dismo)
}
 if (!require(raster)) {
  install.packages("raster", repos="http://ftp.ussg.iu.edu/CRAN/")
  library(raster)
}
 if (!require(marmap)) {
  install.packages("marmap", repos="http://ftp.ussg.iu.edu/CRAN/")
  library(marmap)
}
 if (!require(rgdal)) {
  install.packages("rgdal", repos="http://ftp.ussg.iu.edu/CRAN/")
  library(rgdal)
}
 if (!require(maptools)) {
  install.packages("maptools", repos="http://ftp.ussg.iu.edu/CRAN/")
  library(maptools)
}
 if (!require(rasterVis)) {
  install.packages("rasterVis", repos="http://ftp.ussg.iu.edu/CRAN/")
  library(rasterVis)
}
 if (!require(shapefiles)) {
  install.packages("shapefiles", repos="http://ftp.ussg.iu.edu/CRAN/")
  library(shapefiles)
}
 if (!require(calibrate)) {
  install.packages("calibrate", repos="http://ftp.ussg.iu.edu/CRAN/")
  library(calibrate)
}
 if (!require(plotrix)) {
  install.packages("plotrix", repos="http://ftp.ussg.iu.edu/CRAN/")
  library(plotrix)
}
 if (!require(base)) {
  install.packages("base", repos="http://ftp.ussg.iu.edu/CRAN/")
  library(base)
}
 if (!require(mapplots)) {
  install.packages("mapplots", repos="http://ftp.ussg.iu.edu/CRAN/")
  library(mapplots)
}
 if (!require(data.table)) {
  install.packages("data.table", repos="http://ftp.ussg.iu.edu/CRAN/")
  library(data.table)
}
 if (!require(tinytex)) {
  install.packages("tinytex", repos="http://ftp.ussg.iu.edu/CRAN/")
  library(tinytex)
 }
if (!require(knitr)) {
  install.packages("knitr", repos="http://ftp.ussg.iu.edu/CRAN/")
  library(knitr)
}


detach(package:Hmisc)

```

```{r, echo=F}
knitr::opts_current$set(echo=F)
```




<!-- `r paste0("# ", title)` -->
<!-- `r paste0("# ", cruiseTitle)` -->
<!-- `r paste0("# ", cruiseTitle2)` -->

<!-- `r paste0("using")` -->
<!-- `r paste0("# ", platform1)` -->
<!-- `r paste0("# ", cruiseArea)` -->



```{r cruise_details, echo=F,warning=F, error=F}

tripQuery <- paste0("select * from Trip where year = ", year, " and cruise = '",cruise,"'")
cruiseQuery <- paste0("select * from Cruise where year = ", year, " and cruise = '",cruise,"'")
stationQuery <- paste0("select * from Sample where year = ", year, " and cruise = '",cruise,"'")

channel <- odbcConnect("FishLineDW")
trip <- sqlQuery(channel, tripQuery,stringsAsFactors=FALSE)
cruise <- sqlQuery(channel, cruiseQuery,stringsAsFactors=FALSE)
station <- sqlQuery(channel, stationQuery,stringsAsFactors=FALSE)
close(channel)

```
# Cruise details
\n
```{r,echo=F,warning=F, error=F}
cd <- data.frame(key = c("**Cruise**","**Vessel**","**Area**","**Departure**","**Arrival**"),
                 value = c(cruiseTitle, trip$platform1[1],cruiseArea, 
                           trip$harbourSample[1],trip$harbourLanding[1]),
                 key2 = c("","","","**Date:**","**Date:**"),
                 value2 = c("","","",paste0(trip$dateStart[1]),paste0(trip$dateEnd[1])),
                 stringsAsFactors = F)



kable(cd,row.names = F,col.names = NULL,format = "pandoc")

```

\n

Project number: 



## Participants (Scientific)

Cruise leader: `r trip$tripLeaderName[1]`







## Objectives
```{r,echo=F,warning=F, error=F}

paste0("This survey constitutes the extended part of the annual sand eel dredge 
       survey. The purpose of the sand eel dredge survey is to collect sand eels
       buried in the seabed and compare catches (number and age composition) 
       with the previous year's collections to assess the ",
       year,
       " year class strength of sand eel in area 1r, 2r and 3r of the different 
       areas adopted by ICES in 2016 (figure 1). Data from the dredge survey is
       the basis for calculating an index, which is used in the stock assessment
       for sand eel in the North Sea. A separate cruise report exists covering 
       the total sand eel dredge survey. Please consult this for information 
       from the complete cruise.")
```

# Achievements



# Sampling method and strategy

In 2017 the survey was extended with 57 additional stations in the southern end of the North Sea (Sand eel area 1r and 2r). A similar extension of the survey area was made in 2012. The same and some additional positions were selected. The sampling and data working-up procedure is similar in the extended survey as in the basis annual survey.

Number of samples per position
•	At all positions, where samples are taken, three stations are carried out in a ”star” formation using the dredge. Furthermore, one sediment sample is taken using Van Veen sampler (0.2m2).

Time of the day for sampling
Sampling using the dredge is carried out during night time (i.e. 15 min after sunset to 15 min before sunrise). There is no time restriction on sediment samples. 


## Working up of samples on board

For more detailed description of the working-up procedure, see the cruise program.

## Catch from dredge

The catch of the sand eel species is sorted (Lesser sand eel (Ammodytes marinus and Ammodytes tobianus) are pooled).  The weight and the length distribution of the lesser sand eel are recorded. Sub-samples are frozen for split into the two species and age reading later in the laboratory. Each drag is worked up separately.

## Sediment samples (Van Veen grab)
The content of the sediment samples are later on analyzed for grain size distribution in the lab.


# Results

In total where `length(unique(station$stationName))` stations fished using the dredges distributed on 19 positions. Furthermore, 5 sediment samples where obtained.


	Salling		Grand Total
Row Labels	1r	2r	
Sediment samples	5		5
Sand eel dredge	45	12	57
Grand Total	50	12	62



## Tables

```{r,echo=F,warning=F, error=F}
stationTable <- station %>% 
  filter(gearType == "DK2") %>% 
  arrange(dateGearStart) %>% 
  # group_by(station, stationName) %>% 
  transmute(Date = strftime(dateGearStart,format = "%d-%m-%Y"),
         Gear = gearType,
         Station = stationName,
         SandEelArea = "",
         EEZ_location = "",
         StationNo = station,
         TimeStart = strftime(dateGearStart, format="%H:%M"),
         TimeEnd = strftime(dateGearEnd, format="%H:%M"),
         lat.Start = latPosStartDec,
         lon.Start = latPosEndDec,
         Depth = depthAvg) 

kable(stationTable, row.names = F,
      col.names = c("Date","Gear","Station","Sand eel area","EEZ/ location",
                    "Station No","Time start","Time end", "Lat. start", "Lon. start",
                    "Water depth"),
      caption = "List of completed stations using modified mussle scraper"
      )

```

```{r,echo=F,warning=F, error=F}
stationTable <- station %>% 
  filter(gearType == "GRB") %>% 
  arrange(dateGearStart) %>% 
  # group_by(station, stationName) %>% 
  transmute(Date = strftime(dateGearStart,format = "%d-%m-%Y"),
         Gear = gearType,
         Station = stationName,
         SandEelArea = "",
         EEZ_location = "",
         StationNo = station,
         TimeStart = strftime(dateGearStart, format="%H:%M"),
         TimeEnd = strftime(dateGearEnd, format="%H:%M"),
         lat.Start = latPosStartDec,
         lon.Start = latPosEndDec,
         Depth = depthAvg) 

kable(stationTable, row.names = F,
      col.names = c("Date","Gear","Station","Sand eel area","EEZ/ location",
                    "Station No","Time start","Time end", "Lat. start", 
                    "Lon. start","Water depth"),
      caption = "List of completed stations using modified mussle scraper"
      )

```



## Maps

```{r,echo=F}
ggplot(station, aes(x=lonPosStartDec,y=latPosStartDec,col=gearType))+
  borders(xlim = c(min(station$lonPosStartDec)-.01,
                   max(station$lonPosStartDec)+.01),
          ylim = c(min(station$latPosStartDec)-.01,
                   max(station$latPosStartDec)+.01))+
  geom_point(aes())+
  theme_bw()

```

