---
fontsize: 11pt
geometry: top=2cm, bottom=2cm, left=1.5cm, right=1.5cm,headsep=1cm
header-includes:
- \usepackage[T1]{fontenc}
- \usepackage[danish]{babel}
- \usepackage[utf8]{inputenc}
- \usepackage{fancyhdr}
- \pagestyle{fancy}
- \fancyhf{}
- \fancyfoot{}
- \usepackage{ragged2e}
- \linespread{1.15}
- \usepackage{lipsum}
- \usepackage{float}
- \usepackage{lastpage}
output: pdf_document
fig_caption: yes
keep_tex: yes
---
  
\renewcommand{\familydefault}{\sfdefault}
\sffamily

\setlength{\LTleft}{-20cm plus -1fill}
\setlength{\LTright}{\LTleft}

\lhead{\footnotesize \color{darkgray}  Kvalitet og Status - Havneindsamling}
\rhead{\footnotesize  \color{darkgray} SIDE \color{red} \thepage\ \color{darkgray} AF \color{darkgray} \pageref*{LastPage} }


```{r define_input, echo=FALSE, include=FALSE}

#Parameters that goes into the report by the user, first art to be used directly in r, second part whith userinterface

# year<- 2020
# cruise <- "IN-LYNG"
# quarter <- 1
# tur <- c()
# if (length(c(tur))==0) {tur = "Alle"}

year <- @paramYear
cruise <- @paramCruise
quarter <- @paramQuarter
tur <- c(@paramTrip)
if (length(c(tur))==0) {tur = "Alle"}

#corrects differences in nameing
cruise0 <- cruise
if (cruise %in% c("IN-CHAR","IN-LYNG")){
  cruise <- c("IN-CHAR","IN-LYNG")
}
```

```{r set_libraries, include=FALSE, warning=FALSE}

#Libraries used in the r code
if (!require(kableExtra)) {
  install.packages("kableExtra", repos="http://ftp.ussg.iu.edu/CRAN/")
  library(kableExtra)
}
if (!require(RODBC)) {
  install.packages("RODBC", repos="http://ftp.ussg.iu.edu/CRAN/")
  library(RODBC)
}
if (!require(dplyr)) {
  install.packages("dplyr", repos="http://ftp.ussg.iu.edu/CRAN/")
  library(dplyr)
}

# useful functions
'%!in%' <- function(x,y)!('%in%'(x,y)) #a "NOT in" statement

## account for "number" in FishlineDW, lines with more than one fish pr line
convert_number <- function(data) {
  
  if ("weight" %in% names(data)){
    dat <- data[data$treatment %!in% c("RU", "VV", "VK"), ]
    #set fish individual weight
    dat$weight <- (dat$weight/dat$number) * dat$treatmentFactor
    #expand the data so each row represents one fish
    dat <- dat[rep(seq(nrow(dat)), dat$number), ]
    dat$number <- rep(1, nrow(dat))
    #quick check
    if (sum(data$weight*data$treatmentFactor, na.rm = T) != sum(dat$weight, na.rm = T))stop()
    dat
  } else if ("age" %in% names(data)){
    dat <- data[rep(seq(nrow(data)), data$number), ]
    dat$number <- rep(1, nrow(dat))
    dat
  } else stop()
  
}

```


```{r include=FALSE, cache=FALSE} 

################### Collecting data from Fishline #############################

channel <- odbcConnect("FishLineDW")

# Animal 
animal <- sqlQuery(channel,
                   paste("SELECT    animalID, year, cruise, trip,station, 
                                    speciesCode, dfuArea, number, 
                                    treatment, treatmentFactor,
                                    length, weight, 
                                    landingCategory, individNum, 
                                    representative, quarterGearStart as qtr,
                                    sizeSortingEU
                          FROM      Animal
                          WHERE     (year between ",year - 4," and ",year," ) AND
                                    quarterGearStart = (",quarter,") AND
                                    cruise in ('",paste0(cruise,collapse="','"), "') ", sep = ""),
                                    stringsAsFactors=FALSE)

#apply function to account for number
animal <- convert_number(animal)

# age information
age <- sqlQuery(channel,
                   paste("SELECT    animalID, year, cruise, trip,station,
                                    speciesCode, dfuArea, number,
                                    length, age, sexCode,
                                    landingCategory, individNum,
                                    representative, quarterGearStart as qtr,
                                    sizeSortingEU
                          FROM      Age
                          WHERE     (year between ",year - 4," and ",year," ) AND
                                    quarterGearStart = (",quarter,") AND
                                    cruise in ('",paste0(cruise,collapse="','"), "') ", sep = ""),
                                    stringsAsFactors=FALSE)

#apply function to account for number
age <- convert_number(age)

# Trip info
trip <- sqlQuery(channel,
                 paste("SELECT     year, trip, cruise, dateEnd as dateLand, platform1, 
                                   logBldNr, samplingMethod,samplingType,
                                   fisheryType,remark, DATEPART(quarter,dateEnd) as qtr, 
                                   dateSample, harbourSample, harbourLanding
                        FROM       Trip
                        WHERE      year = (",year,") AND
                                   DATEPART(quarter,dateEnd) = (",quarter,") AND
                                   cruise in ('",paste0(cruise,collapse="','"), "') ", sep = ""), 
                                   stringsAsFactors=FALSE)

sample <- sqlQuery(channel,
                   paste("SELECT   tripId, trip, station, fishingtime, 
                                   latPosStartDec AS lat, lonPosStartDec AS lon,
                                   latPosStartText AS latT, lonPosStartText AS lonT, 
                                   catchRegistration, speciesRegistration, gearType, 
                                   selectionDevice, meshSize, dfuArea, 
                                   statisticalRectangle, quarterGearStart as qtr,
                                   remark
                          FROM     Sample
                          WHERE    year = (",year,") AND
                                   quarterGearStart = (",quarter,") AND
                                   cruise in ('",paste0(cruise,collapse="','"), "') ", sep = ""), 
                                   stringsAsFactors=FALSE)

close(channel)

``` 

\thispagestyle{empty}

\vspace*{2cm} 

\textbf{\LARGE Tjek på havneindsamlingerne}

\vspace{3cm}   

\textbf{\LARGE `r quarter`. Kvartal `r year`}\
\vspace{0.5cm}

\textbf{\Large Togt:}
\textbf{\Large `r cruise0`}\
\vspace{0.5cm}

\textbf{Tur(e):}
\textbf{`r tur`}\

\newpage

\renewcommand{\contentsname}{Indhold}
\tableofcontents

\newpage



\part{Mangler, indtastningsfejl og outliers}

\section{Ture: `r tur`, `r quarter`. Kvartal `r year`}

\subsection{Tid og sted}

Tabellen herunder viser de ture, hvor nogle informationer om turen mangler. 


\small
\renewcommand{\arraystretch}{1.1}
\renewcommand{\tabcolsep}{8pt}

```{r data_out2, results='asis',echo=FALSE,message=FALSE,warning=FALSE,fig.pos='H'}
# Account for the resolution choice, all trips, or just some
if (tur != "Alle"){
  trip <- trip[trip$trip %in% tur, ]
  sample <- sample[sample$trip %in% tur, ]
}
## Check for missing trip information -----------------------------------------

## The table checks for missing variables about the trip...
#make table of trips with zero animals measured, but Animal under the station is present, within the chosen year
no_fish <- animal[animal$year == year & is.na(animal$length), ]$trip
#list of trips present in animal, within the chosen year
trips <- unique(animal[animal$year == year, ]$trip)

#add a column identifying zero samples
trip$zero_catch <- ifelse(trip$trip %in% no_fish | trip$trip %!in% trips, "yes", "no")

trip_input <- trip[trip$zero_catch == "no",
                   c("trip", "dateSample", "harbourLanding", "samplingMethod",
                     "samplingType", "fisheryType", "platform1", "logBldNr", "remark")]

#format the table input, replace blank with dash in comments
trip_input[is.na(trip_input$remark) | trip_input$remark=="\r\n","remark"] <- "-"

#select all lines where one or more missing value
mis_trip <- trip_input[!complete.cases(trip_input),]

if (nrow(mis_trip)>0) {

  #format date output
  mis_trip$dateSample <- format(mis_trip$dateSample,format='%d/%m/%y')
  
  #replace NA, with text
  mis_trip$dateSample <- as.character(mis_trip$dateSample)
  mis_trip[is.na(mis_trip)] <- "Mangler"
  
  #replace with text
  mis_trip[mis_trip$fisheryType==1,"fisheryType"] <- "Konsum"
  mis_trip[mis_trip$fisheryType==2,"fisheryType"] <- "Industri"
  
  #make sure the remarks contains no quotations marks
  mis_trip$remark <- gsub("\"", "", mis_trip$remark)   
  #Make table, and use mutate_all, to color "mangler" in red
  mis_trip %>%      
         mutate_all(~cell_spec(.x, color = case_when(.x == "Mangler" ~ "red",   
                                                          TRUE ~ "black")))  %>%
         kbl(escape = F, longtable = T, booktabs = T, linesep = "", row.names = F,
             col.names = c("tur","Indsaml dato","Land havn", "Metode",
                                     "Flere skibe?", "Type", "fartøjs nr.", "Log nr.", "Bemærkning"),
             align = "l") %>%
         row_spec(0, bold = TRUE) %>%
         kable_styling(latex_options = c("striped", "hold_position")) %>%
         column_spec(1, width = "1cm")  %>%
         column_spec(2:8, width = "1.5cm")  %>%
         column_spec(9, width = "4cm")
  
  
} else {
  #message if no errors where found
  text<-c("Ingen Fejl i Tid og sted")
  #Make table
  text %>% 
      cell_spec(color = "green", font_size = 15, bold = T) %>%
      kbl(booktabs = T, escape = F, col.names = NULL)  %>%  
      kable_styling(latex_options = c("hold_position")) 
}
```

\cleardoublepage
\section{Stationer}

\subsection{Position og redskab}

I tabllen nedenfor er vist de stationer, hvor det ikke har været muligt at assosiere et ICES område og/eller square til de indtastetde koordinater. Derudover er stationsnavne, der afviger fra den normale form på seks cifre, markeret med rødt i tabellen. 

\renewcommand{\tabcolsep}{12pt}


```{r stations, results='asis', echo = FALSE, message = FALSE, warning = FALSE, fig.pos='H'}

## Check for missing gear and missing/correct position  ------------------------
# merge trips and samples to get all information neeeded in the table
dat_merge <- merge(trip, sample, by = c("trip", "qtr"))

#format date
dat_merge$dateSample <- format(dat_merge$dateSample,format='%d/%m/%y')

#exclude trips with no fish
stat_input <- dat_merge[dat_merge$zero_catch == "no", 
                        c("platform1", "trip", "dateSample", "station", "dfuArea",
                                              "statisticalRectangle", "gearType", "meshSize")]

#format geartype
stat_input[stat_input$gearType %in% c("LL", "LLD", "LLS") & 
             is.na(stat_input$meshSize), "meshSize"] <- "-"

#select all lines where one or more missing value
mis_stat <- stat_input[!complete.cases(stat_input), ]

if (nrow(mis_stat) > 0) {
  
  #replace NA, with text
  mis_stat[is.na(mis_stat)] <- "Mangler"
  mis_stat <- mis_stat[order(mis_stat$trip,mis_stat$station),] 
  
  #Make table, and use mutate_all, to color "mangler" in red
  mis_stat %>%      
         mutate_all(~cell_spec(.x, color = case_when(.x == "Mangler" ~ "red",   
                                                          TRUE ~ "black")))  %>%
         kbl(escape = F, longtable = T, booktabs = T, linesep = "", row.names = F,
             col.names = c("fartøjs nr.","Tur","Indsamling-dato", "Station",
                           "ICES område", "ICES square", "Redskab", "Maskevidde"), align = "l") %>%
         row_spec(0, bold = TRUE) %>%
         kable_styling(latex_options = c("striped", "hold_position")) %>%
         column_spec(1:8, width = "1.2cm") 
  
  
} else {
  
  #message if no errors are found
  text<-c("Ingen Fejl i Position og Redskab")
  #Make table
  text %>% 
      cell_spec(color = "green", font_size = 15, bold = T) %>%
      kbl(booktabs = T, escape = F, col.names = NULL)  %>%  
      kable_styling(latex_options = c("hold_position")) 
}

```


\newpage

\section{Individfisk}

\subsection{Længde-vægt forhold}

I graferne nedenfor er plottet længde-vægt forhold for alle individfisk fra turene, i det valgte år, kvartal og togt. Det skraverede område representere de tidligere år fra samme kvartals, spreding (prediktions intervallet), de Blå punkter følger derved tidligere år, og de Røde punkter representere afvigelse fra det forventede. Da dette udregnes automatisk, kan det dog godt forekomme at individer med helt fine længde-vægt forhold betragtes som afvigelser. \

I den efterfølgende tabel er listet de individer, hvor der forekommer at være en afvigelse for den valgte periode og tidligere år. 


\renewcommand{\arraystretch}{1}
```{r ,echo=FALSE, results='asis', cache=FALSE, message=FALSE, warning=FALSE, fig.width=12, fig.height=7}

# Catch length-weight relation -----------------------------------------------
#select individuals that have both length and weight 
animal_ind <- animal[!is.na(animal$length) & !is.na(animal$weight), ] 
#add an id column to keep track
animal_ind$id<-c(1:nrow(animal_ind))
###############################################################################
#log stuff to get a straigt line relationship
animal_ind$log_length <- log(animal_ind$length)
animal_ind$log_weight <- log(animal_ind$weight)

#find relevant species for the given time period
sps <- unique(animal_ind[animal_ind$year == year & animal_ind$trip %in% trip$trip, ]$speciesCode)

if (length(sps) > 0){
#Loop through each species and plot
fun <- function(i) {
 #subset dataset by sepcies  
 df_sps <- animal_ind[animal_ind$speciesCode==sps[i],]
 
 #break down data into the new and old, data. NOTE: all data is from same quarter, as relations  changes with the season
 new <- df_sps[df_sps$year == year & df_sps$trip %in% trip$trip, ]
 old <- df_sps[df_sps$id %!in% new$id, ]
 
 if (nrow(old) > 0 & nrow(new)> 0) {
 #make a linear model, the log relationship between weight and length should be linear
 mod1 = lm(log_weight ~ log_length, data = old)
 
 #estimate the prediction interval, with evenly generated numbers based on data range
 sim.dat = seq(min(old$log_length), max(old$log_length), length.out=nrow(old))
 preds <- predict(mod1, newdata = data.frame(log_length=sim.dat), 
                  level=0.999999, interval = 'prediction')
 
 #put the "new"/relevant data trough the model made with the old data, to see how well it follows the given trend
 preds2 <- predict(mod1, newdata = data.frame(log_length=new$log_length), 
                   level=0.999999, interval = 'prediction')
 #select data within the preiction interval, and thereby finding outliers
 insideInterval <- new[new$log_weight > preds2[,'lwr'] & new$log_weight < preds2[,'upr'], ] 
 
 #plot. firstly the confidence band and trend from old data, but without old data points (overridden with white points)
 #secondly, plot the new data (in red), and data within confidence interval (in blue). overlapping points so as to visualize the putliers
 plot(old$log_length, old$log_weight, pch = 16, cex = 0.1, 
        main = paste(" Art:", sps[i],"- Kvartal:", quarter, sep=" "),
        xlab = "Log(Længde) (mm)",
        ylab = "Log(Vægt) (kg)", 
        cex.main = 1.5,
        cex.lab = 1.5)+ 
     points(old$log_length, old$log_weight, pch = 16, cex = 0.2, col = "white")+
     lines(sort(old$log_length), fitted(mod1)[order(old$log_length)], col='red', lwd=3)+
     polygon(c(rev(sim.dat), sim.dat), 
             c(rev(preds[ ,3]), preds[ ,2]), density=10, col = 'blue', border = NA)+
     lines(sim.dat, preds[ ,3], lty = 'dashed', col = 'red')+
     lines(sim.dat, preds[ ,2], lty = 'dashed', col = 'red')+
     points(new$log_length, new$log_weight, pch = 16, cex = 1, col = "red")+
     points(insideInterval$log_length, insideInterval$log_weight, pch = 16, cex = 1, col = "blue")
    
  #the new data NOT inside the interval, previously defined
  db_diff <- new[new$id %!in% insideInterval$id, ] 
  #Remove the duplicates, that comes from the "number" column treatment
  db_diff <- db_diff[!duplicated(db_diff[, 5:12]), ]
  
  # Make table of outliers, 
  db_diff <- db_diff[ , 
                 c("year", "trip", "station", "speciesCode", "landingCategory", 
                   "individNum", "length", "weight")]
                   
 } else if (nrow(new) > 0){
  
  #Use only data for chosen period, if not enough data is availeble 
  text<-c(paste0("Ingen Tidligere Data for ", sps[i], " Bruger Kun Indeværende År"))
  #Make table
  print(text %>% 
      cell_spec(color = "blue", font_size = 15, bold = T) %>%
      kbl(booktabs = T, escape = F, col.names = NULL)  %>%  
      kable_styling(latex_options = c("hold_position"))) 
  
  lw<-new$log_length/new$log_weight
  
  ## Calculate the mean and sd
  smean <- mean(lw, na.rm = TRUE)
  sds <-  sd(lw, na.rm = TRUE)
  ## Identify the cells with value greater than cutoff * sd (column wise)
  points <- rbind(new[which(lw >  smean + (4 * sds)), ], new[which(lw <  smean - (4 * sds)), ])
  
  plot(new$log_length, new$log_weight, pch = 16, cex = 1,
        main = paste(" Art:", sps[i],"- Kvartal:", quarter, sep=" "),
        xlab = "Log(Længde) (mm)",
        ylab = "Log(Vægt) (kg)",
        cex.main = 1.5,
        cex.lab = 1.5)+
     points(points$log_length, points$log_weight, pch = 16, cex = 1, col = "red")
  
    
  db_diff <- points[, c("year", "trip", "station", "speciesCode",
                        "landingCategory", "individNum", "length", "weight")]
 } 
}
temp<-lapply(1:length(sps), fun) #funktion to get data and run the loop/function
db_diff<-data.frame(do.call("rbind", temp)) #make data frame from the temp file 


if (nrow(data.frame(db_diff)) >0) {
  
  # Output table of outliers in latex table format
  
  cat("\\newpage") 
  
  db_diff <- db_diff[order(db_diff$speciesCode),]
  #Make table
  db_diff %>%      
          kbl(escape = F, longtable = T, booktabs = T, linesep = "", row.names = F,
              col.names = c("År", "Tur", "Station", "Art", "Landings-kategori", 
                            "individ-nummer", "Længde (mm)", "Vægt (kg)"), align = "l") %>%
          row_spec(0, bold = TRUE) %>%
          kable_styling(latex_options = c("striped", "hold_position")) %>%
          column_spec(1:8, width = "1.2cm")
  
} else {
  #message if no outliers where found
  text<-c("Ingen afvigelser i Længde-vægt forhold")
  #Make table
  text %>% 
      cell_spec(color = "green", font_size = 15, bold = T) %>%
      kbl(booktabs = T, escape = F, col.names = NULL)  %>%  
      kable_styling(latex_options = c("hold_position"))
}

} else {
  #message if no measured fish is present for the given period
  text<-c("Ingen Enkeltfisk")
  #Make table
  text %>% 
      cell_spec(color = "blue", font_size = 15, bold = T) %>%
      kbl(booktabs = T, escape = F, col.names = NULL)  %>%  
      kable_styling(latex_options = c("hold_position"))
}
```


\newpage{}
\subsection{Lændge-alder forhold}
I graferne nedenfor er plottet længde-alder-forhold for alle individfisk fra turene, i det valgte år, kvartal og togt. Det skraverede område representere de tidligere års spreding (prediktions intervallet), de Blå punkter følger derved tidligere år, og de Røde punkter representere afvigelse fra det forventede. Dette udregnes automatisk, og det kan derfor forekomme at individer med helt fine længde-alder forhold betragtes som afvigelser. \

I den efterfølgende tabel er listet de individer, hvor der forekommer at være en afvigelse for den valgte periode og tidligere år. 


\renewcommand{\arraystretch}{1}

```{r ,echo=FALSE,results='asis', cache=FALSE, message=FALSE, warning=FALSE, fig.width=12, fig.height=7}
if (length(sps) > 0){
## Plot length - age relations ----------------------------------------------

  # Select lines form age data where age and length is known.. 
age_ind <- age[!is.na(age$length) & !is.na(age$age), ]

if (nrow(data.frame(age_ind))>0){
  #add id column to keep track of rows
  age_ind$id<-c(1:nrow(age_ind))
  #Loop through each species and plot
  fun <- function(i) {
  #subset data by sepcies  
  df_sps <- age_ind[age_ind$speciesCode==sps[i],]
  
  #break down data into the new and old, data. NOTE: all data is from same quarter, as relations changes with the season
  new <- df_sps[df_sps$year == year & df_sps$trip %in% trip$trip, ]
  old <- df_sps[df_sps$id %!in% new$id, ]
  
  if (nrow(old) > 0 & nrow(new)> 0 & FALSE %!in% (new$age %in% old$age)) { 
  #make a polynomial model, the age-length relationship is not linear, and quite complex, and varies from spoecies to soecies. to simplify a simple model is fitted, and deviation from previus years should therby be visible
  mod2 = lm(age ~ poly(length, 2), data = old)
  
  summary<- summary(mod2)
  if (summary[["adj.r.squared"]] > 0.2){
  #estimate the prediction interval, with evenly genrated numbers based on data range
  sim.dat = seq(min(old$length), max(old$length), length.out=nrow(old))
  preds <- predict(mod2, newdata = data.frame(length=sim.dat), level=0.999, interval = 'prediction')
 
  #put the "new"/relevant data trough the model made with the old data, to see how well it follows the given trend
  preds2 <- predict(mod2, newdata = data.frame(length=new$length), level=0.999, interval = 'prediction')
  #select data within the preiction interval, and therby finding outliers
  insideInterval <- new[new$age > preds2[,'lwr'] & new$age < preds2[,'upr'], ]
 
  #plot. firstly the confidence band and trend from old data, but without old dataponts (overidden with white points)
 #secondly, plot the new data (in red), and data within confidence interval (in blue). overlapping points so as to visualise the putliers
  plot(old$length, old$age, pch = 16, cex = 0.1, 
        main = paste(" Art:", sps[i],"- Kvartal:", quarter, sep=" "),
        xlab = "Længde (mm)",
        ylab = "Alder (år)",
        cex.main = 1.5,
        cex.lab = 1.5)+ 
     points(old$length, old$age, pch = 16, cex = 0.2, col = "white")+
     lines(sort(old$length), fitted(mod2)[order(old$length)], col='red', lwd=3)+
     polygon(c(rev(sim.dat), sim.dat), 
             c(rev(preds[ ,3]), preds[ ,2]), density=10, col = 'blue', border = NA)+
     lines(sim.dat, preds[ ,3], lty = 'dashed', col = 'red')+
     lines(sim.dat, preds[ ,2], lty = 'dashed', col = 'red')+
     points(new$length, new$age, pch = 16, cex = 1, col = "red")+
     points(insideInterval$length, insideInterval$age, pch = 16, cex = 1, col = "blue")
    
  #the new data NOT inside the interval, previously defined
  db_diff <- new[new$id %!in% insideInterval$id, ] 
  #Remove the duplicates, that comes from the "number" column treatment
  db_diff <- db_diff[!duplicated(db_diff[, 6:11]), ]
  
  # Make table of outliers, 
  db_diff <- db_diff[ , 
                   c("year", "cruise", "trip", "speciesCode", 
                     "landingCategory", "individNum", "length", "age", "sexCode")]
    
    } else {
      #message if the model has r^2 adjusted, below 0.2
      text<-c(paste0("Statistisk model fejlede for", sps[i], "Prøver Simpler Metode"))
      #Make table
      print(text %>% 
                cell_spec(color = "red", font_size = 15, bold = T) %>%
                kbl(booktabs = T, escape = F, col.names = NULL)  %>%  
                kable_styling(latex_options = c("hold_position")))
    }
  } else if (nrow(new) > 0){ 
    #If not enough data, or model fails, use simpler method, where each length group is tested seperetly
      text<-c(paste0("Bruger Kun Data fra Valgte Kvartal for ", sps[i]))
      #Make table
      print(text %>% 
          cell_spec(color = "blue", font_size = 15, bold = T) %>%
          kbl(booktabs = T, escape = F, col.names = NULL)  %>%  
          kable_styling(latex_options = c("hold_position")))
  
      #subset by age group
      ID <- unique(new$age)
      fun <- function(ii) {
        a <- new[new$age == ID[ii], ]

        ## Calculate the mean and sd
        smean <- mean(a$length, na.rm = TRUE)
        sds <-  sd(a$length, na.rm = TRUE)
        ## Identify the cells with value greater than cutoff * sd (column wise)
        points <- rbind(a[which(a$length >  smean + (3 * sds)), ],
                        a[which(a$length <  smean - (3 * sds)), ])
      }
      temp<-lapply(1:length(ID), fun) #funktion to get data and run the loop/function
      outliers<-data.frame(do.call("rbind", temp)) #make data frame from the temp file
    
      ## Plot the data, by species by area, with outliers in red
      plot(new$age, new$length, col = "white",
           main = paste(paste0(sps[i], " - Alder ved Længde")),
           xlab = "Alder (år)",
           ylab = "Længde [mm]")+
        grid()+
        points(new$age, new$length, pch = 16, cex = 1, col = "blue")+
        points(outliers$age, outliers$length, pch = 16, cex = 1, col = "red")

      db_diff <- outliers[ , c("year", "cruise", "trip", "speciesCode", 
                               "landingCategory", "individNum", "length", "age", "sexCode")]
 
  
  } else {
    #message of no age data is available, for a species, where weight data is availeble
      text<-c(paste0("Ingen Alders Data for ", sps[i]))
      #Make table
      print(text %>% 
          cell_spec(color = "red", font_size = 15, bold = T) %>%
          kbl(booktabs = T, escape = F, col.names = NULL)  %>%  
          kable_styling(latex_options = c("hold_position")))
      
      db_diff <- c()
   }
  }
  temp<-lapply(1:length(sps), fun)
  db_diff<-do.call("rbind", temp)
  
  
  if (nrow(data.frame(db_diff))>0) {
    
    cat("\\newpage") 
    
    #make Table over outliers
    print(db_diff %>%      
          kbl(escape = F, longtable = T, booktabs = T, linesep = "", row.names = F,
              col.names = c("År", "Tur", "Station", "Art", "Landings-kategori", 
                            "individ-nummer", "Længde (mm)", "Alder (år)", "Køn"), align = "l") %>%
          row_spec(0, bold = TRUE) %>%
          kable_styling(latex_options = c("striped", "hold_position")) %>%
          column_spec(1:9, width = "1.5cm"))
    library(Hmisc)
    # Output table of outliers in latex table format
    
  } else {
    #message if no outliers are found
  text<-c("Ingen afvigelser i Længde-alder forhold")
  #Make table
  print(text %>% 
      cell_spec(color = "green", font_size = 15, bold = T) %>%
      kbl(booktabs = T, escape = F, col.names = NULL)  %>%  
      kable_styling(latex_options = c("hold_position")))
} 
  
}else{
  #message if no age data is available for any of the species
  text<-c("Ingen Aldersdata, fra Valgte Togt og Periode")
  
  print(text %>% 
      cell_spec(color = "red", font_size = 15, bold = T) %>%
      kbl(booktabs = T, escape = F, col.names = NULL)  %>%  
      kable_styling(latex_options = c("hold_position")))
} 
} else {
  #message if no fish is in station (skips from the top of this chuck)
  text<-c("Ingen Enkeltfisk")
  #Make table
  text %>% 
      cell_spec(color = "blue", font_size = 15, bold = T) %>%
      kbl(booktabs = T, escape = F, col.names = NULL)  %>%  
      kable_styling(latex_options = c("hold_position"))
}
```
