---
fontsize: 12pt
geometry: top=2cm, bottom=2cm, left=1.5cm, right=1.5cm
header-includes:
- \usepackage{tabularx}
- \usepackage{tcolorbox}
output: pdf_document
---

<!-- 
Extract data on single fish. 
Raw data and total number of fish per year/cruise/area/species 
-->
  
<!-- change font type -->
\renewcommand{\familydefault}{\sfdefault}
\sffamily

```{r set_libraries, include=FALSE}

#Libraries
if (!require(sqldf)) {
  install.packages("sqldf", repos="http://ftp.ussg.iu.edu/CRAN/")
  library(sqldf)
}
if (!require(RODBC)) {
  install.packages("RODBC", repos="http://ftp.ussg.iu.edu/CRAN/")
  library(RODBC)
}
if (!require(xtable)) {
  install.packages("xtable", repos="http://ftp.ussg.iu.edu/CRAN/")
  library(xtable)
}
if (!require(dplyr)) {
  install.packages("dplyr", repos="http://ftp.ussg.iu.edu/CRAN/")
  library(dplyr)
}
if (!require(plyr)) {
  install.packages("plyr", repos="http://ftp.ussg.iu.edu/CRAN/")
  library(plyr)
}

```

```{r set_paramters, echo=FALSE, message=FALSE, warning=FALSE}

# Parameters
#year_min <-  @paramYearMin
#year_max <-  @paramYearMax
#cruise_in <- c(@paramCruise)
#level <- @paramLevel
#levelSpatial <- @paramLevelSpatial

# Paramters to use in R
year_min <-  2016
year_max <-  2016
cruise_in <- c('BITS-1')
level <- "Tur"
levelSpatial <- "Område"

```

\begin{tcolorbox}[colback=white!5,colframe=blue!40!black,title=Information om udtrækket,width=15cm]
\renewcommand{\arraystretch}{1.2}
\begin{tabularx}{13cm}{@{}lXr@{}}
\textbf{År} & `r year_min` - `r year_max` & \\ 
\textbf{Togt(er)} & `r c(cruise_in)` & \\
\textbf{Aggregeringsnivau (togt/tur/station)} & `r level` & \\
\textbf{Aggregeringsnivau (område/square)} & `r levelSpatial` & 
\end{tabularx}
\end{tcolorbox}

```{r get_data, echo=FALSE, message=FALSE, warning=FALSE}

channel <- odbcConnect("FishLineDW")
data <- sqlQuery(channel, paste("SELECT     slr.year, slr.cruise, slr.trip, slr.station,
                                            slr.quarterGearStart AS quarter, slr.dfuArea AS icesArea, 
                                            slr.statisticalRectangle AS icesSquare, slr.speciesCode, 
                                            sp.dkName AS species_dk, sp.ukName AS species_uk,
                                            sp.latin AS speices_latin, SUM(slr.weightTotal) AS totWeight_kg
                                 FROM       SpeciesListRaised AS slr INNER JOIN
                                                      L_Species AS sp ON slr.speciesCode = sp.speciesCode
                                 WHERE      slr.year between ",year_min," AND ",year_max,"  AND 
                                            slr.cruise IN ('",paste(cruise_in,collapse = "','"),"') AND
                                            slr.speciesCode <> 'DTO'
                                 GROUP BY   slr.year, slr.cruise, slr.trip, slr.station, slr.quarterGearStart, 
                                            slr.dfuArea, slr.statisticalRectangle, slr.speciesCode, 
                                            sp.dkName, sp.ukName, sp.latin
                                                   " ,sep=""), stringsAsFactors=FALSE)

close(channel)


```

```{r do_analysis, include=FALSE}

# Depending on chosen aggregation level get parameters to
# do aggregation on.
if (level == "Togt") {
    param <- colnames(select(data, -c(trip,station,totWeight_kg)))
} else if (level == "Tur") {
    param <- colnames(select(data, -c(station,totWeight_kg) ))
} else if (level == "Station") {
    param <- colnames(select(data, -totWeight_kg))
}

# If chosen ICES area for spation aggregation, 
# remove parameter square from aggregation parameters
if (levelSpatial == "Område") {
    param <- param[!param %in% "icesSquare"]
}


# Do aggreation and order data
data_level <- ddply(data, param, summarise, 
                    totWeight_kg = sum(totWeight_kg, na.rm = TRUE))
data_out <- data_level[with(data_level, 
                            order(year, cruise, quarter, speciesCode)),]


```

```{r make_output, include = FALSE }

write.csv(data_out, paste0("SpeciesCatch_",year_min,"-",year_max,"_",
                           format(Sys.Date(),"%d%m%y"),".csv"),
          row.names = FALSE, quote= FALSE)


```

