---
fontsize: 11pt
geometry: top=1in, bottom=1in, left=0.8in, right=0.8in
header-includes:
- \usepackage{booktabs}
- \usepackage{longtable}
- \usepackage{floatrow}
- \usepackage[T1]{fontenc}
- \usepackage[danish]{babel}
- \usepackage[utf8]{inputenc}
- \usepackage{graphicx}
- \floatsetup[table]{capposition=bottom}
- \usepackage{fancyhdr}
- \pagestyle{fancy}
- \fancyhf{}
- \fancyfoot[R]{\thepage}
- \usepackage[table]{}
- \usepackage{rotating}
- \usepackage{ragged2e}
- \usepackage{catchfile}
- \usepackage{array}
- \usepackage[export]{adjustbox}
- \usepackage{multirow}
- \linespread{1.15}
- \usepackage{tabularx}
- \usepackage{tcolorbox}
- \usepackage{lipsum}
- \usepackage{makecell}
- \usepackage{etoolbox}
- \usepackage{colortbl}
- \usepackage{lscape}
- \usepackage{caption}
output:
  pdf_document: 
    number_sections: yes
---

\pagenumbering{arabic}

\renewcommand{\familydefault}{\sfdefault}
\def\Tiny{\fontsize{5pt}{5pt}\selectfont}

\sffamily
\def\figurename{Figure}
\def\tablename{Table}


```{r libraries, include=FALSE}

library(xtable)
library(sqldf)
library(plyr)
library(RODBC)
library(ggplot2)
library(grid)
library(gridExtra)
library(plyr)
library(lubridate)
library(reshape2)

```


```{r table_setup, echo=FALSE, results='asis',message=FALSE,warning=FALSE}

######### Setup to use in xtable prints ###################### 

bold <- function(x) {paste('{\\textbf{',x,'}}', sep ='')}
gray <- function(x) {paste('{\\textcolor{gray}{',x,'}}', sep ='')}

addtorow          <- list()
addtorow$pos      <- list()
addtorow$pos[[1]] <- c(0)
addtorow$command  <- c(paste("\\hline \n",
                             "\\endhead \n",
                             "\\hline \n",
                             #"{\\footnotesize Continued on next page} \n",
                             "\\endfoot \n",
                             "\\endlastfoot \n",sep=""))

```


```{r setup, include=FALSE}

cruise <- @paramCruise
year <- @paramYear


cruiseNo <- 10
plannedHauls <- 50
quarter <- 3
  
```



```{r info_cruise, echo=FALSE, message=FALSE, warning=FALSE,include=FALSE}

query1<-paste("SELECT Trip.year,Trip.contactPersonName,Trip.contactPersonId , Trip.trip, Trip.cruise, tripLeaderName, dateStart, dateEnd, platform1
              FROM Trip
              WHERE     (Trip.year = ",year," and Trip.cruise='",cruise,"')"
             ,sep = "")
query1


query2 <-paste("SELECT     Animal.year, Animal.cruise, Animal.speciesCode, Animal.representative, Animal.individNum, 
                           Animal.number, Animal.length, Animal.weight,Animal.statisticalRectangle as ICESsquare
                FROM       Animal
                WHERE     (Animal.year=",year," and Animal.cruise='",cruise,"')"
                            ,sep = "")
query2

query4<-paste("SELECT Sample.station, Sample.fishingtime, Sample.latPosStartDec AS lat, Sample.lonPosStartDec AS lon, 
                      Sample.gearType,Sample.gearQuality,Sample.haulType, Sample.selectionDevice,Sample.meshSize, Sample.dfuArea,
                      Sample.statisticalRectangle,Sample.quarterGearStart,
                      Sample.netOpening,Sample.wireLength as warpLength, Sample.otterBoardDist as DoorSpread,
                      Sample.depthAvg,Sample.windDirection,Sample.windSpeed, Sample.dateGearStart
              FROM Sample
              WHERE     (Sample.year=",year," and Sample.cruise='",cruise,"')"
              ,sep = "")
query4


channel <- odbcConnect("FishLineDW")
data1 <- sqlQuery(channel, paste(query1),stringsAsFactors=FALSE)
data_animal <- sqlQuery(channel, paste(query2),stringsAsFactors=FALSE)
data_sample <- sqlQuery(channel, paste(query4),stringsAsFactors=FALSE)
close(channel)

data1 <- with(data1, data1[order(data1$dateStart),])


cruise2 <- ifelse(cruise %in% c('Torsk','2262-Torsk'),"Torsk",ifelse(tolower(cruise)=='tunger',"Tunger",substr(cruise,1,4)))
Quarter <- unique(quarter(data1$dateStart),quarter(data1$dateEnd) )
StartDate <- ifelse(nrow(data1)==1,format(data1$dateStart,"%d-%m-%Y"),format(data1$dateStart[1],"%d-%m-%Y"))
EndDate <- ifelse(nrow(data1)==1,format(data1$dateEnd,"%d-%m-%Y"),format(data1$dateEnd[nrow(data1)],"%d-%m-%Y"))


StartTime <- paste0(format(data1$dateStart,"%H"),":00")
EndTime <- paste0(format(data1$dateEnd,"%H"),":00")



cruiseName <- ifelse(substr(cruise,1,4) %in% c("IBTS","BITS","KASU"),substr(cruise,1,4),cruise)
ship <- ifelse(substr(cruise,1,4) %in% c("IBTS","BITS"),"R/V DANA",ifelse(substr(cruise,1,4)=="KASU","Havfisken",paste(unique(data1$platform1), collapse=', ' )))  

cruise_title2 <- ifelse(substr(cruise,1,4)=="IBTS","International Bottom Trawl Survey",ifelse(substr(cruise,1,4)=="BITS",
                                                                                              "Baltic International Trawl Survey",""))
#cruise_title <- ifelse(substr(cruise,1,4) %in% c("IBTS","BITS","KASU"),paste0(cruiseName," ",Quarter[1],"Q"," ",year),cruiseName)
cruise_title <- ifelse(length(unique(Quarter))==1,paste0(cruiseName," ",Quarter,"Q"," ",year),
                   paste(cruiseName, paste0(Quarter,"Q"," ",year, collapse = "\\& ")))

TripNum <- ifelse(nrow(data1)>1,"MT","ST")

```

<!-- definere forside -->




\thispagestyle{empty}

<!--

\vspace*{-1cm}


\vspace{-0.9cm}


\begin{figure}[H]
        \flushright
        \includegraphics[width=10cm]{X:/Line/Togtrapport/logotilkort.png}
\end{figure}

\vspace*{0.5cm}

-->

\noindent\textcolor{gray}{\rule{0.6\textwidth}{1pt}}\par

\textcolor{gray}{\Large DTU Aqua - Cruise report}

\vspace*{3cm}



\textbf{\Huge `r cruise_title`}\

\vspace*{-0.3cm}

\textbf{\it{\Large `r cruise_title2`}}\

\vspace*{1cm}

\textbf{\Huge `r ship`}

\vspace*{0.3cm}

\textbf{\Huge Denmark}

\vspace*{0.5cm}

\textbf{\large Cruise no. `r cruiseNo`}\

\textbf{\large From `r StartDate` to `r EndDate`}



\vfill
              
DTU Aqua\
Charlottenlund Slot\
2920 Charlottenlund\
Denmark




\newpage


<!-- define header -->


\chead{\footnotesize `r cruise_title`}
\lhead{\footnotesize Cruise report }
\rhead{\footnotesize `r StartDate` - `r EndDate`}



\vspace*{0.01cm}

\renewcommand{\contentsname}{Contents}
\tableofcontents

\newpage



#Cruise summary
\vspace{0.3cm}

\newcolumntype{s}{>{\hsize=.4\hsize}X}
\newcolumntype{u}{>{\hsize=1\hsize}X}
\newcolumntype{t}{>{\hsize=0.6\hsize}X}


\subsubsection*{General information}
\vspace{-0.5cm}



\renewcommand{\arraystretch}{1}
\renewcommand{\tabcolsep}{5pt}
\begin{tabularx}{0.93\textwidth}{utst}
        &\textbf{}   & \textbf{} &  \textbf{} \\
\it{Cruise} & `r cruiseName`  &  &  \\
\it{Cruise number} & ??  & &  \\
\it{Reseach vessel(s)}   & `r ship` &   &  \\
\it{Year and quarter}   & `r paste0(Quarter[1],"Q")` `r year`&   &  \\
\it{Country}    & Denmark & & 
\end{tabularx}



\vspace{0.3cm}

\subsubsection*{Location and time}

\vspace{-0.2cm}


\rowcolors{1}{}{white}


\newcommand{\abTN}{`r TripNum`}

\newcommand{\aORbTN}[1]{%
        \edef\mytemp{{#1}}%
        \expandafter\ifstrequal\mytemp{ST}{

\renewcommand{\arraystretch}{1.1}
\renewcommand{\tabcolsep}{5pt}
\begin{tabularx}{0.93\textwidth}{utst}
        &\textbf{Date}   & \textbf{Time} &  \textbf{Port} \\
\hline
\it{Departure} & `r StartDate`  & `r StartTime` & Copenhagen \\
\it{Arrival}   & `r EndDate`    & `r EndTime`   & Rønne \\
\it{Staff and crew exchange}    & `r EndDate` & & Ystad
\end{tabularx}


  }{} %
    \expandafter\ifstrequal\mytemp{MT}{
        
        
        
        
        
        }{}%
}



\aORbTN{\abTN}



```{r tripInfo, results='asis',echo=FALSE,message=FALSE,warning=FALSE}


if (TripNum=="MT") {

    tripInfo <- data1[,c("trip","dateStart","dateEnd","platform1")]

    tripInfo$dateStart <- paste0(format(data1$dateStart,"%d-%m-%Y %H"),":00")
    tripInfo$dateEnd <- paste0(format(data1$dateEnd,"%d-%m-%Y %H"),":00")
    
 
    trip_table <- xtable(tripInfo)
    colnames(trip_table) <- c("Trip no.","Start date and time", "End date and time","Ship")
    align(trip_table) <- "lp{3cm}p{5cm}p{5cm}p{2.5cm}"
    
    print(trip_table,include.rownames=FALSE, sanitize.colnames.function=bold)

}
     

```


\vspace{0.5cm}



\subsubsection*{Participants}


\
\renewcommand{\arraystretch}{1}
\renewcommand{\tabcolsep}{28pt}



\newpage



