---
fontsize: 12pt
geometry: top=0.2cm, bottom=1.2cm, left=0.5cm, right=0.5cm
header-includes:
- \usepackage{booktabs}
- \usepackage{longtable}
- \usepackage{floatrow}
- \usepackage[T1]{fontenc}
- \usepackage[danish]{babel}
- \usepackage[utf8]{inputenc}
- \usepackage{graphicx}
- \floatsetup[table]{capposition=top}
- \usepackage[table]{xcolor}
- \usepackage{ragged2e}
- \usepackage{catchfile}
- \usepackage{array}
- \usepackage[export]{adjustbox}
- \usepackage{multirow}
- \linespread{1.15}
- \usepackage{tabularx}
- \usepackage{tcolorbox}
- \usepackage{lipsum}
- \usepackage{pbox}
output:
  pdf_document: default
word_document: default
---
  
  \renewcommand{\familydefault}{\sfdefault}
\sffamily


```{r , include=F}
# @paramCruise
# SELECT c.cruise, c.cruise
# FROM FishLineDW.dbo.Cruise c
# WHERE c.year = @paramYear
# 
# @paramTrip
# SELECT t.tripType + ' - ' +t.trip, t.trip
# FROM FishLineDW.dbo.Trip t
# WHERE t.year = @paramYear
#   AND t.cruise = @paramCruise
# ORDER BY t.tripType + ' - ' + t.trip DESC
# 
# @paramStation
# SELECT 'Station ' + s.station, s.station
# FROM FishLineDW.dbo.Sample s
# WHERE s.year = @paramYear
#   AND s.cruise = @paramCruise
#   AND s.trip = @paramTrip
# ORDER BY s.station DESC
# 
# @paramJournal
# SELECT s.labJournalNum, s.labJournalNum
# FROM FishLineDW.dbo.Sample s
# WHERE s.year = @paramYear
#   AND s.cruise = @paramCruise
#   AND s.trip = @paramTrip
#   AND s.station = @paramStation
# ORDER BY s.labJournalNum DESC
# 
# @paramSpecies
# SELECT A.speciesCode + ' - '+ ISNULL(s.dkName, ''), A.speciesCode
# FROM FishLineDW.dbo.Sample sa 
# INNER JOIN FishLineDW.dbo.SpeciesList sp 
#         ON sp.sampleId = sa.sampleId
# INNER JOIN FishLineDW.dbo.Animal A 
#         ON A.speciesListId = sp.speciesListId 
# LEFT OUTER JOIN FishLine.dbo.L_Species s 
#         ON s.speciesCode = A.speciesCode
# WHERE A.year = @paramYear
#   AND A.cruise = @paramCruise
#   AND A.trip = @paramTrip
#   AND A.station = @paramStation
#   AND A.individNum != 0
# GROUP BY s.dkName, A.speciesCode
# ORDER BY A.speciesCode + ' - ' + ISNULL(s.dkName, '')
```


```{r define_input, echo=FALSE}

#Parameters
# year <- @paramYear
# cruise <- @paramCruise
# trip <- @paramTrip
# station <- @paramStation
# journal <- @paramJournal 
# species <- @paramSpecies

year <- 2019
cruise <- "KASU-1"
trip <- "1"
station <- "21"
journal <- ""
species <- "TOR"

```




```{r set_libraries, include=FALSE}

#Libraries
if (!require(sqldf)) {
  install.packages("sqldf", repos="http://ftp.ussg.iu.edu/CRAN/")
  library(sqldf)
}
if (!require(RODBC)) {
  install.packages("RODBC", repos="http://ftp.ussg.iu.edu/CRAN/")
  library(RODBC)
}
if (!require(xtable)) {
  install.packages("xtable", repos="http://ftp.ussg.iu.edu/CRAN/")
  library(xtable)
}

```

```{r, echo=FALSE, message=FALSE, warning=FALSE}


channel <- odbcConnect("FishLineDW")
data <- sqlQuery(channel, paste("SELECT     Animal.animalId, Animal.year, Animal.cruise, Animal.trip, Animal.tripType, 
                                Animal.station, Animal.dateGearStart,Animal.dfuArea, Animal.statisticalRectangle,
                                Animal.speciesCode, Animal.landingCategory, 
                                Animal.representative, Animal.sizeSortingEU as sorting,
                                Animal.individNum, Animal.number, Animal.length, Animal.weight, Animal.sexCode, 
                                Animal.maturityIndex, Age.age, Sample.labJournalNum,Trip.harbourLanding as havn
                                FROM       Animal INNER JOIN
                                SpeciesList ON Animal.speciesListId = SpeciesList.speciesListId INNER JOIN
                                Sample ON SpeciesList.sampleId = Sample.sampleId INNER JOIN
                                Trip ON Sample.tripId = Trip.tripId LEFT OUTER JOIN
                                Age ON Animal.animalId = Age.animalId
                                WHERE      (Animal.year = (",year, ") AND 
                                Animal.trip = ('",trip,"') AND
                                Animal.cruise = ('",cruise,"') AND
                                Animal.station = (",station, ") AND
                                Animal.speciesCode = ('",species, "') AND
                                Animal.individNum != 0  ) " ,sep=""), stringsAsFactors=FALSE)                        
close(channel)

date <- format(as.Date(data$dateGearStart[1]), "%d-%m-%Y")

```






```{r, echo=FALSE, include=FALSE, cache=FALSE, warning=FALSE}

##make tex-table 1


data[21][is.na(data$labJournalNum),] <- "-"; journal <- data$labJournalNum[1]
data_table <- data[c("sorting", "individNum","length","weight","age","sexCode","maturityIndex","animalId")]
data_table2 <- data_table[order(data_table$sorting,data_table$individNum) ,]
data_table2$comment <- ""
data_table2[data_table2=="FALSE"] <- ""


tbl <- xtable(data_table2)
digits(tbl) <- c(0,0,0,0,3,0,0,0,0,0)
print(tbl,
      only.contents=TRUE,
      include.rownames=FALSE,
      include.colnames=FALSE,
      type="latex",
      file="tblout.tex")


```



\setlength{\tabcolsep}{20pt}
\renewcommand{\arraystretch}{1.2}
\begin{tabularx}{\textwidth}{ l l l l l l}
\textbf{Togt:} `r cruise`  & \textbf{Tur:} `r trip` & \textbf{Station:} `r station` & \textbf{Type:} `r data$tripType[1]` & \textbf{Dato:} `r date`\\
\textbf{Art:} `r species`  & \textbf{Journal:} `r journal` & \textbf{Område:} `r data$dfuArea[1]` & 
  \textbf{Square:} `r data$statisticalRectangle[1]` & \textbf{Havn:} `r data$havn[1]` \\
\end{tabularx}




\vspace{0.5cm}

\CatchFileDef{\tabmacro}{tblout}{}

\newcommand\B{\rule[-1.2ex]{0pt}{0pt}} % Bottom strut

\definecolor{lightgray}{gray}{0.85}
\setlength\LTleft{0.5cm}
\setlength\LTright{0pt}
\setlength{\tabcolsep}{0.8em}
\renewcommand{\arraystretch}{1.1}
\rowcolors{3}{}{lightgray}
\begin{longtable}{l|r|r|r|l|l|l|l|p{3cm}@{} l}
\hline
\rule{0pt}{4ex}
\centering
\pbox{8cm}{\textbf{Sortering} \\  } & \pbox{8cm}{\textbf{Individ} \\ \textbf{fisk}} & \pbox{8cm}{\textbf{Længde} \\ \textbf{(mm)}} & \pbox{8cm}{ \textbf{Vægt} \\ \textbf{(kg)}} & \pbox{8cm}{\textbf{Alder} \\ }
& \pbox{8cm}{\textbf{Køn} \\} & \pbox{8cm}{\textbf{Modenhed} \\ } & \pbox{8cm}{\textbf{ID} \\} &  \pbox{8cm}{\textbf{Kommentar} \\}   \\[0.3cm]

\hline
\endhead


\tabmacro

\end{longtable}





