---
fontsize: 11pt
geometry: top=1in, bottom=1in, left=1in, right=1in
header-includes:
- \usepackage{tabularx}
- \usepackage{tcolorbox}
output: pdf_document
---

<!-- 
Extract data on single fish. 
Raw data and total number of fish per year/cruise/area/species 
-->

<!-- change font type -->
\renewcommand{\familydefault}{\sfdefault}
\sffamily


```{r set_libraries, include=FALSE}

#Libraries
if (!require(sqldf)) {
  install.packages("sqldf", repos="http://ftp.ussg.iu.edu/CRAN/")
  library(sqldf)
}
if (!require(RODBC)) {
  install.packages("RODBC", repos="http://ftp.ussg.iu.edu/CRAN/")
  library(RODBC)
}
if (!require(plyr)) {
  install.packages("plyr", repos="http://ftp.ussg.iu.edu/CRAN/")
  library(plyr)
}

```

```{r set_parameters, include=FALSE}

y1 <- @paramYear1
y2 <- @paramYear2
cruise_val <- c(@paramCruise)
area_val <- c(@paramArea)
species_val <- c(@paramSpecies)

# Paramters to use in R
#y1 <- 2016
#y2 <- 2016
#cruise_val <- c('MON', 'SEAS')
#area_val <- c(21, 22, 23)
#species_val <- c('TNG')

```


```{r get_data, include=FALSE}

channel <- odbcConnect("FishLineDW")
ind_fish <- sqlQuery(channel, paste("SELECT   a.animalId, a.year, a.cruise, a.trip, a.tripType, 
                                              a.station, a.dateGearStart, a.quarterGearStart, 
                                              a.dfuArea, a.statisticalRectangle, a.gearQuality, 
                                              a.gearType, a.meshSize, a.speciesCode, a.sizeSortingEU, 
                                              a.treatment, a.sexCode, a.representative, a.individNum, 
                                              a.number, a.speciesList_number, a.length AS length_mm,
                                              a.weight AS weight_g, a.weight * a.treatmentFactor AS weightUR_g, 
                                              b.age, a.maturityIndex, a.maturityIndexMethod, a.weightGutted, 
                                              a.weightLiver, a.weightGonads, a.numVertebra, 
                                              c.referenceName AS reference
                                     FROM     Animal AS a LEFT OUTER JOIN
                                                 Age AS b ON a.animalId = b.animalId LEFT OUTER JOIN
                                                     R_AnimalReference AS c ON a.animalId = c.animalId
                                     WHERE    (a.individNum > 0) AND 
                                  			  (a.speciesCode IN ('", paste(species_val,collapse = "','"),"')) AND 
                                  			  (a.dfuArea IN ('", paste(area_val,collapse = "','"),"')) AND 
                                              (a.year between ",y1," and ",y2," ) AND
                                              (a.cruise IN ('", paste(cruise_val,collapse = "','"),"')) 
                                  	ORDER BY   a.dateGearStart
                                			        ", sep = ""))

close(channel)


```

```{r summarize, include=FALSE}

# Calculate number of fish per year, cruise, area and species
# Show total number of fish and number of aged/not aged fish 
tot_fish <- ddply(ind_fish, .(year, cruise, dfuArea, speciesCode),
					        summarize, antal = sum(number), 
					        antalAldret = sum(!is.na(age)),
					        antalIkkeAldret = sum(is.na(age)))


```


\section{Data - Enkeltfiskoplysninger}

\vspace{1cm}

\begin{tcolorbox}[colback=white!5,colframe=blue!40!black,title=Information om udtrækket,width=0.7\textwidth]
\renewcommand{\arraystretch}{1.2}
\begin{tabularx}{10cm}{@{}lXr@{}}
\textbf{År (fra)}        & `r y1` & \\ 
\textbf{År (til og med)} & `r y2` & \\ 
\textbf{Togter}          & `r cruise_val` & \\
\textbf{Arter}           & `r species_val` & \\
\textbf{Områder}         & `r area_val` &
\end{tabularx}
\end{tcolorbox}

```{r save_output, echo=FALSE, warning=FALSE,message=FALSE}

#Output single fish information
write.csv(ind_fish, paste0("Enkeltfisk_", format(Sys.Date(), "%d%m%y"), ".csv"),
          quote = FALSE, row.names = FALSE, na = '')

#Output aggregated number of fish per year, cruise, species and area
write.csv(tot_fish, paste0("EnkeltfiskAntal_",format(Sys.Date(),"%d%m%y"),".csv"),
		      quote = FALSE, row.names = FALSE, na = '')

```

