---
fontsize: 10pt
geometry: top=0.2cm, bottom=1.2cm, left=1cm, right=0.5cm
header-includes:
- \usepackage{booktabs}
- \usepackage{longtable}
- \usepackage{floatrow}
- \floatsetup[table]{capposition=top}
- \usepackage[table]{}
- \usepackage{catchfile}
- \usepackage{array}
- \usepackage[export]{adjustbox}
- \usepackage{multirow}
- \linespread{1.15}
- \usepackage{tabularx}
- \usepackage{tcolorbox}
- \usepackage{pbox}
output:
  pdf_document: default
word_document: default
---
  
  \renewcommand{\familydefault}{\sfdefault}
\sffamily


```{r define_input, echo=FALSE}

#Parameters
year <- @paramYear
cruise <- @paramCruise
trip <- @paramTrip
station <- @paramStation
journal <- @paramJournal
species <- @paramSpecies
opdeling <- @paramOpdeling

opdelingSQL <- paste0(opdeling,collapse = "','")

# year <- 2018
# cruise <- 'IN-LYNG'
# trip <- '617'
# station <- '617'
# journal <- ""
# species <- "SIL"
```




```{r set_libraries, include=FALSE}

#Libraries
if (!require(sqldf)) {
  install.packages("sqldf", repos="http://ftp.ussg.iu.edu/CRAN/")
  library(sqldf)
}
if (!require(RODBC)) {
  install.packages("RODBC", repos="http://ftp.ussg.iu.edu/CRAN/")
  library(RODBC)
}
if (!require(xtable)) {
  install.packages("xtable", repos="http://ftp.ussg.iu.edu/CRAN/")
  library(xtable)
}
if (!require(tinytex)) {
  install.packages("tinytex", repos="http://ftp.ussg.iu.edu/CRAN/")
  library(tinytex)
}

```

```{r, echo=FALSE, message=FALSE, warning=FALSE}


channel <- odbcConnect("FishLineDW")
data <- sqlQuery(channel, sprintf("SELECT     Animal.animalId, Animal.year, Animal.cruise, Animal.trip, Animal.tripType, 
                                Animal.station, Animal.dateGearStart,Animal.dfuArea, Animal.statisticalRectangle,
                                Animal.speciesCode, Animal.landingCategory, 
                                Animal.representative, Animal.sizeSortingEU as sorting, Animal.sizeSortingDFU as opdeling, 
                                Animal.individNum, Animal.number, Animal.length, Animal.weight, Animal.sexCode, 
                                Animal.maturityIndex, Age.age, Sample.labJournalNum,Trip.harbourLanding as havn
                                FROM       Animal INNER JOIN
                                SpeciesList ON Animal.speciesListId = SpeciesList.speciesListId INNER JOIN
                                Sample ON SpeciesList.sampleId = Sample.sampleId INNER JOIN
                                Trip ON Sample.tripId = Trip.tripId LEFT OUTER JOIN
                                Age ON Animal.animalId = Age.animalId
                                WHERE      (Animal.year = (%s) AND 
                                Animal.trip = ('%s') AND
                                Animal.cruise = ('%s') AND
                                Animal.station = ('%s') AND
                                Animal.speciesCode = ('%s') AND
                                Animal.individNum != 0  ) " ,
                                year, trip, cruise, station, species), stringsAsFactors=FALSE, as.is=T)                        
close(channel)

if (opdeling != "") {
  data <- subset(data, opdeling ==  @paramOpdeling)
} else {
  data <- data
}
                          

data$opdeling[data$opdeling == "SMÅ"] <- "SMA"

data$weight <- as.numeric(data$weight)

date <- format(as.Date(data$dateGearStart[1]), "%d-%m-%Y")

```






```{r, echo=FALSE, include=FALSE, cache=FALSE, warning=FALSE}

##make tex-table 1


data[21][is.na(data$labJournalNum),] <- "-"; journal <- data$labJournalNum[1]
data_table <- data[c("sorting","opdeling","individNum","length","weight","age","sexCode","maturityIndex","animalId")]
data_table$weight <- as.numeric(data_table$weight)
data_table2 <- data_table[order(data_table$sorting,data_table$individNum) ,]
data_table2$comment <- ""
data_table2[data_table2=="FALSE"] <- ""


tbl <- xtable(data_table2, digits = c(0,0,0,0,0,3,0,0,0,0,0))

print(tbl,
      only.contents=TRUE,
      include.rownames=FALSE,
      include.colnames=FALSE,
      type="latex",
      file="tblout.tex")


```



\setlength{\tabcolsep}{20pt}
\renewcommand{\arraystretch}{1.2}
\begin{tabularx}{\textwidth}{ l l l l l l}
\textbf{Togt:} `r cruise`  & \textbf{Tur:} `r trip` & \textbf{Station:} `r station` & \textbf{Type:} `r data$tripType[1]` & \textbf{Dato:} `r date`\\
\textbf{Art:} `r species`  & \textbf{Journal:} `r journal` & \textbf{Område:} `r data$dfuArea[1]` & 
  \textbf{Square:} `r data$statisticalRectangle[1]` & \textbf{Havn:} `r data$havn[1]` \\
\end{tabularx}




\vspace{0.5cm}

\CatchFileDef{\tabmacro}{tblout}{}

\newcommand\B{\rule[-1.2ex]{0pt}{0pt}} 

\setlength\LTleft{0.5cm}
\setlength\LTright{0pt}
\setlength{\tabcolsep}{0.8em}
\renewcommand{\arraystretch}{1.1}
\begin{longtable}{|l|l|r|r|r|l|l|l|l|p{3.5cm}|}
\hline
\rule{0pt}{4ex}
\centering
\pbox{8cm}{\textbf{Sorte-} \\ \textbf{ring}} &  
\pbox{8cm}{\textbf{Opde-} \\ \textbf{ling}} & 
\pbox{8cm}{\textbf{Individ} \\ \textbf{fisk}} & 
\pbox{8cm}{\textbf{Længde} \\ \textbf{(mm)}} & 
\pbox{8cm}{ \textbf{Vægt} \\ \textbf{(kg)}} & 
\pbox{8cm}{\textbf{Alder} \\ } & 
\pbox{8cm}{\textbf{Køn} \\} & 
\pbox{8cm}{\textbf{Moden-} \\ \textbf{hed}} & 
\pbox{8cm}{\textbf{ID} \\} &  
\pbox{8cm}{\textbf{Kommentar} \\}   
\\[0.3cm]

\hline
\endhead


\tabmacro

\end{longtable}





