---
fontsize: 11pt
geometry: top=2cm, bottom=2cm, left=1.5cm, right=1.5cm,headsep=1cm
header-includes:
- \usepackage[utf8]{inputenc}
- \usepackage{fancyhdr}
- \pagestyle{fancy}
- \fancyfoot{}
- \usepackage{ragged2e}
- \linespread{1.15}
- \usepackage{float}
output: pdf_document
fig_caption: yes
keep_tex: yes
---

```{r set_libraries, include=FALSE, warning=FALSE}
#Libraries used in the r code
if (!require(pacman)){
  install.packages("pacman", repos="http://ftp.ussg.iu.edu/CRAN/")
  library(pacman)
}
p_load(kableExtra, sqldf, RODBC, dplyr)

#special for this script
p_load(sm, ggplot2, ggrepel, dbscan)

'%!in%' <- function(x,y)!('%in%'(x,y)) #a "NOT in" statement

```

```{r set_parameters, include=FALSE}

y1 <- @paramYear1
y2 <- @paramYear2
species <- c(@paramSpecies)
areas <- c(@paramArea)
cruise <- c(@paramCruise)
Q <- c(@paramQuarter)


# Paramters to use in R
# y1 <- 2021
# y2 <- 2022
# species <- c("SPE")
# areas <- c(20, 21, 22, "4A", "4B", "4C")
# cruise <- c("IBTS-1", "IBTS-2", "IN-3 PART", "IN-FISKER", "IN-HIRT", "KASU-1", "KASU-2", "SEAS")
# Q <- c(1, 2, 3, 4)

if (TRUE %!in% (c(1, 2, 3, 4) %in% Q)){
	Q <- c("")
	qtrs <- c(1,2,3,4)
	} else {
	qtrs <- Q
	}
```


```{r get_data, include=FALSE}

channel <- odbcConnect("FishLineDW")
age <- sqlQuery(channel, paste("SELECT   animalId, individNum, year, 
                                              dateGearStart AS date, quarterGearStart AS quarter,
                                              cruise, trip, tripType, station, 
                                              statisticalRectangle, 
                                              speciesCode, treatment, sexCode,
                                              age, agePlusGroup, 
                                              otolithWeight, edgeStructure, otolithReadingRemark,
                                              hatchMonth, hatchMonthRemark,
                                              ageReadId, ageReadName, 
                                              hatchMonthReaderId, hatchMonthReaderName,
                                              genetics, geneticStock, remark AS reamrk_age
                                     FROM     Age
                                     WHERE    (speciesCode IN ('", paste(species,collapse = "','"),"')) AND 
                                  	  	      (dfuArea IN ('", paste(areas,collapse = "','"),"')) AND 
                                              (year between ",y1," and ",y2," ) AND
                                              (cruise IN ('", paste(cruise,collapse = "','"),"')) AND
                                              (quarterGearStart IN ('", paste(qtrs,collapse = "','"),"')) AND 
                                              (individNum != 0) 
                                  	 ORDER BY dateGearStart
                                			        ", sep = ""))

animal <- sqlQuery(channel, paste("SELECT     animalId, year, quarterGearStart AS quarter,
                                              cruise, trip, station, dfuArea AS area, speciesCode, 
                                              speciesListId, 
                                              number, weight, length AS length_mm, 
                                              remark AS remark_animal
                                     FROM     animal
                                     WHERE    (speciesCode IN ('", paste(species,collapse = "','"),"')) AND 
                                  	  	      (dfuArea IN ('", paste(areas,collapse = "','"),"')) AND 
                                              (year between ",y1-4," and ",y2," ) AND
                                              (cruise IN ('", paste(cruise,collapse = "','"),"')) AND
                                              (quarterGearStart IN ('", paste(qtrs,collapse = "','"),"')) AND
                                              (individNum != 0)
                                        ORDER BY dateGearStart
                                			        ", sep = ""))

speciesList <- sqlQuery(channel, paste("SELECT    year, 
                                              cruise, trip, station, speciesCode, speciesListId,
                                              remark AS remark_speciesList
                                     FROM     SpeciesList
                                     WHERE    (speciesCode IN ('", paste(species,collapse = "','"),"')) AND
                                              (dfuArea IN ('", paste(areas,collapse = "','"),"')) AND 
                                              (year between ",y1," and ",y2," ) AND
                                              (cruise IN ('", paste(cruise,collapse = "','"),"'))
                                     ORDER BY dateGearStart
                                			        ", sep = ""))
close(channel)

age <- age[!(is.na(age$otolithReadingRemark) & is.na(age$age)), ]
animal <- animal[animal$weight != 0, ]

merged <- merge(animal, speciesList, by = c("year", "cruise","trip", "station", "speciesCode", "speciesListId"))
merged$speciesListId <- NULL
merged$quarter <- NULL

age_fish <- merge(age, merged, by = c("animalId" ,"year", "cruise","trip", "station", "speciesCode"))

```

```{r export table, include=FALSE}

# ##Output fish-age information
# write.csv2(age_fish, file = "Q:/dfad/users/jostou/home/21_11_11_Julie_reports/results/table.csv",
#            quote = FALSE, row.names = FALSE, na = '')

age_fish <- age_fish %>% relocate(c(number, weight, length_mm), 
                        .before = age)

age_fish <- age_fish %>% relocate(c(area), 
                        .after = station)

write.csv(age_fish, paste0("age_fish_", format(Sys.Date(), "%d%m%y"), ".csv"),
            quote = FALSE, row.names = FALSE, na = '')


#get rid of records where the otolith could not be read, to make analysis esier
age_fish <- age_fish[!is.na(age_fish$age), ]

if ("" %in% Q) {
  age_fish$quarter <- "All"
  animal$quarter <- "All"}
```

\thispagestyle{empty}

\vspace*{1cm} 

\textbf{\huge Data Output and Quality Check of Age}

\vspace{1cm}   

\textbf{\LARGE  Period: `r y1` - `r y2` }\

\textbf{\LARGE  Species: `r species`. }\

\textbf{\LARGE  Quarters: `r Q`. }\

\textbf{\LARGE  cruise: `r cruise`}\

\textbf{\LARGE  Area: `r areas`. }\

\vspace{2cm}

\textcolor{gray}{\LARGE  Data on `r species` was found for the following input}\

\textcolor{gray}{\LARGE  years: `r unique(age_fish$year)`. }\

\textcolor{gray}{\LARGE  Quarters: `r unique(age_fish$quarter)`. }\

\textcolor{gray}{\LARGE  cruise: `r unique(age_fish$cruise)`}\

\textcolor{gray}{\LARGE  Area: `r unique(age_fish$area)`. }\


\newpage

\tableofcontents

\newpage


\section{Introduction}
This report has two parts to it, 1) Overall trends and outliers by species, where all data is pooled together 2) a closer look at the trends and outliers for data further subdivided by year, quarter and area.  

\section{Collected Overview}

The figures here, are plotted with all the age data from all the chosen periods and areas. These plots can be used to generate an overall picture, and spot obvious outliers/mistakes

The first figure is a scatter plot of the age at length relationship, colored and shaped by area. Assuming that each age at length follows it own normal distribution, Outliers are defined as points greater or smaller than mean ± 4·sd. These points are marked in the plot with the animalID.     

The second plot here, is the length frequency of the sex. For most species the trends between females and males should look similar. If the difference between male and female is substantial, this should be considered when looking at outliers. 
\vspace{1cm} 

\small
\renewcommand{\arraystretch}{1.1}
\renewcommand{\tabcolsep}{8pt}


```{r ,echo=FALSE, results='asis', cache=FALSE, message=FALSE, warning=FALSE, fig.width=12, fig.height=7}
if (nrow(age_fish) != 0){
  age_fish$date <- as.Date(age_fish$date, "%y/%m/%d")
  

  ##subset the data, exclude individuals without age, and set area as factor
  fish <- age_fish

  fish$area <- as.factor(fish$area)
  
  ##function to subset the data by age, to look for outliers, assuming each age is its own normal distribution
  ID <- unique(fish$age)
  fun <- function(ii) {
    a <- fish[fish$age == ID[ii], c("animalId", "speciesCode", "cruise", "date", "station", "individNum", 
                                    "area", "sexCode", "length_mm", "age", "otolithReadingRemark")]
    
    ## Calculate the mean and sd
    smean <- mean(a$length_mm, na.rm = TRUE)
    sds <-  sd(a$length_mm, na.rm = TRUE)
    ## Identify the cells with value greater than cutoff * sd (column wise)
    points <- rbind(a[which(a$length_mm >  smean + (4 * sds)), ], 
                    a[which(a$length_mm <  smean - (4 * sds)), ])
  }
  temp<-lapply(1:length(ID), fun) #function to get data and run the loop/function
  points<-data.frame(do.call("rbind", temp)) #make data frame from the temp file 

  ## make scatter plot of the data, with any outliers labeled 
  p1 <- ggplot(fish, aes(x=length_mm, y=age, group=area))+
        geom_point(aes(shape=area, color=area, size = area))+
        theme_bw() +
        labs(x = "Length [mm]", y = "Age")+
        ggtitle(paste0(species, " - Length at Age by Area"))+
        theme(plot.title = element_text(hjust = 0.5))+
        geom_text_repel(data = points, aes(label = animalId), segment.size = 0, 
                               box.padding = unit(0.20, "lines"), color='black')+
        theme(legend.key = element_blank(),
                       axis.title = element_text(size = 14),
                       axis.text = element_text(size=14),
                       legend.text = element_text(size=14),
                       legend.title = element_text(size=14),
                       plot.title=element_text(face="bold", size=18))
  
  ## plot the created plot (needed when ggplot in markdown while in loop/ function)
  plot(p1)
  
  #Make a frequency plot of the length, by sex. where NA, is converted so as to be displayed in the plot
  sex_plot <- fish
  if (TRUE %in% unique(is.na(sex_plot$sexCode))){
  sex_plot[is.na(sex_plot$sexCode), ]$sexCode <- "Not Sexed"
  }
  
  #remove class if it occurs only once (since this will be weird in a frequency plot)
  count <- data.frame(table(sex_plot$sexCode))
  sex_plot <- sex_plot[sex_plot$sexCode %in% count[count$Freq > 1, "Var1"], ]
  
  sex_plot$sexCode <- as.factor(sex_plot$sexCode)
  ##make the frequency plot with sm::sm.density.compare (using "with" for easy data extraction)
  with(sex_plot, {
    # Length frequency plot, pr sex.
    sm.density.compare(length_mm, sexCode, xlab="lengt [mm]", lwd=2)
      title(main=paste0(species, " - Length Distribution by sex"))
      legend("topright", levels(sexCode), fill = c(2:5))
  })
  
  
} else {
  text<-c(paste0("No Ages of ", species, " in the chosen area/cruise"))
  #Make table
  text %>% 
      cell_spec(color = "red", font_size = 15, bold = T) %>%
      kbl(booktabs = T, escape = F, col.names = NULL)  %>%  
      kable_styling(latex_options = c("hold_position")) 
}
```


\newpage
\section{Frequency Plot by year, quarter, area}
Here the length distributions by age is shown, for each area separately. Ages with only one measurement in an area is omitted here.
\vspace{1cm}

```{r ,echo=FALSE, results='asis', cache=FALSE, message=FALSE, warning=FALSE, fig.width=12, fig.height=7}

## subsection data again to plot frequency by species by area, 
#subset again in new loop due to report structure (markdown does not allow break of chunks inside loops or if() statements.

##This time subset with for() loop, since no data needs to be collected, only plot outputs.
if (nrow(age_fish) != 0){
  
  years <- unique(age_fish$year)
   
  for (j in years[1:length(years)]) {
    
    #create headder
    cat(paste0("\n\n## ", "Year ", j, "\n"))
    
    #subset by time
    fish <- age_fish[age_fish$year == j, ]
 
    qtr <- unique(fish$quarter)
    
    for (jj in qtr[1:length(qtr)]){
      fish_q <- fish[fish$quarter == jj, ]
      fish_q$area <- as.factor(fish_q$area)
      
      #create headder
      cat(paste0("\n\n### ", "Quarter ", jj, "\n"))
      #further subset by area
      areas <- unique(fish_q$area)
      for (jjj in areas[1:length(areas)]) {
        area <- fish_q[fish_q$area == jjj, ]
        
        # get the frequency of age by length
        freq <- data.frame(table(area$length_mm, area$age))
        names(freq) <- c("length_mm", "age", "frequency")
        
        # Stacked barplot with multiple groups
        p2 <- ggplot(freq, aes(x=length_mm, y=frequency, fill=age)) +
                geom_bar(stat="identity")+
                theme_bw() +
                labs(x = "Length [mm]", y = "Frequency in Nr")+
                ggtitle(paste0(species, " - ", j, " - Q",jj," - Area ", jjj, " - Histogram of Length by Age"))+
                theme(plot.title = element_text(hjust = 0.5))+
                theme(axis.text.x = element_text(angle = 45, hjust=1))
        
       plot(p2) 
    }
   }  
  }
}  
```

\newpage
\section{Age and Weight at Length for Speceies by area}
Here the length at age by area is looked at in more detail. For each area, the Length at age is plotted, together with the general trend, derived from a nls (non linear least square) model. Outliers are defined with the same assumptions as above, however with greater resolution: smaller than mean ± 3·sd. These points are marked in the plot with red, and listed in a table after the plots. Additionally Weight at length is plotted to look for outliers, here outliers are defined from a liner model.  
\vspace{1cm}

```{r ,echo=FALSE, results='asis', cache=FALSE, message=FALSE, warning=FALSE, fig.width=12, fig.height=7}  
## subsection data again to plot frequency by species by area, (same subset over again due to report structure)
##this time with fuction, as to collect outlier data
if (nrow(age_fish) != 0){
  
    fun <- function(k) {
    
    #create headder
    cat(paste0("\n\n## ", "Year ", years[k], "\n")) 
    ##subset by species
    fish <- age_fish[age_fish$year == years[k], ] 
    qtr <- unique(fish$quarter)
    
    fun <- function(kk) {
      
      #create headder
      cat(paste0("\n\n### ", "Quarter ", qtr[kk], "\n"))
      
      fish_q <- fish[fish$quarter == qtr[kk], ]
      
      fish_q$area <- as.factor(fish_q$area)
    
      anim1 <- animal[animal$quarter == qtr[kk], ]
    
      ##subset by area
      areas <- unique(fish_q$area)
      fun <- function(kkk) {
    
        data <- fish_q[fish_q$area == areas[kkk], ]
        anim <- anim1[anim1$area == areas[kkk], ]
        ##subset by age
        ID <- unique(data$age)
        fun <- function(kkkk) {
          a <- data[data$age == ID[kkkk], ]
          
          if (nrow(a) >= 2){
          
          a$ids <- c(1:nrow(a))
          
          #Local Outlier Factor Score    
          a$lofs <- lof(a[, c("length_mm", "age")], minPts = 2)
          
          lofs <- a[a$lofs > 1 & a$lofs != Inf, ]
          
          ## Calculate the mean and sd
          smean <- mean(a$length_mm, na.rm = TRUE)
          sds <-  sd(a$length_mm, na.rm = TRUE)
          ## Identify the cells with value greater than cutoff * sd (column wise)
          points <- a[a$length_mm <  smean + (2 * sds) & a$length_mm >  smean - (2 * sds), ]
          
          ## exclude points from lof, which are too close to the mean to be outliers
          lofs <- lofs[lofs$ids %!in% points$ids, ]
          
          ## outliers that is far from the mean, but have more than one occurence, so does not get picked up by lof
          points2 <- a[a$length_mm  >  smean + (3.5 * sds) | a$length_mm <  smean - (3.5 * sds), ]
          
          #bind the outliers, but exclude rows that has already been found, as to avoid duplicates
          outliers <- rbind(lofs, points2[points2$ids %!in% lofs$ids, ])
          } else outliers <- c()
      }
      temp<-lapply(1:length(ID), fun) #funktion to get data and run the loop/function
      outliers<-data.frame(do.call("rbind", temp)) #make data frame from the temp file
      
      ##make a fitted line, by fitting data with non linear least square model
      try(lm_fit <- nls(length_mm ~ SSlogis(age, Asym, xmid, scal), data = data), silent = TRUE)
      if (exists("lm_fit")) {
      ## Plot the data, by species by area, with outliers in red, and trend line in red
      plot(data$age, data$length_mm, col = "white",
           main = paste(paste0(species, " - ", years[k], " - Q",qtr[kk],
                               " - Area ", areas[kkk], " - Age at Length")),
           xlab = "Age",
           ylab = "Length [mm]",
           cex.main = 1.5,
           cex.lab = 1.5,
           xaxt="n")+
        axis(1,at=unique(data$age),labels=unique(data$age))+
        grid()+
        lines(sort(data$age), fitted(lm_fit)[order(data$age)], col='red', lwd=1.5)+
        points(data$age, data$length_mm, pch = 16, cex = 1, col = "blue")+
        points(outliers$age, outliers$length_mm, pch = 16, cex = 1, col = "red")
  
      } else{
      plot(data$age, data$length_mm, col = "white",
           main = paste(paste0(species, " - ", years[k], " - Q",qtr[kk],
                               " - Area ", areas[kkk], " - Age at Length")),
           xlab = "Age",
           ylab = "Length [mm]",
           cex.main = 1.5,
           cex.lab = 1.5,
           xaxt="n")+
        axis(1,at=unique(data$age),labels=unique(data$age))+
        grid()+
        points(data$age, data$length_mm, pch = 16, cex = 1, col = "blue")+
        points(outliers$age, outliers$length_mm, pch = 16, cex = 1, col = "red")  
        
      }
      
      ### weight stuff
      anim <- anim[!is.na(anim$length_mm), ]
      anim <- anim[!is.na(anim$weight), ]
      
      anim$log_length <- log(anim$length_mm)
      anim$log_weight <- log(anim$weight)
      new <- anim[anim$animalId %in% data$animalId, ]
      old <- anim[anim$animalId %!in% data$animalId, ]
      
      if (nrow(old) > 0){
      #make a linear model, the log relationship between weight and length should be linear
      mod1 = lm(log_weight ~ log_length, data = old)
   
      #estimate the prediction interval, with evenly generated numbers based on data range
      sim.dat = seq(min(old$log_length), max(old$log_length), length.out=nrow(old))
      preds <- predict(mod1, newdata = data.frame(log_length=sim.dat), 
                    level=0.999999, interval = 'prediction')
   
      #put the "new"/relevant data trough the model made with the old data, to see how well it follows the given           trend
      preds2 <- predict(mod1, newdata = data.frame(log_length=new$log_length), 
                     level=0.999999, interval = 'prediction')
      #select data within the preiction interval, and thereby finding outliers
      insideInterval <- new[new$log_weight > preds2[,'lwr'] & new$log_weight < preds2[,'upr'], ] 
      
      #the new data NOT inside the interval, previously defined
      out <- new[new$animalId %!in% insideInterval$animalId, ]
      
      # IF THERE IS DUPLICATED LENGTH WEIGHT it is assumed that it is not an outlier
      outliers2 <- out[!(duplicated(out[, c("weight", "length_mm")]) | 
                   duplicated(out[, c("weight", "length_mm")], fromLast = TRUE)), ]
      
      # add possible duplicated points to inside interval for plot purposes
      insideInterval <- rbind(insideInterval, out[out$animalId %!in% outliers2$animalId, ])
      
      #plot. firstly the confidence band and trend from old data, but without old data points (overridden with white         points)
        #secondly, plot the new data (in red), and data within confidence interval (in blue). overlapping points so           as to visualize the putliers
      plot(new$length_mm, new$weight, pch = 16, cex = 0.5, col = "red", 
              main = paste(paste0(species, " - ", years[k], " - Q",qtr[kk],
                               " - Area ", areas[kkk], " - Length at Weight")),
              xlab = "Length (mm)",
              ylab = "Weight (kg)", 
              cex.main = 1.5,
              cex.lab = 1.5)+ 
           points(insideInterval$length_mm, insideInterval$weight, pch = 16, cex = 1, col = "blue")
      
      } else {
        lw<-new$log_length/log(new$weight*1000)
  
        ## Calculate the mean and sd
        smean <- mean(lw, na.rm = TRUE)
        sds <-  sd(lw, na.rm = TRUE)
        ## Identify the cells with value greater than cutoff * sd (column wise)
       outliers2 <- rbind(new[which(lw >  smean + (4 * sds)), ], new[which(lw <  smean - (4 * sds)), ])
        
        plot(new$length_mm, new$weight, pch = 16, cex = 1, col = "blue",
              main = paste(paste0(species, " - ", years[k], " - Q",qtr[kk],
                               " - Area ", areas[kkk], " - Length at Weight")),
              xlab = "Length (mm)",
              ylab = "Weight (kg)",
              cex.main = 1.5,
              cex.lab = 1.5)+
           points(outliers2$length_mm, outliers2$weight, pch = 16, cex = 1, col = "red")
      }
        
      #gather the outliers from the original data set, as to have all relevant information 
      outliers_age <- data[data$animalId %in% outliers$animalId, ]    
      outliers_age$type <- rep("age", nrow(outliers_age))
      
      outliers_weight <- data[data$animalId %in% outliers2$animalId, ]
      outliers_weight$type <- rep("weight", nrow(outliers_weight))
      
      collect <- rbind(outliers_age, outliers_weight) 
      collect #state the variable that should be collected by the function
    }
    temp<-lapply(1:length(areas), fun) #function to get data and run the loop/function
    outliers<-data.frame(do.call("rbind", temp))
    
    }
    temp<-lapply(1:length(qtr), fun) #function to get data and run the loop/function
    outliers<-data.frame(do.call("rbind", temp))
    
    outliers #state the variable that should be collected by the function
  }
  temp<-lapply(1:length(years), fun) #function to get data and run the loop/function
  outliers<-data.frame(do.call("rbind", temp))
}
```


\newpage
\section{Table of Outliers}
```{r ,echo=FALSE, results='asis', cache=FALSE, message=FALSE, warning=FALSE, fig.width=12, fig.height=7}

if (nrow(age_fish) != 0){
  age_outliers <- outliers[outliers$type == "age", 
                           c("animalId", "speciesCode", "cruise", "date", "station", "individNum", "area",
                                           "sexCode", "length_mm", "age", "otolithReadingRemark")] #state the variable that should be
  
  weight_outliers <- outliers[outliers$type == "weight", 
                              c("animalId", "speciesCode", "cruise", "date", "station", "individNum", "area",
                                           "sexCode", "length_mm", "weight")] #state the variable that should be
  ## make a table of outliers found above, if any.
  if (nrow(data.frame(age_outliers)) > 0){
  
   print(age_outliers %>%
           kbl(escape = F, longtable = T, caption = "Age outliers", 
               booktabs = T, linesep = "", row.names = F,    
               col.names = c("AnimalId", "Species", "Cruise", "Date", "Station", "Fish No", "Area", 
                             "Sex", "Length", "Age", "AQ"), align = "l") %>%
           row_spec(0, bold = TRUE) %>%
           kable_styling(latex_options = c("striped", "hold_position")) %>%
           column_spec(1, width = "1.5cm") %>%
           column_spec(2:3, width = "1.2cm") %>%
           column_spec(4, width = "2cm") %>%
           column_spec(5, width = "1.2cm") %>%
           column_spec(6, width = "1.5cm") %>%
           column_spec(7:10, width = "1cm") %>%
           column_spec(11, width = "0.5cm")
   )
  } else {
    
    text<-c("No Detected Age Outliers")
    #Make table
    print(text %>% 
        cell_spec(color = "green", font_size = 15, bold = T) %>%
        kbl(booktabs = T, escape = F, col.names = NULL)  %>%  
        kable_styling(latex_options = c("hold_position")) 
    )
  }  
  
  if (nrow(data.frame(weight_outliers)) > 0){
  
    print(weight_outliers %>%
           kbl(escape = F, longtable = T, caption = "Weight outliers", 
               booktabs = T, linesep = "", row.names = F,    
               col.names = c("AnimalId", "Species", "Cruise", "Date", "Station", "Fish No", "Area", 
                             "Sex", "Length", "Weight"), align = "l") %>%
           row_spec(0, bold = TRUE) %>%
           kable_styling(latex_options = c("striped", "hold_position")) %>%
           column_spec(1, width = "1.5cm") %>%
           column_spec(2:3, width = "1.2cm") %>%
           column_spec(4, width = "2cm") %>%
           column_spec(5, width = "1.2cm") %>%
           column_spec(6, width = "1.5cm") %>%
           column_spec(7:10, width = "1.2cm")
    )
    
  } else {
    
    text<-c("No Detected Weight Outliers")
    #Make table
    print(text %>% 
        cell_spec(color = "green", font_size = 15, bold = T) %>%
        kbl(booktabs = T, escape = F, col.names = NULL)  %>%  
        kable_styling(latex_options = c("hold_position")) 
    )
  }
}  
```




