---
fontsize: 11pt
geometry: top=2cm, bottom=2cm, left=1.5cm, right=1.5cm,headsep=1cm
header-includes:
- \usepackage[utf8]{inputenc}
- \usepackage{fancyhdr}
- \pagestyle{fancy}
- \fancyfoot{}
- \usepackage{ragged2e}
- \linespread{1.15}
- \usepackage{float}
output: pdf_document
fig_caption: yes
keep_tex: yes
---

```{r set_libraries, include=FALSE, warning=FALSE}

#Libraries used in the r code
if (!require(pacman)){
  install.packages("pacman", repos="http://ftp.ussg.iu.edu/CRAN/")
  library(pacman)
}
p_load(kableExtra, sqldf, RODBC, dplyr, lubridate, data.table)

#special for this script

## costum functions


```


```{r set_parameters, include=FALSE}

# y1 <- @paramYear1
# y2 <- @paramYear2
#areas <- c(@paramArea)
# species <- c(@paramSpecies)

# Paramters to use in R
y1 <- 2021
y2 <- 2021
areas <- c(20, 21)
species <- c("SIL")


```


```{r get_data, include=FALSE}

channel <- odbcConnect("FishLineDW")

dat <- sqlQuery(channel,
        paste("SELECT Sample.sampleId, Sample.tripId, Animal.animalId, Sample.year, 
                      Sample.quarterGearStart, Sample.cruise, Sample.trip, Sample.tripType, 
                      Sample.station, Sample.labJournalNum, Trip.platform1, Trip.harbourLanding, 
                      Sample.dfuArea, Sample.statisticalRectangle, Sample.latPosStartText, 
                      Sample.latPosEndText, Sample.lonPosStartText, Sample.lonPosEndText, 
                      Sample.latPosStartDec, Sample.lonPosStartDec, Sample.latPosEndDec, 
                      Sample.lonPosEndDec, Sample.dateGearStart, SpeciesList.speciesCode, 
                      SpeciesList.sizeSortingDFU, SpeciesList.landingCategory, 
                      SpeciesList.treatment, SpeciesList.speciesListId,
                      Animal.representative, Animal.individNum, Animal.length, Animal.lengthMeasureUnit,
                      SpeciesList.sexCode AS sp_sexcode, Animal.sexCode, Animal.number AS AnimalNumber, 
                      Animal.weight, Animal.treatmentFactor, Animal.parasiteCode, Animal.maturityIndex,
                      Animal.maturityIndexMethod, Animal.maturityReaderId, Animal.maturityReader, 
                      Animal.numVertebra, Age.age, Age.number AS AgeNumber, Age.ageReadId,
                      Age.ageReadName, Age.otolithReadingRemark, Age.hatchMonth, Age.hatchMonthRemark,
                      Age.hatchMonthReaderId, Age.hatchMonthReaderName, Sample.remark AS remarkSample, 
                      Animal.remark AS remarkAnimal, Age.remark AS remarkAge, Age.hatchMonthRemark, 
                      Age.genetics, Age.visualStock, Age.geneticStock
            FROM      [FishLineDW].[dbo].Sample INNER JOIN
                      [FishLineDW].[dbo].SpeciesList ON Sample.sampleId = SpeciesList.sampleId INNER JOIN
                      [FishLineDW].[dbo].Animal ON SpeciesList.speciesListId = Animal.speciesListId INNER JOIN
                      [FishLineDW].[dbo].Trip ON Sample.tripId = Trip.tripId LEFT OUTER JOIN
                      [FishLineDW].[dbo].Age ON Animal.animalId = Age.animalId
            WHERE     (Sample.year between ",y1," and ",y2," ) AND 
                      (SpeciesList.speciesCode IN ('", paste(species,collapse = "','"),"')) AND
                      (Sample.dfuArea IN ('", paste(areas,collapse = "','"),"')) AND
            (Animal.individNum != 0)
            ORDER BY  Sample.dateGearStart
                      ", sep = ""))
                    

#length dist
len_dist <- sqlQuery(channel, paste("SELECT
       [speciesListRaisedId] AS speciesListId
      ,[speciesCode]
      ,[year]
      ,[cruise]
      ,[trip]
      ,[tripType]
      ,[station]
      ,[DFUArea]
      ,[dateGearStart]
      ,[cuticulaHardness]
      ,[ovigorous]
      ,[broodingPhase]
      ,[landingCategory]
      ,[dfuBase_Category]
      ,[quarterGearStart] AS quarter
      ,[sizeSortingEU] AS sortering
      ,[sizeSortingDFU] AS opdeling
      ,[speciesList_sexCode] AS kønsOpdelt
      ,[length]
      ,[numberTotalPerLength]
  FROM      [FishLineDW].[dbo].[AnimalRaised]
  WHERE     (speciesListRaisedId IN ('",paste0(dat$speciesListId, collapse="','"), "'))
  " ,sep = ""))

close(channel)

len_dist <- merge(len_dist, unique(dat[, c("speciesListId", "sampleId")]))

setDT(len_dist)
len_dist <- len_dist[ ,. (numAtLngtRaised = sum(numberTotalPerLength, na.rm = T)),
                      by = .(sampleId, DFUArea,
                             year, cruise, trip, station, speciesCode,
                             length)]

dat$labJournalNum <- ifelse((dat$labJournalNum == '' | is.na(dat$labJournalNum)) & dat$tripType == "HVN",
                            dat$station, dat$labJournalNum)

dat$date <- date(dat$dateGearStart)

###

channel <- odbcConnect("FishLineDW")
animalReference<-sqlQuery(channel,
                  paste("SELECT  animalId, referenceId
                         FROM     [FishLineDW].[dbo].R_AnimalReference
                                          ", sep = ""))
close(channel)

channel <- odbcConnect("FishLine")
L_reference<-sqlQuery(channel,
                  paste("SELECT  L_referenceId AS referenceId, description
                        FROM     [FishLine].[dbo].L_Reference
                               ", sep = ""))
close(channel)

merged1 <- merge(animalReference, L_reference, by = c("referenceId"), all.y = TRUE)
merged1$referenceId <- paste0("ref_", merged1$referenceId)

setDT(merged1)
wide <- dcast(merged1, animalId ~ referenceId, value.var = "description")
wide <- wide[complete.cases(wide$animalId), ]

merged2 <- merge(dat, wide, by = c("animalId"), all.x = TRUE)

```

```{r export table, include=FALSE}
#reorder data frame
merged2 <- merged2 %>% relocate(c(animalId), 
                        .after = tripId)

merged2 <- merged2 %>% relocate(c(ref_1, ref_2, ref_3, ref_4, ref_6, ref_7, ref_8, ref_9, 
                                  ref_10, ref_11, ref_12, ref_13), 
                        .after = date)

# ##Output fish-age information

#write.csv2(merged2, file = "Q:/dfad/users/jostou/home/temp/SIL_otput.csv",
#            quote = FALSE, row.names = FALSE, na = '')

names <- toString(species)
names <- gsub(', ', '.', names)

write.csv2(merged2, paste0(names, "_", y1, "_", y2, "_Data_", Sys.Date(), ".csv"),
           quote = FALSE, row.names = FALSE, na = '')


write.csv2(len_dist, paste0("lenDist_", names, "_", y1, "_", y2, "_Data_", Sys.Date(), ".csv"),
           quote = FALSE, row.names = FALSE, na = '')

title<-c(paste0(Sys.Date(), ".csv"))
```

\thispagestyle{empty}

\vspace*{2cm} 

\textbf{\LARGE Data eksporteret som "`r names`\_`r y1`\_`r y1`\_Data\_`r title`"}

\vspace{2cm}   


\textbf{\LARGE Data for år `r y1` til `r y2`}\
\vspace{0.5cm}

\textbf{\Large Art:}
\textbf{\Large `r species`}\
\vspace{0.5cm}


Two outputs to file, one with all positional / station information together with individual fish data. The other is length distributions of the species, with raised numbers. 


